### 2018-02-27 book.tex
migdec and paper updates

%% This file is automatically generated, DO NOT EDIT

\renewcommand{\REPORT}{THESIS}
\renewcommand{\GROUP}{None}
\renewcommand{\thepage}{}
\include{tpg}	\cleardoublepage	\newpage
\pagenumbering{roman}
\setcounter{page}{1}
\include{intro}		\newpage
\cleardoublepage
\pagenumbering{arabic}
\setcounter{page}{1}
\GEOheader{\GROUP, \REPORT, \today}
%% start of paper list
\setfigdir{Fig}\GEOpaper{chapter-intro}{chapter-intro}	\include{chapter-intro/paper}
\cleardoublepage
%% end of paper list
\cleardoublepage
\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{seg}
\bibliography{thesis}

### 2018-02-27 chapter-intro/paper.tex
migdec and paper updates

\title{Introduction}
\author{Sarah Yvonne Greer}
\maketitle

\subsection{Background}

### 2018-02-27 vita.tex
migdec and paper updates

Sarah graduated with highest honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin to pursue her undergraduate studies.

### 2018-03-13 chapter-merge/paper.tex
added junk to migdec yay

\title{Introduction}
\author{Sarah Yvonne Greer}
\maketitle

\subsection{Background}

\section{Introduction}

Modern high-resolution seismic acquisition systems, such as P-cable
\cite[]{pcable,tip}, can produce detailed images of the subsurface at
shallow depths. These images often need to be matched with those
previously produced from legacy images using conventional seismic acquisition. In
comparison with high-resolution images, conventional images have
generally lower frequency content and correspondingly lower depth
resolution, but better signal content with depth. In order to reconcile the
differences between the two types of images, they need to be
properly matched.

Analogous problems occur when interpreting images from multicomponent
seismic acquisition. In particular, single-component
PP and converted PS images often exhibit significantly different frequency content
and different resolution and need to be balanced for accurate registration
\cite[]{hardage,SEG-2003-07810784,warp}.

In this paper, we consider the problem of matching images obtained
with different resolution. Using techniques borrowed from
multicomponent image processing \cite[]{warp}, we propose a multistep
approach. First, the two images are balanced in amplitude and
frequency content. As a result, the resolution of the
high-resolution image is degraded. Next, we measure shifts between
images using local similarity
scanning \cite[]{attr,timelapse}. Finally, when the images are aligned and 
matched, we create a blended image using least-squares inversion.

%We test the proposed approach using data from the Gulf of Mexico. 
We test the proposed approach using data from the Gulf of Mexico. 
A 2D image is used to demonstrate the method, and a 3D
example is provided at the end.

\inputdir{apache}

%\multiplot{3}{legacy,hires,merge2-reverse}{width=1.0\columnwidth}{The initial legacy (a) and high-resolution (b) images.
%The merged image (c) is the final product of the proposed workflow: the combination of both the legacy and high-resolution images.}

\section{Method}

The initial legacy and high-resolution example images are shown in Figures~\ref{fig:legacy}
and \ref{fig:hires}, respectively. The images show similar structures, particularly at shallow depths, but with
strikingly different resolution. The main difference comes from the
broader frequency bandwidth of the high-resolution image in comparison
with that of the legacy image. Therefore, our first step in comparing
the two images is balancing their spectral content.

\subsection{Balancing spectral content}

Analyzing the spectra of the legacy and high-resolution images, as
%seen in Figure \ref{fig:nspectra}, it is clear that the
seen in Figure \ref{fig:nspectra22-reverse}, it is clear that the
high-resolution image has a wider range of frequencies with a higher
dominant frequency than the legacy image. In order to match these
images, our first step is to balance their spectral content. We can achieve 
this by attenuating the high frequencies of the high-resolution image
to match the lower frequency content of the legacy image. One approach
to doing this is to apply a stationary bandpass filter to the
high-resolution image. However, this does not take into account
local frequency variations in each image caused by seismic wave attenuation.
A more effective method is to apply a non-stationary filter using
frequency information from both of the images. To accomplish this, we use a
simple triangle smoothing operator with an adjustable radius. 
To measure local frequencies and to estimate the smoothing radius, we
utilize the concept of local seismic attributes, which
involves measuring signal characteristics in a specified local region of data
samples, rather than globally through the whole image or
instantaneously at each point \cite[]{attr}.

%\multiplot{2}{nspectra,hires-smooth-spec}{width=0.68\columnwidth}{Spectra of legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}

The justification for triangle smoothing is that it approximates
Gaussian smoothing \cite[]{pvi}. The frequency response of the triangle smoothing filter \cite[]{pvi} is
\begin{equation}
\label{eq:Tf}
T(f) = \mathrm{sinc}^2\left(\frac{2\pi f \Delta t}{2}\right) \approx 1-\frac{(2\pi f)^2(\Delta t)^2}{12}\;.
\end{equation}
This frequency response closely resembles that of a Gaussian,
\begin{equation}
\label{eq:gaussian}
G(f) = e^{-\alpha f^2} \approx 1 - \alpha f^2\;.
\end{equation}
If the signals' spectra can be represented by Ricker wavelets,
\begin{equation} 
\label{eq:Sn}
S_{n}(f) = A_{n} \left(\frac{f}{f_{n}}\right)^2e^{-\left(\frac{f}{f_{n}}\right)^{2}}\,
\end{equation}
where, in image $n$, $S_n$ is the frequency spectrum, $f_n$ is the peak frequency, and $A_n$ is the amplitude, Gaussian smoothing can transform the signal to a different dominant frequency.

Because we are smoothing the high-resolution image to match it with the legacy image, we can model the high-resolution frequencies, $S_h$, after the legacy frequencies, $S_l$, such that 
\begin{equation} 
\label{eq:smooth}
S_{l}(f)=A e^{-\alpha f^2}\,S_h(f)      
\end{equation}
where $A=A_l/A_h$,
\begin{equation}
\label{eq:alpha}
\alpha = \frac{1}{f_l^2}-\frac{1}{f_h^2} \;,
\end{equation}
and the subscripts $l$ and $h$ correspond to the legacy and high-resolution images, respectively.

Combining equations~(\ref{eq:Tf}), (\ref{eq:gaussian}), and (\ref{eq:alpha}) leads to the specification of the triangle smoothing radius as
\begin{equation}
\label{eq:radius}
\Delta t \approx \frac{1}{2\pi}\sqrt{12\left(\frac{1}{f_{l}^{2}}-\frac{1}{f_{h}^{2}}\right)}\;.
\end{equation}
Here, $\Delta t$ is the radius of smoothing, measured in samples,
applied to the high-resolution image to match the frequency content with the legacy image
at each sample. 
%Measuring local frequencies varying across the two
%images, we can also make the smoothing radius variable according to
%equation~(\ref{eq:radius}).         % change this? redundant?

We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image. The constant 12 in the equation is adjusted to achieve a better match. This effectively reduces the difference between the spectral content of the images.
%, as shown in Figure \ref{fig:hires-smooth-spec}. 
Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. After smoothing, the frequency difference is minimized. % Change?

%\multiplot{2}{freqdif,freqdif-filt}{width=0.85\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing the frequency content by non-stationary smoothing.}

%\plot{warpscan3}{width=\columnwidth}{Local similarity scan for the entire image. Red indicates a high similarity at that time shift between the two images.}

% possibly skip
%\plot{warppick3}{width=0.95\columnwidth}{Relative time shift for the entire image estimated by the trend of highest picked similarity from the local similarity scan.} % Why is the time shift generally less at depth?

%\plot{nspectra22}{width=0.95\columnwidth}{The spectra of the legacy (blue dotted), high-resolution (red dashed), and merged (magenta solid) images.}

\subsection{Measuring time shifts}
% Time variant shift?

After balancing the spectral content, we attempt to account for potential time shifts of the
high-resolution image relative to the legacy image, which can be
caused by changes in acquisition and processing parameters. We measure
this shift using local similarity scanning \cite[]{attr,
  timelapse}. In this method, we detect the relative time shift by
first calculating the local similarity at different time shifts of the
high-resolution image relative to the legacy image
\cite[]{timelapse}. %The result is shown in Figure \ref{fig:warpscan3}. From
%this, the trend of greatest similarity is automatically detected
From this, the trend of greatest similarity is picked
and represents the relative time shift between the two images.
%and represents the relative time shift between the two images, as shown in Figure \ref{fig:warppick3}.

%\newpage

Next, we apply the estimated time shift to the original high-resolution image in order to align the signal content between the two images.
%The differences between the two images before and after the time shift correction are shown in Figure \ref{fig:diff0,diff1}, and demonstrate a better match resulting from the time shift.

%\multiplot{2}{diff0,diff1}{width=0.67\columnwidth}{Difference between the legacy and smoothed high-resolution images before (a) and after (b) accounting for time shifts. Before warping, much of the signal content did not align in time, so coherent reflections were subtracted out. After warping, the reflections are more aligned, so much of the subtracted information is noise.}

\subsection{Creating the blended image}

Since the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together 
to combine the strengths of each while minimizing their weaknesses.
%In addition to comparing the two images, we can also try to blend them together. 
We can achieve this by imposing two conditions. First, the blended image should match the high-resolution image, particularly in the shallow part. Second, after smoothing with the non-stationary smoothing operator, the blended image should match the legacy image. We combine the two conditions together in the least-squares system
\begin{equation}
\label{eq:ls}
\left[\begin{array}{c} \mathbf{W_h} \\
        \mathbf{W_lS} \end{array}\right]\,\mathbf{b} \approx \left[\begin{array}{c} \mathbf{W_h\,h} \\
        \mathbf{l} \end{array}\right]\;,
\end{equation}
% should it be h hat?
where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the
legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$
are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary
smoothing specified by equation (\ref{eq:radius}). The formal solution of the
least-squares problem~(\ref{eq:ls}) is
\begin{eqnarray}
\nonumber
\mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right) \\
& = & \mathbf{h} +  \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,
\mathbf{S}^T\,\mathbf{W_l}\left(\mathbf{l - W_l S h}\right)\;.
\label{eq:inv}
\end{eqnarray}

The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities 
from each image. We estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy images's amplitudes with respect to the high-resolution image.

%\plot{nspectra22-reverse}{width=0.90\columnwidth}{The spectra of the legacy (blue dotted), high-resolution (red dashed), and merged (magenta solid) images for the first data set.}
% Dotted dashed solid

We implement the inversion in equation~(\ref{eq:inv}) iteratively
using the method of conjugate gradients. The resultant blended image,
shown in Figure~\ref{fig:merge2-reverse}, retains the higher
frequencies from the high-resolution image while incorporating the
lower frequencies from the legacy image
(Figure~\ref{fig:nspectra22-reverse}). The broader frequency bandwidth
corresponds to an increase in resolution and leads to a more detailed
and interpretable image.  As a result, the blended image resembles the
high-resolution image but has a marked decrease in noise and extended
coverage with depth. 
%The change from the high-resolution image to the blended image is shown in Figure~\ref{fig:merge1-reverse}.

%\plot{merge1-reverse}{width=\columnwidth}{The difference between the merged and high-resolution images. It is clear that the merged image generally resembles the high-resolution image, especially in the shallow part. However, at depth, it incorporates more from the legacy image.}

\section{P-cable Example}
\inputdir{pcable}
We also applied this method to a 3D data set, which is shown in Figure \ref{fig:legacy4,hires4,merge3}.
%This second example includes data from the inner shelf of the Gulf of Mexico, just off of San Luis Pass, Texas. The high-resolution P-cable data set was acquired by The Bureau of Economic Geology at The University of Texas at Austin of a shallow marine environment in the Gulf of Mexico. 
This second example includes data from the inner shelf of the Gulf of Mexico, just off of San Luis Pass, Texas. The high-resolution P-cable data set was acquired from a shallow marine environment in the Gulf of Mexico. 
%This P-cable acquisition system allows for short offset, low fold data. 
%The area of interest for this survey was the near subsurface, and a high frequency source was used which allows for exceptional resolution in the shallow section, at the expense of less coherent signal information at depth due to attenuation. There is legacy data coverage over the same area, which has better signal continuity at depth than the high-resolution P-cable data. This is apparent by looking at the first few hundred milliseconds of data for both data sets, as shown in Figure \ref{fig:legacy4window,hires4window,legacy4window2,hires4windowagc} (\cite{tip}).
The area of interest for this survey was the near subsurface, and a high frequency source was used which allows for exceptional resolution in the shallow section, at the expense of less coherent signal information at depth due to attenuation \cite[]{tip}. There is legacy data coverage over the same area, which has better signal continuity at depth than the high-resolution P-cable data. 
%\multiplot{4}{legacy4window,hires4window,legacy4window2,hires4window2agc}{width=0.7\columnwidth}{The first 600 ms of data from a sample line from the legacy (a) and high-resolution (b) data sets, and the same images with depth for the legacy (c) and high-resolution (d) data sets. From this, it is clear that we would like our final data set to resemble the high-resolution data set in the shallow parts and the legacy data with depth.} 
%\multiplot{2}{window1,window2}{width=0.75\columnwidth}{The first 600 ms of data from a sample line from the legacy, high-resolution, and merged data sets (a). The same images with depth for the legacy, high-resolution, and merged data sets (b). The merged data set resembles the high-resolution data set in the shallow parts and incorporates the more coherent lower frequency information from the legacy data set with depth.} 
%\plot{windowed}{width=\columnwidth}{The first 600 ms of data from a sample line from the legacy (a) and high-resolution (b) data sets, and the same images with depth for the legacy (c) and high-resolution (d) data sets. From this, it is clear that we would like our final data set to resemble the high-resolution data set in the shallow parts and the legacy data with depth.}

Due to the nature of acquisition, the high resolution data set has very dense spatial coverage, %with bins of about 6.25 m\textsuperscript{2}, 
providing detailed time slices of the near subsurface \cite[]{tip}. The legacy data set has lower spatial resolution, and the two images were acquired using different geometries. %in different directions. 
As a result, when matching the high-resolution and legacy images spatially, the high spatial resolution of the high-resolution data set must be degraded to match that of the legacy data set. The legacy and high-resolution images are rebinned to ensure that they are aligned spatially before continuing.
%, and the rebinned initial data sets are shown in Figures \ref{fig:legacy4} and \ref{fig:hires4}.

%\plot{cdp}{width=\columnwidth}{The CDP bin map of the legacy (blue) and high-resolution (red) data sets. The high-resolution data set has much more dense coverage than the legacy data set, which must be compromised when spatially aligning the two data sets.}
%\plot{nspectra}{width=\columnwidth}{The spectral content of the legacy (blue) and high-resolution (red) data sets.}

%\inputdir{pcable}

There is a definite separation in frequency content when comparing the legacy and high-resolution images, as shown in Figure \ref{fig:nspectra2}. 
Because there is not much overlap in frequency bandwidth, balancing their spectral content is difficult. As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:radius}) to ensure matching frequency content. We first apply a low-cut filter to the legacy data.

Next, we adjust the non-stationary smoothing radius based on two assumptions. 
First, the smoothing radius is too small at a specified point if, after smoothing, the high-resolution image still has a much higher local frequency than the legacy image. Thus, the smoothing radius must be increased at that point.
Second, the smoothing radius is too large if the high-frequency image has lower frequency content than the legacy image at a specified point after smoothing. In this case, the smoothing radius must be decreased at that point.

Using these two assumptions, we can continually adjust the smoothing radius until we have achieved the desired result of balancing the local frequency content between the two images. This process is discussed in further detail in the companion paper \cite[]{locfreq}.

After this, we use the low-cut filtered legacy and smoothed high-resolution images to find estimated time shifts we need to apply to the high-resolution data to align the reflections with the legacy data. Then, we apply this estimated time shift to the original high-resolution image and blend it with the original legacy image as specified by equations~(\ref{eq:ls}) and (\ref{eq:inv}).

The resultant merged image is shown in Figure \ref{fig:merge3}. The frequency content of the merged image is shown in Figure 
\ref{fig:nspectra2}. Here, the merged image spans the frequency bandwidth of the two initial images, thus producing a high resolution volume including optimal signal characteristics from the two initial images.

%\plot{nspectra2}{width=0.90\columnwidth}{The spectral content of the legacy (blue dotted), high-resolution (red dashed), and resultant merged (magenta solid) images for the second data set.}

%The results are shown in Figures \ref{fig:hires4,legacy4,mergeagc} and \ref{fig:hires4,legacy4,merge}.

\inputdir{pcable2}

%\multiplot{3}{legacy4,hires4,merge3}{width=1.0\columnwidth}{The legacy (a), high-resolution (b), and resultant merged (c) images of the second data set.} 
%\plot{nspectra3}{width=\columnwidth}{The spectral content of the legacy (blue dotted), high-resolution (red dashed), and resultant merged (magenta solid) data sets.}

\section{Conclusions}

We have proposed an approach to matching seismic images of different
resolutions. Our first step is non-stationary smoothing of the
high-resolution image to match the spectral content and amplitudes
of the legacy image. Next, we estimate the relative time shifts using
local similarity scanning. After matching the two images, we create a
blended image by least-squares inversion, which effectively
combines the best features of the two images: the broader frequency
bandwidth of the high-resolution image with the reflection continuity
and deeper coverage of the legacy image. The final result is an 
interpretable blended image. We have shown example applications of
the proposed method to high-resolution and legacy images from the Gulf
of Mexico.

\section{Acknowledgments}

We thank August Lau, Tip Meckel, and Chuan Yin for useful discussions and Apache and Fieldwood for providing the first example data set. 
We also thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.

\onecolumn

### 2018-03-13 vita.tex
added junk to migdec yay

@@
-Sarah graduated with highest honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin to pursue her undergraduate studies.
+Sarah graduated with high honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin (UT Austin) to pursue her undergraduate studies. 
+She is a candidate for two Bachelor of Science degrees from UT Austin in Geologocal Sciences and Mathematics. 
+After graduation, she plans on pursuing a PhD in Computational Science, Engineering, and Mathematics from UT Austin's Institute for Computational Engineering and Sciences.

### 2018-04-07 ack.tex
Thesis updates

Add acknowledgements here :)
%\begin{flushright}
%SARAH YVONNE GREER
%\end{flushright}
%
%\noindent \emph{The University of Texas at Austin}\\
%\noindent \emph{April 2018} \\ \\

### 2018-04-07 chapter-locfreq/paper.tex
Thesis updates

\title{Balancing local frequency content in seismic data using non-stationary smoothing}
\author{Sarah Yvonne Greer}
\maketitle

\begin{abstract}
        Seismic data can experience non-stationary frequency variations caused by attenuation. This
        problem is encountered when matching multiple data sets, such as in multicomponent image
        registration, because signals with differing frequency content are hard to correlate. In
        this paper, we propose a method to balance frequency content between data sets while taking
        into account non-stationary frequency variations. This method involves finding and applying
        a non-stationary smoothing operator to minimize the local frequency difference between data
        sets. Numerical examples demonstrate that the proposed method improves multicomponent image
        registration and matching images of differing resolution. 
\end{abstract}

\section{Introduction}
        Matching seismic data has many applications in geophysical processing methods, such as
        multi-component image registration, time-lapse image registration, matching well-ties to
        seismic data, and merging seismic data sets \cite[]{ps,fomel2003,lumley,herrera2012}.
        Typically, the workflow for matching data involves finding the optimal time shift, or amount
        of stretching and compressing, of one trace relative to the other that produces the greatest
        similarity between the two traces, as seen in dynamic time warping and local similarity
        scanning \cite[]{hale2013, timelapse, herrera}. However, when the two signals that need to
        be aligned have different spectral content, their comparison can be difficult. Most seismic
        data experience non-stationary, or spatially and temporally variant, frequency content
        caused by attenuation. This problem was discussed in application to multicomponent image
        registration by \cite{fomel2003}, who applied frequency balancing methods to improve
        registration results. \cite{ltft} proposed using local time-frequency decomposition (LTFD)
        to balance frequencies between multicomponent data during registration. However, LTFD is a
        relatively computationally expensive method.

        In this paper, we propose a method to remove non-stationary frequency differences that limit
        the effectiveness of matching data. We suggest applying the proposed method to processing
        flows that involve matching data before attempting to find the time shift to align their
        signal content. To balance frequency content, we use a non-stationary smoothing operator
        with an adjustable smoothing radius to apply to the higher frequency data set. Our approach
        takes the form of an optimization problem which is solved using an iterative method. We
        apply this method to examples of merging high-resolution and conventional seismic images and
        multicomponent image registration.

\section{Method}
\inputdir{merge}
        Two signals of differing frequencies are more difficult to correlate than signals of similar
        frequencies.  For example, Figure \ref{fig:legacy,hires-agc} shows two seismic images
        representing the same subsurface, except they have distinctly different spectral content, as
        shown in Figure \ref{fig:nspectra-orig}. In order to be directly comparable, these two
        images should have similar frequency content.
        In this paper, we look at local frequency \cite[]{attr}, which can be thought of as a
        smoothed estimate of instantaneous frequency \cite[]{white}. Local frequency is a more
        geologically accurate attribute than instantaneous frequency because it honors
        time-frequency uncertainty and does not contain physically unrealistic negative or extremely
        high frequency values \cite[]{attr}.

        In order to balance local frequency content, we propose smoothing the higher frequency data
        using a non-stationary triangle smoothing operator with an adjustable radius. Here, the
        radius at each point is the number of samples in time that that specific data point gets 
        averaged over
        %in either direction 
        in a triangle weight.

        %Our goal is to specifically remove the higher frequency signal variations

        Our goal is to find the temporally and spatially variable smoothing radius, $\mathbf{R}$, that
        minimizes the difference in local frequencies between the two data sets. This can be shown
        in the objective function
        \begin{equation}
                \label{eq:obj}
                \min_{\mathbf{R} \in [1,N]} \Big \Vert \mathbf{F}[ \mathbf{S}_{\mathbf{R}} \mathbf{d}_h ] - 
                \mathbf{F}[ \mathbf{d}_l] \Big \Vert\;,
        \end{equation}
        where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius
        $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower
        frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of
        the smoothing radius.
        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends
        non-linearly on $R$. However, the objective from equation (\ref{eq:obj}) is nearly convex,
        and we choose to use an intuitive iterative approach to find an approximate smoothing
        radius.

        The main premise behind the method comes from the fact that, in general, 
        %the more samples the data are smoothed over, 
        the greater the smoothing radius, the more high frequencies are attenuated by smoothing.
        We choose an initial guess of the non-stationary smoothing radius before applying
        corrections based on two primary assumptions:
        \begin{enumerate}
        \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the
                higher frequency data has \emph{higher} local frequency than the lower frequency
                data. Thus, the smoothing radius must be \emph{increased} at that point. 
        \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the
                higher frequency data has \emph{lower} local frequency than the lower frequency
                data. Thus, the smoothing radius must be \emph{decreased} at that point.
        \end{enumerate}
        We apply these assumptions using a line-search method:
                        \begin{equation}
                               \label{eq:ls}
                               \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \mathbf{r}^{(i)},
                        \end{equation}
        where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $\alpha$ is a
        scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the
        residual at the $i$th iteration, which can be thought of as the search direction, and is
        defined as
          \begin{equation}
                \label{eq:residual}
                \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}} \mathbf{d}_h] - \mathbf{F}[\mathbf{d}_l]\;.
          \end{equation}
        It can be noted that when equation (\ref{eq:residual}) is positive, the higher frequency
        data still has a higher local frequency value at that specific point than the lower
        frequency data, thus the higher frequency data is under-smoothed and the smoothing radius
        should be increased at that point. This follows the form of the first assumption. The second
        assumption is used when equation (\ref{eq:residual}) is negative. When equation
        (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections
        are made. Thus, it is justifiable to set the search direction from equation (\ref{eq:ls})
        equal to the residual.

        Using the two assumptions, we can continually adjust the smoothing radius until we 
        achieve the desired result of balancing the local frequency content between the two data
        sets. In practice, this method produces an acceptable solution in approximately 5 iterations
        and exhibits sublinear convergence. After smoothing the higher frequency data with the
        estimated radius, we use the lower frequency and smoothed higher frequency data to estimate
        time shifts and align the two data sets.

\section{Examples}
        This method is applicable to workflows that require matching data with different frequency
        content. In this paper, we demonstrate two examples where smoothing data before matching
        produces better results.

        \subsection{Matching legacy and high-resolution images}
        High-resolution seismic data, such as those acquired with the P-cable acquisition system,
        can produce very detailed images of the near subsurface \cite[]{tip}. When compared to
        conventional seismic images, high-resolution images have a higher dominant frequency and a
        larger frequency bandwidth. However, they usually lack low frequency content and depth
        coverage that is present in conventional seismic images. As a result, successful
        interpretation of high-resolution images can be aided by matching with legacy data coverage
        over the same area.

        \multiplot{2}{legacy,hires-agc}{width=0.9\columnwidth}{Initial legacy (a) and
        high-resolution (b) images. These images show the same subsurface geology, but look
        remarkably different as the high-resolution image has distinctly higher frequency content
        than the legacy image.}

        \plot{rect5}{width=0.9\columnwidth}{The smoothing radius, which is a function of time and
        space, this method produces after 5 iterations. This represents the number of samples in
        time that the high-resolution image needs to be smoothed over in a triangle weight %in time
        to balance local frequency content with the legacy image.}

        Example legacy and high-resolution images of the same subsurface are shown in Figure
        \ref{fig:legacy,hires-agc}. The first step in matching the two images is to ensure that they
        both have a similar frequency bandwidth so they are directly comparable. The average frequency
        spectra for the two images are shown in Figure \ref{fig:nspectra-orig}. From this, it is
        evident that there is almost no overlap in frequency bandwidth between the two images.
        To address this problem, we apply a low-cut filter to the legacy image to remove some of the
        lower frequencies that are simply not present in the high-resolution image. Next, we
        implement the method described in the previous section to balance local frequency content
        between the two images. The difference in local frequencies (residual, by equation
        \ref{eq:residual}) between the high-resolution and legacy images before balancing frequency
        content and after 5 iterations of the algorithm in equation (\ref{eq:ls}) is shown in Figure
        \ref{fig:freqdif,freqdif-filt5}. After balancing local frequencies, the images show a
        similar spectral bandwidth (Figure \ref{fig:high-smooth-spec5}), which helps increase the
        correlation between the two images and makes matching reflections better defined.

        After the frequency content is matched, the optimal time shift is found to align signal
        content between the legacy and high-resolution images. We then apply this time shift to
        %the original legacy and high-resolution images---the frequency content is only degraded for
        the original high-resolution image---the frequency content is only degraded for the purpose
        of finding the time shift.

        An application of aligning the high-resolution and legacy images is discussed in the companion
        paper \cite[]{merge}.

        \multiplot{2}{nspectra-orig,high-smooth-spec5}{width=0.81\columnwidth}{Spectral content of
        the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral
        balancing.}

\subsection{Multicomponent image registration}
        Multicomponent seismic image registration is an important step before the interpretation of
        P and S images of the subsurface. It involves warping the space of S images to align
        reflections with the analogous reflections of P images \cite[]{fomel2003,warp}.

        Figure \ref{fig:pp,ss} shows PP and SS images from a 9-component seismic survey \cite[]{attr}.
        To properly register the images, we follow the
        method proposed in \cite{warp}. It consists of three primary steps: (1) initial registration
        of PP and SS images using initial interpretation and well-log analysis; (2) balancing
        frequency and amplitude content; and (3) final registration using residual local similarity
        scanning. We incorporate our method of balancing frequency content into the second step in
        this process.

        Before initial registration, the PP image has much higher frequency content than the SS
        image. After the SS image is temporally compressed to PP time for initial registration, the
        two images have more similar frequency content. However, additional frequency balancing is
        still needed before residual registration. This poses a problem as neither image has
        distinctly higher frequencies than the other, so both images need to be smoothed in
        different areas to balance frequency content. In order to do this, we modify the proposed
        method to include two separate smoothing operators---one for each image.

        \multiplot{2}{freqdif,freqdif-filt5}{width=0.81\columnwidth}{Difference in local frequencies
        (residual) between the legacy and high-resolution images before (a) and after (b) the 5th
        iteration of frequency balancing.}

        We modify the objective in equation (\ref{eq:obj}) as
            \begin{equation}
                \label{eq:obj2}
                \min_{\mathbf{R} \in [-N, -1] \cup [1, N]} \Big \Vert \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_p} \mathbf{d}_{p} ] - \mathbf{F}[
                \mathbf{S}_{\mathbf{R}_s}\mathbf{d}_{s}] \Big \Vert\;, 
            \end{equation}
        %were $S_{R_p}$ and $S_{R_s}$ are the non-stationary smoothing operators for the PP and
        %SS images, respectively, and 
        where $\mathbf{d}_p$ and $\mathbf{d}_s$ are the PP and SS images, respectively, and
        $\mathbf{S}_{\mathbf{R}_p}$ and $\mathbf{S}_{\mathbf{R}_s}$ are the non-stationary smoothing
        operators for the PP and SS images, respectively.
        We also modify the residual from equation (\ref{eq:residual}) as
            \begin{equation}
                \label{eq:residual2}
                \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}_{p}}\mathbf{d}_p] -
                \textbf{F}[\mathbf{S}_{\mathbf{R}_s}\mathbf{d}_s]\;.
            \end{equation}
        The ideal radius is still found using the same line-search from equation (\ref{eq:ls}),
        except we allow the smoothing radius to be negative. Physically, a negative smoothing radius
        would signify that the image should be sharpened at that particular point instead of
        smoothed. In this case, instead of trying to sharpen the PP image at that particular point, 
        we
        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
        %define $\mathbf{R}_p$ anda $\mathbf{R}_s$ at each sample as
        %\begin{equation}
        %        \mathbf{R}_p = \begin{cases} \mathbf{R} &\mbox{if } \mathbf{R} \ge 1 \\
        %1 & \mbox{otherwise} \end{cases} 
        %\end{equation}
        %and
        %\begin{equation}
        %        \mathbf{R}_s = \begin{cases} |\mathbf{R}| &\mbox{if } \mathbf{R} \le -1 \\
        %1 & \mbox{otherwise} \end{cases} 
        %\end{equation}
        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
        %define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as
        choose to smooth the SS image by the negative part of the smoothing radius. 
        Thus, we define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as
        %Thus, we define $R_{p,i}$ and $R_{s,i}$ (the $i$th components of $\mathbf{R}_p$ and
        %$\mathbf{R}_s$) as
        \begin{equation}
                R_{p,i} = \begin{cases} R_{i} &\mbox{if } R_{i} \ge 1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}
        and
        \begin{equation}
                R_{s,i} = \begin{cases} |R_{i}| &\mbox{if } R_{i} \le -1 \\
        1 & \mbox{otherwise} \end{cases} 
        \end{equation}

        where $R_i$ is the $i$th component of $\mathbf{R}$ and a radius of 1 represents no
        smoothing. This allows each image to be smoothed in different areas to balance the frequency
        content between the two images.

\inputdir{vecta}
        \multiplot{2}{pp,ss}{width=0.85\columnwidth}{Initial PP (a) and SS (b) images.}

        The results of using this spectral balancing method are shown in Figure
        \ref{fig:before,after}. Comparable results were achieved in \cite{ltft}, who used LTFD to
        balance the spectral content between the two images. However, the method we propose in this
        paper is more straightforward and significantly less computationally expensive.

\section{Conclusions}
        It is difficult to compare signals with differing frequency content because signals with
        differing frequencies are hard to correlate. In this paper, we proposed a method of
        balancing frequency content between data which takes the form of an optimization problem
        solved by a simple iterative algorithm. It is a relatively inexpensive and effective method
        compared to previously proposed methods of balancing frequencies between data sets. We
        applied this method to examples of matching seismic images of differing resolution and for
        multicomponent image registration.

        \multiplot{2}{before,after}{width=0.85\columnwidth}{Interleaved PP and warped SS traces before
        (a) and after (b) frequency balancing and residual registration. After registration, the
        signal content between the two initial images is more aligned; for example, the reflections
        around 0.3 and 0.6 s. This indicates a successful registration.}

\section{Acknowledgements}
        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their
        financial support.

\onecolumn

%\bibliographystyle{seg}
%\bibliography{SEG,locfreq}

### 2018-04-07 chapter-mighes/paper.tex
Thesis updates

\title{Migration deconvolution}
\author{Sarah Yvonne Greer}
\maketitle

%\title{Migration deconvolution using non-stationary matching}
%\title{Approximating the inverse Hessian to enhance migration using non-stationary matching operators}
%\title{Improving migration resolution by approximating the Hessian using non-stationary matching operators}
%\title{Improving migration resolution by approximating the Hessian using non-stationary amplitude and frequency matching operators}
%\title{Improving migration resolution using non-stationary amplitude and frequency matching operators}
%\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
%\title{Approximating the inverse Hessian to enhance migration using linear non-stationary matching operators}
%\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
\newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
\maketitle
%\inputdir{sigsbee}
\inputdir{sigsbee2}
\begin{abstract}
    We propose using two non-stationary operators to represent the amplitude and frequency variations in the least-squares Hessian to account for the principal differences between conventional and least-squares migrated images.
    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration,
    and it increases the resolution and amplitude fidelity of the migrated image.
%    When applying these transformation to a conventionally migrated image, it improves the image resolution.
    %We propose an approach of approximating the inverse Hessian operator in application to migration deconvolution. 
    %Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the Hessian---one to account for amplitude variations, and the other to account for frequency variations. 
    %Successful results were achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
    Successful results are achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
\end{abstract}

\section{Introduction}
%However, the process may be computationally expensive as it typically involves multiple iterations of forward modeling and remigrating the data. 
%Least-squares migration \cite[]{lsm} \ldots
Least-squares migration can produce an accurate migrated seismic image.
However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling and migration. 
%However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling, calculating the residual misfit, performing a conventional migration, and updating the model. 
%At the cost of approximately one iteration of least-squares migration, 
Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%These artifacts are due to the fact that standard migration applies only a single adjoint operation \cite[]{pvi}.
%Least-squares migration can help alleviate 
This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by 
finding the least-squares model solution,
standard migration amounts to applying a single adjoint operation \cite[]{pvi}. 
%Conventionally migrated seismic images generally contain migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%A standard way to alleviate these artifacts 
%is an advanced way of producing an accurate image of the subsurface \cite[]{lsm}.
%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%Conventional migration is not , as such, 
%conventionally migrated images generally suffer from migration artifacts affecting amplitude fidelity and resolution. 
%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%solving the least-squares normal equations, 
%While this can be a good approximation to the inverse, and as such, is not a true inverse operation.

Various methods have attempted to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
%Migration deconvolution attempts to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image. 
Here, $\mathbf{L}$ is a standard forward-modeling operator, and $\mathbf{L}\tran$ is its adjoint---the migration operator.
These methods usually take the form of two approaches---for preconditioning before least-squares migration and as a single operation to improve accuracy of a conventionally migrated image.
%This filter approximates the inverse Hessian operator, and can be approximated by solving a data matching problem between two conventionally migrated images. 
%Migration deconvolution \cite[]{poststack,prestack}
Previously, this has been done by 
migration deconvolution \cite[]{poststack,prestack},
%stochastscally approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{diagamp}, 
approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp},
and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
%This has traditionally been done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different operations are specified in each region \cite[]{seiinv}.
This traditionally is done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different matching filters are specified in each region \cite[]{seiinv}.

In this paper, we take a different approach. 
We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
%Because of this, we choose to approximate the  
Here, we treat this as a data matching problem between two conventionally migrated images, and find separate operations to account for both amplitude and frequency variations.
%However, we propose using two separate non-stationary operators---one to account for amplitude variations, and the other to account for frequency variations.

%This has advantages over previous methods as, instead of using a sliding window approach, we rely on local seismic attributes to measure and apply amplitude and frequency balancing operations \cite[]{attr}.
This approach enables us to rely on local seismic attributes to measure and apply amplitude and frequency balancing operations instead of using a sliding window approach \cite[]{attr}.
This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
%of local seismic attributes, and for 
%In the past, 
Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each 
%transformation 
operation
can be adjusted independently, which is another advantage of the proposed method.
To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}. 
%Least squares migration is more computationally expensive than conventional migration, but it produces a more accurate image of the subsurface---conventional migrated images generally 
%suffer from migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
%exhibit less correct amplitude and frequency content. 
%applying a filter to a conventional migrated image to produce a more accurate image with less computational cost than least-squares migration. 
%Previously, this has been done using non-stationary, or spatially and temporally variant, matching filters in a sliding-window approach.

%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the migration-deconvolution image as a starting moel (red).}
%Once finding the forward operation,
\section{Theory}
The goal of least-squares migration is to find the image, $\hat{\mathbf{r}}$, that minimizes
\begin{equation}
p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
\end{equation}
where $\mathbf{L}$ is the forward modeling operator, representing seismic wave propagation through the subsurface, and $\mathbf{d}$ is the acquired seismic data.
This can be solved by the least-squares formulation to find $\hat{\mathbf{r}}$:
\begin{equation}
        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d}\;,
        \label{eq:ls}
\end{equation}
where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, 
%where $\mathbf{L}\tran$ is the migration operator, 
and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
%Equation (\ref{eq:ls}) is usually solved iteratively, where each iteration costs %by multiple iteration of forward modeling
%where each iteration involves 
%On the other hand, conventional migration
Equation (\ref{eq:ls}) is usually solved iteratively, typically requiring multiple iterations of forward modeling and remigrating the seismic image \cite[]{wem,xue16}. 
Conventional migration is less computationally expensive:
\begin{equation}
        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d}.
        \label{eq:mod}
\end{equation}
%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images \cite[]{dutta14}. 
By combining equations (\ref{eq:ls}) and (\ref{eq:mod}), it is evident that
\begin{equation}
        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{0} \;,
\end{equation}
%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
so $\mathbf{m}_0$ is a distorted version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by finding a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.

%The least squares image, $\hat{\mathbf{r}}$

%Here the forward modeling operator, and subsequently the migration operator, $\mathbf{L}\tran$, depends on the type of migration; RTM vs Kirchhoff\ldots

%We can represent acquired seismic data, $\mathbf{d}$, as a forward-modeled version of the Earth's true reflectivity, 
%\begin{equation}
%        \mathbf{d} = \mathbf{L}\mathbf{r},
%\end{equation}
%where $\mathbf{r}$ is the Earth's reflectivity and $\mathbf{L}$ is the forward modeling operator CITE. 
%Least-squares migration can produce a close approximation to the Earth's reflectivity by finding the least-squares solution,
%\begin{equation}
%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d},
%        \label{eq:ls}
%\end{equation}
%but it can be computationally expensive as it typically requires multiple iterations of forward modeling and remigrating the seismic image CITE. 
%Conventional migration is less computationally expensive:
%\begin{equation}
%        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d},
%        \label{eq:mod}
%\end{equation}
%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
%However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images CITE. 
%By combining equations \ref{eq:ls} and \ref{eq:mod}, it is evident that
%\begin{equation}
%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{1},
%\end{equation}
%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
%
%In order to find $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of CITE. We begin by forward modeling the migrated image, $\mathbf{m}_9$:
%\begin{equation}
%        \mathbf{d}_2 = \mathbf{L}\mathbf{m}_0.
%\end{equation}
%We then remigrate $\mathbf{d}_2$:
%\begin{equation}
%        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_2 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0,
%\end{equation}
%and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
%\begin{equation}
%        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1.
%\end{equation}
%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
%

\section{Method}
%Here, we follow the forward-modeling and remigration approach of

In order to approximate $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of \cite{imop}. 
We begin by forward modeling the migrated image, $\mathbf{m}_0$:
\begin{equation}
        \mathbf{d}_1 = \mathbf{L}\mathbf{m}_0 \;.
\end{equation}
We then remigrate $\mathbf{d}_1$:
\begin{equation}
        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_1 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0 \; ,
\end{equation}
and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
\begin{equation}
        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1 \;.
\end{equation}
%The inverse Hessian operator that must be applied to $\mathbf{m}_0$ to correct it closer to the least-squares migrated image, $\hat{\mathbf{r}}$, therefore, can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
%Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.
%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.

%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), migration migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
%\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
%Typically, the differences between least-squares migrated images and conventionally migrated images amount to only amplitude and frequency changes, 
    Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations. 
    Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
    %We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined. 
    We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
    We then invert our approximation to the Hessian and apply it to $\mathbf{m}_0$ to correct the amplitude and frequency content of the migrated image.

\subsection{Amplitude operator}
First, we choose to find an amplitude balancing operation that, when applied to $\mathbf{m}_0$, balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$. 
%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
This operation can be equated to a trace-by-trace multiplication of a diagonal matrix to each trace, where the matrix changes for every trace.
%The matrix $\mathbf{A}$ changes 
We estimate it by first calculating the amplitude envelope of the traces in $\mathbf{m}_0$ and $\mathbf{m}_1$, and then smoothly dividing them.
The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
%to find the diagonal weighting operator 
%to balance the amplitudes of each trace.
%that balances the amplitudes of each trace of $\mathbf{m}_0$ to match with $\mathbf{m}_1$.
%This is a linear diagonal weighting operator
%This linear operator only has elements across the diagonal terms, so it is trivial to find the inverse operator. 
%Therefore, this operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
%Therefore, the operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.

%\multiplot{2}{a0,a1}{width=1.0\columnwidth}{The forward amplitude balancing weights, $\mathbf{A}_0$ (a) and $\mathbf{A}_1$ (b).}
%\plot{rect10}{width=1.0\columnwidth}{The smoothing radius, which represents the number of samples in both spatial dimentions, that $\mathbf{m}_0$ must be smoothed over in a pyramid weight to balance local frequency content with $\mathbf{m}_1$. This represents the forward smoothing operation, $\mathbf{S}$.}

\subsection{Frequency operator}
In addition to amplitude corrections, we also attempt to account for the decrease in resolution of a conventional migrated image compared to its corresponding least-squares migrated image. 
This loss in resolution can be equated to the fact that $\mathbf{L}\tran\mathbf{L}$ acts as a blurring operator, where the conventional migrated image is a blurred version of the ideal least-squares migrated image \cite[]{poststack}. %where each individual value 
We choose to approximate this blurring using non-stationary triangle smoothing.

%This means that the 
We begin by first calculating the local frequency of the two initial images \cite[]{attr}. 
Local frequency is a temporally and spatially varying frequency attribute that smoothly varies across the image without windows.
Our goal is to find a transformation that we can apply to $\mathbf{m}_0$ that matches the local frequency content with $\mathbf{m}_1$. 
To do this, we propose using non-stationary triangle smoothing. 
%This approach involves finding and applying a non-stationary smoothing radius, which is the amount of samples, in time, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance local frequency content with $\mathbf{m}_1$. 
This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.

We find the smoothing radius iteratively using the method of \cite{locfreq}, with a modification that allows the smoothing radius to be calculated in both spatial directions. 
Essentially, this is found by choosing an initial guess of a smoothing radius, $\mathbf{R}^{(0)}$, and updating it iteratively such that 
    \begin{equation}
        \label{eq:it}
\mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \left [ \mathbf{F}[\mathbf{S}_{\mathbf{R}^{(i)}} \mathbf{m}_0] - \mathbf{F}[\mathbf{m}_1] \right ]\;,
    \end{equation}
    where $\mathbf{F}$ is the local frequency operator, $\mathbf{S}_{\mathbf{R}^{(i)}}$ is the smoothing operator of radius $\mathbf{R}$ at the $i$th iteration, and $\alpha$ is a scalar constant that represents the step length.
    After a small number of iterations, the smoothing operator is found that, once applied to $\mathbf{m}_0$, balances local frequency content with $\mathbf{m}_1$.

%    Unlike $\mathbf{A}$, the smoothing operator, $\mathbf{S}$, is more challenging to invert 
%    since it is generally a banded, but not diagonal, operator and physically represents the mixing of each data point with other nearby data points.
    %This smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric. 
    %However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create false high-frequency data if inverted incorrectly without regularization.
%\multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$. This represents the forward smoothing operation, $\mathbf{S}$.}

    \subsection{Calculating the inverse Hessian}
    Now that we have found the forward operators that separately balance amplitude and frequency content from $\mathbf{m}_0$ to $\mathbf{m_1}$, where $\mathbf{m}_1 \approx \mathbf{H} \mathbf{m}_0$, we want to find what combination of $\mathbf{A}$ and $\mathbf{S}$ best approximates $\mathbf{H}$.
    %An advantage of finding $\mathbf{A}$ and $\mathbf{S}$ separately is that they can each be individually adjusted 
    %the inverse of this operator such that $\hat{\mathbf{r}} = \left (\mathbf{H} \right )^{-1} \mathbf{m}_0$.
    Since $\mathbf{H} = \mathbf{L}\tran\mathbf{L}$ is symmetric, we want our approximation of $\mathbf{H}$ to be as close to symmetric as possible.
    Therefore, we define $\mathbf{H}$ as
    \begin{equation}
            \mathbf{H} \approx \mathbf{A}^{\sfrac{1}{2}}\mathbf{S}\mathbf{A}^{\sfrac{1}{2}} \;,
    \end{equation}
            %\mathbf{H} = \frac{1}{2}\left ( \mathbf{A}\mathbf{S} + \mathbf{S}\mathbf{A} \right )
    where $\mathbf{A}$ is the operator that balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, and $\mathbf{S}$ is the operator that balances the local frequency content of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, both defined previously.
    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric, since both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
    %One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
    Splitting up our approximation to the Hessian into two separate operators allows us to control how much of each operation and the order of each operation goes into correcting the image, and see how it affects the resulting image.
%    \begin{equation}
%        \mathbf{H} = \mathbf{A}_1^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}_0^{\sfrac{1}{2}}\;,
%    \end{equation}
%    where $\mathbf{A}_0$ is found by balancing amplitudes between $\mathbf{m}_0$ and $\mathbf{m}_1$, $\mathbf{S}$ is calculated by finding the smoothing operator that balances the local frequency content between $\mathbf{m}_0$ and $\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_1$, and $\mathbf{A}_1$ is found by balancing amplitudes between $\mathbf{S}\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_0$ and $\mathbf{m}_1$.
%    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be close to symmetric. 
%    However, note that here $\mathbf{H}$ is not quite symmetric, but since $\mathbf{A}_0$ and $\mathbf{A}_1$ should be very similar, it is nearly symmetric.
%    One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
%
    Now that we have found the forward Hessian, $\mathbf{H}$, such that $\mathbf{H}\mathbf{m}_0 \approx \mathbf{m}_1$ using data matching operators, we want to find the inverse of this operator, $\mathbf{H}^{-1}$, such that $\hat{\mathbf{r}} \approx \mathbf{H} ^{-1} \mathbf{m}_0$ provides us with the least-squares image.
    This is found as
    \begin{equation}
            \mathbf{H}^{-1} \approx \left ( \mathbf{A}^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}^{\sfrac{1}{2}} \right )^{-1} = 
            \mathbf{A}^{\sfrac{-1}{2}} \mathbf{S}^{-1} \mathbf{A}^{\sfrac{-1}{2}}\;.
            \label{eq:invh}
    \end{equation}

    Since the amplitude operators only contain diagonal terms, they are simple to invert. 
    %However, the smoothing operator, $\mathbf{S}$, is more challenging to invert. 
    %While smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric,. 
    However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
    Therefore, $\mathbf{S}^{-1}$ must be calculated with care to ensure the inverted data is physically plausible. 
    We iteratively invert $\mathbf{S}$ using shaping regularization \cite[]{shap}, where the shaping operator is a bandpass filter picked to ensure the passband contains only physically possible frequencies for the given data set.
    The cost of applying our approximation to $\mathbf{H}^{-1}$ in equation (\ref{eq:invh}) is $\mathcal{O}(N)$, where $N$ is the image size. 
    The constant is small, typically around 10 for the number of iterations, and the calculation and application of this approximation is computationally insignificant compared to one iteration of least-squares migration. %is far less computationally expensive than one iteration of least-squares migration.
    %The constant is 
    %It is a diagonally-dominant operator
    %The amplitude operator accounts for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms of the forward Hessian operator.
    %Our approximation to the forward Hessian operator turns out to be diagonally-dominant, where the amplitude operators account for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms.

%This allows us to find an operator that effectively balances the local frequency content of $\mathbf{m}_0$ to match with $\mathbf{m}_1$. 
%Next, we need to find the inverse of this operation to 
%Since the operation is non-stationary, it is applied in the time domain

%we follow the approach of CITE. This approach uses non-stationary triangle smoothing. for finding the smoothing radius that 
%
%to increase the resolution of the

%    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}

\section{Example}

%\multiplot*{3}{mod-w3,image0-w3,migdec-w3}{width=0.66\columnwidth}{The Sigsbee model reflectivity (a), the first migrated image (b), and the corrected migrated image (c).}
    We demonstrate the effectiveness of this method on the 2D Sigsbee model. %reverse-time migrated 
    The Sigsbee2A 2D synthetic data set was created to mimic the geology of the Sigsbee escarpment in the Gulf of Mexico \cite[]{sigsbee}.
    %In this example, we use reverse-time migration as our migration operator.
    %* Zhiguang---Insert information about migration specifics (shot/receiver spacing, absorbing boundary conditions, etc.) *
    A fixed-spread acquisition survey is generated, which consists of 301 shots spaced every 122 m.
    The source wavelet for generating the synthetic data is a Ricker wavelet centered at 10 Hz.
    The record length of the synthetic data is 10 s with a time step of 4 ms.
We use reverse-time migration (RTM) as our migration operator.
%\plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image.}

    We begin with the sub-surface reflectivity model (Figure \ref{fig:mod}) and migration velocity model (Figure \ref{fig:vel-migration}).
    Next, we forward model the seismic data and migrate it to get our first conventionally migrated image, $\mathbf{m}_0$ (Figure \ref{fig:image0}). 
    Then, we forward model $\mathbf{m}_0$ and remigrate that data to get $\mathbf{m}_1$ (Figure \ref{fig:image1}).
    This provides us with the two images, $\mathbf{m}_0$ and $\mathbf{m}_1$, that we can use to find the operation $\mathbf{H}$ that maps $\mathbf{m}_0$ to $\mathbf{m}_1$.

    Next, we calculate and apply the data matching operations as described in the previous section. 
    The forward amplitude balancing weight, $\mathbf{A}$, is shown in Figure \ref{fig:a0}.
    The calculated radius for the forward smoothing operation is shown in Figure \ref{fig:rect10b}.
    After applying these two operators to $\mathbf{m}_0$ as described by equation (\ref{eq:invh}), we produce the corrected migrated image, as shown in Figure \ref{fig:migdec-shap}.
    This corrected image better represents the subsurface reflectivity than the conventionally migrated image (Figure \ref{fig:image0}), as it exhibits more correct amplitude content and higher resolution comparable with the reflectivity model.

    Figure \ref{fig:mod-w3,image0-w3,migdec-w3} shows a windowed section of the reflectivity model, the conventionally migrated image, and the corrected migrated image.
    %The corrected migrated image is clearly of higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.
    The corrected migrated image exhibits clearly higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.

%    Figure \ref{fig:spec2} shows the frequency content of the conventionally migrated image and the corrected migrated image. 
%    The corrected migrated image has a broader bandwidth and a flatter spectra than the conventionally migrated image, and generally recovers the higher frequency data that was lost during conventional migration.
%    However, it does lose some low frequency content as a result of the process, 
%    %Additionally, the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
%    but the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
%    is still a better approximation of the model than that of the conventionally migrated image.
%    %is a better approximation of the model than that of the conventionally migrated image.
%

    In addition to directly applying this operator to the conventionally migrated image to improve resolution, this operator can be used as a preconditioner in iterative least-squares migration.
    In this case, the corrected migrated image could be used as an initial model for least-squares migration for faster convergence.

\section{Conclusions}
%Conventionally migration involves 
%A higher resolution least-squares migrated image 
%This method does not involve dividing the data into windows 
Least-squares migration can produce an accurate migrated image, but it is more computationally expensive than conventional migration.
In this paper, we apply an approximate inverse Hessian operator to a conventional migrated image to approximate the least-squares migrated image.
Since the primary differences between least-squares migration and conventional migration amount to amplitude and frequency variations, we approximate the forward Hessian by calculating frequency and amplitude matching operators.
The amplitude matching operator is found by calculating the amplitude envelopes of migrated and remigrated images and smoothly dividing them, and the frequency matching operator is found using an iterative algorithm and non-stationary smoothing.
The Hessian is approximated by a combination of these two operators to ensure symmetry.
This method involves a windowless approach and is cheap to calculate and apply.
Additionally, by defining the Hessian with two separate operators, we can examine, and control, the ``ingredients'' of the Hessian operator, and see how changing them impacts the final image.

After the forward Hessian is calculated, we invert it iteratively using shaping regularization, and apply it to the conventionally migrated image to get an approximation of the least-squares migrated image.
Successful results are achieved on the 2D Sigsbee synthetic model with reverse-time migration as the migration operator.

%\plot{spec2}{width=0.85\columnwidth}{The frequency content of the conventionally migrated image (blue solid), and the corrected migrated image (red dashed).}

\inputdir{sigmoid}
%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the corrected migrated image as a starting model (red). Here, the migration operator is post-stack Kirchhoff migration.}

\section{Acknowledgements}
        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
The examples in this paper can be reproduced using the Madagascar open-source software package \cite[]{madagascar}.

%\inputdir{kir}

\onecolumn

\bibliographystyle{seg}
\bibliography{SEG,migdec}

%        In seismic processing we have the operation of migration, which is a linear transform, and we can think of it as the adjoint of modeling. So if you know the velocity, and you have reflectivitym, so going from reflectivity to data is a linear transformaiton the adjoint of that is migration.
%
%        And then so reflectivity
%        d = Lm
%        So migraziton would be the adjoint applied to the data
%        And if we try to do inverse, it would be:
%        so this is LSM
%
%        And normally we would do it with iterations, so doing conjugate gradients or some sort of iterative method, where we approximate its inverse using iterations. But it is still expensive because in each iteration we need to do modeling and migration, and that's an expensive process.
%        So, the idea is instead of computing this exactly, we approximate it.
%        This is called migrtion deconvolution.
%
%        Now, what does it actrually do?
%        SO the interesting part about the operations of modeling and migration here is that when you do them in term, you do modeling and migfration, so theoretixallty, it's an operation that does somethjing with the input, so you put in one image and get another image.
%        But the other image does not have a shift---things will return to the same place. So, mostly it amounts to scaling, so different scale, and there is also some smearing.
%
%        SO if for example you put this as an input, you'll get the same points but they'll be smeared a little bit, but they'll be in the same place.
%
%        There is some smearing and there is some scaling. So that's what this is basically trying to correct.
%        So, we go from here to here, and there are different ways people tried to do it before.
%        One was just to focus on the scaling, and then so you're looking at the diagonal matrix to apply some scale to compensate.
%        The other was to use theory to try to derive theoretically what this should be, and there are other theories, but they are based on ideal situations, so you don't consider the fact, for example, that the data that you have is not infinite so it has a finite extent.
%        SO the theory is good, but it's idealized to look that everything is continuous, infinite, which is not the case. So part of what we see here when we look at the smearing, so part comes from the nature of modeling and migraiton, which we know theoretically, but part of it is from the fact that the data are not perfect, so we have limited extent, and discrete non-continuous data. So the theory may work in practice and get most of it, but not all of it because it is idealized. 
%        So it's useful, but it's not ??? 27:45
%
%        So Antoine in CSM\ldots
%        This year he shows an application that is specifically for RTM, but the idea comes from his older paper which is 
%        And that was just simply that you \ldots
%        This was done previously to look for just the scaling.
%        You have sort of training images. You can use this M ans one of the training. But you can also create a bunch of the other ones. If you create a bunch of synthetic you have a bunch of reflectivity models, but it's sort of an open question of how you do it. So you can use spikes, reflectors, random, but in some way generate a bunch of those but you apply modeling and migration to it. And now you have example inputs and example outputs, and you want the inverse of this. SO you want to find out how to go back from this to the theoretical. And you cannot use too many bc it get expensive and it is easier to do LS migration with iterations. Computatinoally, the challenge is how to figure out what this is without using too many training images.
%        Instead of the simple scale, he looks for a non-stationary matching filter. Now if we learn what this is, you can just apply it once, and there are also\ldots
%        Single iteration migration, but they mean doing it once
%        Find out how to approximate this inverse and they apply it to compensate. But you can also use it as a preconditioner.
%        So the other use is, so say I'm still going to run iterations, but I'll but this correction inside, and then instead of 10 iterations, maybe I can use it fewer. 
%
%        So there are differences between the asdasd of preconditioned conjugate gradients. Some of them use m, and some split m into two parts. So we can say that you have instead of r and you're looking for x, and you're inverting afjsdkl;, so \ldots 36:40
%        In any conjugate gradients, you can precondition by making it run faster by making the inverted matrix closer to the identity. So there is a dual purpose to this --- to find something you can apply once but you can also use it as a precondioner if you want to do it more than one time.
%        So in this other paper, . . .
%        The reason I mention it to you now for what you did for the matching and triangle filters, so we have another way to describe this kind of a transformation which is fairly robust, and it may work in this application. Basically we have scaling and smearing which is like legacy and high-resolution. So the better question is to find a good example to try. I'm not sure if we have anything in Madagascar yet. We have modeling and migration, so we need to find some kind of example of applying modeling and migration so we can look how to measure the transformation for that. 
%        The interesting question is if you have scaling and you have smearing, maybe with variable radius traingle filters, so the two opeations you need both of them but they don't commute. So if you do scaling first and smearing second it's not the same if you do smearing first and then scaling. When we are dealing with this we know that it needs to be symmetric. 
%
%        There is scaling with the weight and triangle filtering. It can be this, or this. So we are not scaling symmetrically. Or maybe this. So if we start doing something like that, it becomes non-linear, so if we have scaling twice we cannot use linear inversion to find the scaling. So it actually makes it more interesting, so now we need to think how to linearize it so if we have something like that for example, we can say that we want to find maybe an inital scaling; maybe I'll take it to be one initial and 43:15
%        and the other term you neglect to get\ldots
%        Now this one is linear, but it has an interesting combination here from the left side 
%        So now it's a linear problem can be solved with regularization but not the same one as before. So it makes the whole problem a little more interesting
%
%        And then potentially, even if it's not that, so say we go back to legacy and high resolution, so we know there is scaling and there is smearing, but nothing says that scaling has to be on this side or on this size, so it can be both or it can be different on this side and the other size, so it makes it a more general problem with potentially more interesting solutions. 
%
%        So in terms of ideas there is not a lot there, besides what I have told you, but you can read it and follow the references to other papers. So they put some work into implementing it. But if we make it work with scaling and smoothing, it would actually me a much cleaner implementation. Because they have to, So I suspect that what Antoine Guitton had to do to implement it was breaking everything into windows, some overlap, and then finding filters in each window and trying to change them, so it's not very stable and it's a bit messy. So if it works, it works, but I think we can find a cleaner result. and also you know if you break it into scaling and smearing, you know the ingredients of what happens in there, so you have a better understanding.
%

### 2018-04-07 chapter-locfreq/merge/radius.c

@@ -1,0 +1,57 @@
+/* smoothing radius (min = 1) */
+
+#include <rsf.h>
+#include <math.h>
+
+int main (int argc, char* argv[])
+{
+    int n1, n1f, n2, n2f, i, n12, n12f;
+    float *rect, *fr, maxrad, c, *rad;
+    sf_file in, out, freq;
+	
+    sf_init (argc,argv);
+
+    in = sf_input("in");
+    freq = sf_input("freq");
+    out = sf_output("out");
+
+    if (!sf_histint(in,"n1",&n1)) sf_error("No n1= in input.");
+    if (!sf_histint(freq,"n1",&n1f)) sf_error("No n1= in frequency difference.");
+
+    n2 = sf_leftsize(in,1);    
+    n2f = sf_leftsize(freq,1);    
+    
+    n12 = n1*n2;
+    n12f = n1f*n2f;
+
+    if (n1 != n1f) sf_error("Need matching n1");
+    if (n2 != n2f) sf_error("Need matching n2");
+
+    if (!sf_getfloat("c",&c)) c=1.;
+    if (!sf_getfloat("maxrad",&maxrad)) maxrad=1000.;
+
+    rect = sf_floatalloc(n12);
+    sf_floatread(rect,n12,in);
+
+    fr = sf_floatalloc(n12f);
+    sf_floatread(fr,n12,freq);
+
+    rad = sf_floatalloc(n12);
+	
+    for (i=0; i < n12; i++) {
+
+        /* update radius */
+	    rad[i] = rect[i]+c*fr[i];
+
+        /* set constraint conditions: [1, maxrad] */
+        if (rad[i] > maxrad)
+                rad[i] = maxrad;
+        if (rad[i] < 1.0)
+                rad[i] = 1.0;
+    }
+
+    sf_floatwrite(rad,n12,out);
+    exit(0);
+}
+
+

### 2018-04-07 chapter-locfreq/merge/radius.py

@@ -1,0 +1,99 @@
+from rsf.proj import *
+
+def radius(high, low,               # initial high-resolution and legacy images
+           niter,                   # number of corrections
+           c,                       # 'step length' for radius corrections. Can be type int or float for constant c 
+                                    # or type array for changing c.
+           bias=-15, clip=30,       # bias and clip for display
+           rect1=40, rect2=80,      # radius for local frequency calculation
+           maxrad=1000,             # maximum allowed radius
+           theor=True,              # use theoretical smoothing radius
+           scale=9,                 # scale for theoretical smoothing radius
+           initial=10,              # initial value for contant smoothing radius 
+           minval=0,
+           maxval=25,
+           titlehigh="Hires",
+           titlelow="Legacy"):
+
+    if type(c) is float or type(c) is int:
+        c = [c]*niter
+
+    def seisplot(name):
+        return 'grey title="%s"'%name
+    
+    locfreq = '''iphase order=10 rect1=%d rect2=%d hertz=y complex=y | 
+                 put label="Frequency" unit=Hz'''%(rect1,rect2)
+
+    def locfreqplot(name):
+        return 'grey mean=y color=j scalebar=y title="%s" '%name
+
+    freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
+
+    def freqdifplot(num):
+        return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %s" 
+                  clip=%d bias=%d minval=%d maxval=%d''' %(num,clip,bias,minval,maxval) 
+
+    specplot = '''cat axis=2 ${SOURCES[1]} | 
+                  scale axis=1 | window max1=180 |
+                  graph title="Normalized Spectra" label2="Amplitude" unit2=""'''
+
+    def rectplot(name):
+        return 'grey color=j mean=y title="%s" scalebar=y barlabel=Radius barunit=samples'%name
+
+    smooth = 'nsmooth1 rect=${SOURCES[1]}'
+
+    Result(high, seisplot(titlehigh))
+    Result(low, seisplot(titlelow))
+
[…]

### 2018-04-07 chapter-locfreq/vecta/newwarp_locfreq.py

@@ -1,0 +1,643 @@
+from rsf.proj import *
+import math, string, sys
+import rsf.recipes.version as version
+from radius2 import radius2
+
+###########################################################
+#  Modified from $RSFSRC/book/tccs/ltft/vecta/newwarp.py  #
+###########################################################
+
+warp0 = '''
+warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
+verb=1 nliter=0
+'''
+
+getmask = 'add scale=1,-1 ${SOURCES[1]} | mask min=0 | dd type=float'
+
+def psrect(rect):
+    return '''
+    math min=${SOURCES[2]} max=${SOURCES[1]}
+    output="sqrt(1+%d*(1/min^2-1/max^2)*input)" | dd type=int
+    ''' % rect
+
+def pprect(rect):
+    return '''
+    math min=${SOURCES[2]} max=${SOURCES[1]}
+    output="sqrt(1+%d*(1/max^2-1/min^2)*(1-input))" | dd type=int
+    ''' % rect
+
+balance = '''
+nsmooth1 rect=${SOURCES[1]} |
+abalance rect1=100 order=100 other=${SOURCES[2]}
+'''
+
+def simil(rect1=1,rect2=1):
+    return '''
+    similarity other=${SOURCES[1]} rect1=%d rect2=%d
+    ''' % (rect1,rect2)
+
+def warping(niter,rect1=1,rect2=1,rect3=1):
+    return '''
+    warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
+    warpout=www.rsf
+    verb=1 nliter=%d noamp=1 rect1=%d rect2=%d rect3=%d > ${TARGETS[1]} &&
+    warpadd < ${SOURCES[3]} add=www.rsf > $TARGET &&
+    rm www.rsf
+    ''' % (niter,rect1,rect2,rect3)
+
+def pick(min2,max2,rect1=1,rect2=1,rect3=1,an=0.5):
+    return '''
+    window min2=%g max2=%g | 
+    pick rect1=%d rect2=%d rect3=%d an=%g |
+    window''' % (min2,max2,rect1,rect2,rect3,an)
+
+def warpscan(ng,g0,gmax,rect1=1,rect2=1,rect3=1,rect4=1):
+    dg = (gmax-g0)/(ng-1)
+    return '''
+    warpscan other=${SOURCES[1]} niter=100
[…]

### 2018-04-07 chapter-locfreq/vecta/radius2.py

@@ -1,0 +1,113 @@
+from rsf.proj import *
+
+def radius2(high, low,               # initial high-resolution and legacy images
+            niter,                   # number of corrections
+            c,                       # step length for radius corrections. Can be type int or float for constant c 
+                                     #      or type array for changing c.
+            bias=-15, clip=30,       # bias and clip for display
+            rect1=40, rect2=80,      # radius for local frequency calculation
+            maxrad=1000,             # maximum allowed radius
+            theor=True,              # use theoretical smoothing radius
+            scale=9,                 # scale for theoretical smoothing radius
+            initial=10,              # initial value for contant smoothing radius 
+            minval=0, maxval=25,     # minval and maxval for freqdif-filt display
+            titlehigh="Hires",       # high title
+            titlelow="Legacy",       # low title
+            it=0):                   # correction number (from newarp.py)
+
+    if type(c) is float or type(c) is int:
+        c = [c]*niter
+
+    def seisplot(name):
+        return 'grey title="%s"'%name
+    
+    locfreq = '''iphase order=10 rect1=%d rect2=%d hertz=y complex=y | 
+                 put label="Frequency" unit=Hz'''%(rect1,rect2)
+
+    def locfreqplot(name):
+        return 'grey mean=y color=j scalebar=y title="%s" '%name
+
+    freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
+
+    def freqdifplot(num):
+        #return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %d" ''' %num
+        #return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %d" 
+        #          clip=%d bias=%d minval=%d maxval=%d''' %(num,clip,bias,minval,maxval) 
[…]

### 2018-04-13 book.tex
added junk to migdec yay
formatting and junk for SEG abstract
Thesis updates
geofigs

@@
 \cleardoublepage
+\setfigdir{Fig}\GEOpaper{chapter-locfreq}{chapter-locfreq}	\include{chapter-locfreq/paper}
+\cleardoublepage
+\setfigdir{Fig}\GEOpaper{chapter-merge}{chapter-merge}	\include{chapter-merge/paper}
+\cleardoublepage
+\setfigdir{Fig}\GEOpaper{chapter-mighes}{chapter-mighes}	\include{chapter-mighes/paper}
+\cleardoublepage
+\setfigdir{Fig}\GEOpaper{chapter-conclusion}{chapter-conclusion}	\include{chapter-conclusion/paper}
+\cleardoublepage
 %% end of paper list

### 2018-04-13 chapter-conclusion/paper.tex
geofigs

--- 2018-04-07 chapter-mighes/paper.tex
@@
-\title{Migration deconvolution}
+\title{Conclusions}
 \author{Sarah Yvonne Greer}
 \maketitle
-
-%\title{Migration deconvolution using non-stationary matching}
-%\title{Approximating the inverse Hessian to enhance migration using non-stationary matching operators}
-%\title{Improving migration resolution by approximating the Hessian using non-stationary matching operators}
-%\title{Improving migration resolution by approximating the Hessian using non-stationary amplitude and frequency matching operators}
-%\title{Improving migration resolution using non-stationary amplitude and frequency matching operators}
-%\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
-%\title{Approximating the inverse Hessian to enhance migration using linear non-stationary matching operators}
-%\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
-\newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
-\maketitle
-%\inputdir{sigsbee}
-\inputdir{sigsbee2}
-\begin{abstract}
-    We propose using two non-stationary operators to represent the amplitude and frequency variations in the least-squares Hessian to account for the principal differences between conventional and least-squares migrated images.
-    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration,
-    and it increases the resolution and amplitude fidelity of the migrated image.
-%    When applying these transformation to a conventionally migrated image, it improves the image resolution.
-    %We propose an approach of approximating the inverse Hessian operator in application to migration deconvolution. 
-    %Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the Hessian---one to account for amplitude variations, and the other to account for frequency variations.
-    %Successful results were achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
-    Successful results are achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
-\end{abstract}
-
-\section{Introduction}
-%However, the process may be computationally expensive as it typically involves multiple iterations of forward modeling and remigrating the data. 
-%Least-squares migration \cite[]{lsm} \ldots
-Least-squares migration can produce an accurate migrated seismic image.
-However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling and migration. 
-%However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling, calculating the residual misfit, performing a conventional migration, and updating the model.
-%At the cost of approximately one iteration of least-squares migration, 
-Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%These artifacts are due to the fact that standard migration applies only a single adjoint operation \cite[]{pvi}.
-%Least-squares migration can help alleviate 
-This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by 
-finding the least-squares model solution,
-standard migration amounts to applying a single adjoint operation \cite[]{pvi}. 
-%Conventionally migrated seismic images generally contain migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%A standard way to alleviate these artifacts 
-%is an advanced way of producing an accurate image of the subsurface \cite[]{lsm}.
-%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%Conventional migration is not , as such, 
-%conventionally migrated images generally suffer from migration artifacts affecting amplitude fidelity and resolution. 
-%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%solving the least-squares normal equations, 
-%While this can be a good approximation to the inverse, and as such, is not a true inverse operation.
-
-Various methods have attempted to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
-%Migration deconvolution attempts to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
-Here, $\mathbf{L}$ is a standard forward-modeling operator, and $\mathbf{L}\tran$ is its adjoint---the migration operator.
-These methods usually take the form of two approaches---for preconditioning before least-squares migration and as a single operation to improve accuracy of a conventionally migrated image.
-%This filter approximates the inverse Hessian operator, and can be approximated by solving a data matching problem between two conventionally migrated images. 
-%Migration deconvolution \cite[]{poststack,prestack}
-Previously, this has been done by 
-migration deconvolution \cite[]{poststack,prestack},
-%stochastscally approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{diagamp}, 
-approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp},
-and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
-%This has traditionally been done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different operations are specified in each region \cite[]{seiinv}.
-This traditionally is done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different matching filters are specified in each region \cite[]{seiinv}.
-
-In this paper, we take a different approach. 
-We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
-%Because of this, we choose to approximate the  
-Here, we treat this as a data matching problem between two conventionally migrated images, and find separate operations to account for both amplitude and frequency variations.
-%However, we propose using two separate non-stationary operators---one to account for amplitude variations, and the other to account for frequency variations.
-
-%This has advantages over previous methods as, instead of using a sliding window approach, we rely on local seismic attributes to measure and apply amplitude and frequency balancing operations \cite[]{attr}.
-This approach enables us to rely on local seismic attributes to measure and apply amplitude and frequency balancing operations instead of using a sliding window approach \cite[]{attr}.
-This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
-%of local seismic attributes, and for 
-%In the past, 
-Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each 
-%transformation 
-operation
-can be adjusted independently, which is another advantage of the proposed method.
-To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}. 
-%Least squares migration is more computationally expensive than conventional migration, but it produces a more accurate image of the subsurface---conventional migrated images generally 
-%suffer from migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%exhibit less correct amplitude and frequency content. 
-%applying a filter to a conventional migrated image to produce a more accurate image with less computational cost than least-squares migration. 
-%Previously, this has been done using non-stationary, or spatially and temporally variant, matching filters in a sliding-window approach.
-
-%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the migration-deconvolution image as a starting moel (red).}
-%Once finding the forward operation,
-\section{Theory}
-The goal of least-squares migration is to find the image, $\hat{\mathbf{r}}$, that minimizes
-\begin{equation}
-p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
-\end{equation}
-where $\mathbf{L}$ is the forward modeling operator, representing seismic wave propagation through the subsurface, and $\mathbf{d}$ is the acquired seismic data.
-This can be solved by the least-squares formulation to find $\hat{\mathbf{r}}$:
-\begin{equation}
-        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d}\;,
-        \label{eq:ls}
-\end{equation}
-where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, 
-%where $\mathbf{L}\tran$ is the migration operator, 
-and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
-%Equation (\ref{eq:ls}) is usually solved iteratively, where each iteration costs %by multiple iteration of forward modeling
-%where each iteration involves 
-%On the other hand, conventional migration
-Equation (\ref{eq:ls}) is usually solved iteratively, typically requiring multiple iterations of forward modeling and remigrating the seismic image \cite[]{wem,xue16}. 
-Conventional migration is less computationally expensive:
-\begin{equation}
-        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d}.
-        \label{eq:mod}
-\end{equation}
-%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
-However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images \cite[]{dutta14}. 
-By combining equations (\ref{eq:ls}) and (\ref{eq:mod}), it is evident that
-\begin{equation}
-        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{0} \;,
-\end{equation}
-%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
-so $\mathbf{m}_0$ is a distorted version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by finding a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
-
-%The least squares image, $\hat{\mathbf{r}}$
-
-%Here the forward modeling operator, and subsequently the migration operator, $\mathbf{L}\tran$, depends on the type of migration; RTM vs Kirchhoff\ldots
-
-%We can represent acquired seismic data, $\mathbf{d}$, as a forward-modeled version of the Earth's true reflectivity, 
-%\begin{equation}
-%        \mathbf{d} = \mathbf{L}\mathbf{r},
-%\end{equation}
-%where $\mathbf{r}$ is the Earth's reflectivity and $\mathbf{L}$ is the forward modeling operator CITE. 
-%Least-squares migration can produce a close approximation to the Earth's reflectivity by finding the least-squares solution,
-%\begin{equation}
-%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d},
-%        \label{eq:ls}
-%\end{equation}
-%but it can be computationally expensive as it typically requires multiple iterations of forward modeling and remigrating the seismic image CITE. 
-%Conventional migration is less computationally expensive:
-%\begin{equation}
-%        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d},
-%        \label{eq:mod}
-%\end{equation}
-%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
-%However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images CITE. 
-%By combining equations \ref{eq:ls} and \ref{eq:mod}, it is evident that
-%\begin{equation}
-%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{1},
-%\end{equation}
-%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
-%
-%In order to find $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of CITE. We begin by forward modeling the migrated image, $\mathbf{m}_9$:
-%\begin{equation}
-%        \mathbf{d}_2 = \mathbf{L}\mathbf{m}_0.
-%\end{equation}
-%We then remigrate $\mathbf{d}_2$:
-%\begin{equation}
-%        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_2 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0,
-%\end{equation}
-%and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
-%\begin{equation}
-%        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1.
-%\end{equation}
-%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
-%
-
-\section{Method}
-%Here, we follow the forward-modeling and remigration approach of
-
-In order to approximate $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of \cite{imop}. 
-We begin by forward modeling the migrated image, $\mathbf{m}_0$:
-\begin{equation}
-        \mathbf{d}_1 = \mathbf{L}\mathbf{m}_0 \;.
-\end{equation}
-We then remigrate $\mathbf{d}_1$:
-\begin{equation}
-        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_1 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0 \; ,
-\end{equation}
-and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
-\begin{equation}
-        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1 \;.
-\end{equation}
-%The inverse Hessian operator that must be applied to $\mathbf{m}_0$ to correct it closer to the least-squares migrated image, $\hat{\mathbf{r}}$, therefore, can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
-%Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
-Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
-This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.
-%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
-
-%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), migration migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
-%Typically, the differences between least-squares migrated images and conventionally migrated images amount to only amplitude and frequency changes, 
-    Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations.
-    Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
-    %We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined. 
-    We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
-    We then invert our approximation to the Hessian and apply it to $\mathbf{m}_0$ to correct the amplitude and frequency content of the migrated image.
-
-\subsection{Amplitude operator}
-First, we choose to find an amplitude balancing operation that, when applied to $\mathbf{m}_0$, balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$. 
-%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
-%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
-This operation can be equated to a trace-by-trace multiplication of a diagonal matrix to each trace, where the matrix changes for every trace.
-%The matrix $\mathbf{A}$ changes 
-We estimate it by first calculating the amplitude envelope of the traces in $\mathbf{m}_0$ and $\mathbf{m}_1$, and then smoothly dividing them.
-The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
-%to find the diagonal weighting operator 
-%to balance the amplitudes of each trace.
-%that balances the amplitudes of each trace of $\mathbf{m}_0$ to match with $\mathbf{m}_1$.
-%This is a linear diagonal weighting operator
-%This linear operator only has elements across the diagonal terms, so it is trivial to find the inverse operator. 
-%Therefore, this operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
-%Therefore, the operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
-Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.
-
-%\multiplot{2}{a0,a1}{width=1.0\columnwidth}{The forward amplitude balancing weights, $\mathbf{A}_0$ (a) and $\mathbf{A}_1$ (b).}
-%\plot{rect10}{width=1.0\columnwidth}{The smoothing radius, which represents the number of samples in both spatial dimentions, that $\mathbf{m}_0$ must be smoothed over in a pyramid weight to balance local frequency content with $\mathbf{m}_1$.
-This represents the forward smoothing operation, $\mathbf{S}$.}
-
-\subsection{Frequency operator}
-In addition to amplitude corrections, we also attempt to account for the decrease in resolution of a conventional migrated image compared to its corresponding least-squares migrated image. 
-This loss in resolution can be equated to the fact that $\mathbf{L}\tran\mathbf{L}$ acts as a blurring operator, where the conventional migrated image is a blurred version of the ideal least-squares migrated image \cite[]{poststack}.
-%where each individual value
-We choose to approximate this blurring using non-stationary triangle smoothing.
-
-%This means that the 
-We begin by first calculating the local frequency of the two initial images \cite[]{attr}. 
-Local frequency is a temporally and spatially varying frequency attribute that smoothly varies across the image without windows.
-Our goal is to find a transformation that we can apply to $\mathbf{m}_0$ that matches the local frequency content with $\mathbf{m}_1$. 
-To do this, we propose using non-stationary triangle smoothing. 
-%This approach involves finding and applying a non-stationary smoothing radius, which is the amount of samples, in time, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance local frequency content with $\mathbf{m}_1$.
-This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.
-
-We find the smoothing radius iteratively using the method of \cite{locfreq}, with a modification that allows the smoothing radius to be calculated in both spatial directions. 
-Essentially, this is found by choosing an initial guess of a smoothing radius, $\mathbf{R}^{(0)}$, and updating it iteratively such that 
-    \begin{equation}
-        \label{eq:it}
-\mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \left [ \mathbf{F}[\mathbf{S}_{\mathbf{R}^{(i)}} \mathbf{m}_0] - \mathbf{F}[\mathbf{m}_1] \right ]\;,
-    \end{equation}
-    where $\mathbf{F}$ is the local frequency operator, $\mathbf{S}_{\mathbf{R}^{(i)}}$ is the smoothing operator of radius $\mathbf{R}$ at the $i$th iteration, and $\alpha$ is a scalar constant that represents the step length.
-    After a small number of iterations, the smoothing operator is found that, once applied to $\mathbf{m}_0$, balances local frequency content with $\mathbf{m}_1$.
-
-%    Unlike $\mathbf{A}$, the smoothing operator, $\mathbf{S}$, is more challenging to invert 
-%    since it is generally a banded, but not diagonal, operator and physically represents the mixing of each data point with other nearby data points.
-    %This smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric. 
-    %However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create false high-frequency data if inverted incorrectly without regularization.
-%\multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$.
-This represents the forward smoothing operation, $\mathbf{S}$.}
-
-    \subsection{Calculating the inverse Hessian}
-    Now that we have found the forward operators that separately balance amplitude and frequency content from $\mathbf{m}_0$ to $\mathbf{m_1}$, where $\mathbf{m}_1 \approx \mathbf{H} \mathbf{m}_0$, we want to find what combination of $\mathbf{A}$ and $\mathbf{S}$ best approximates $\mathbf{H}$.
-    %An advantage of finding $\mathbf{A}$ and $\mathbf{S}$ separately is that they can each be individually adjusted 
-    %the inverse of this operator such that $\hat{\mathbf{r}} = \left (\mathbf{H} \right )^{-1} \mathbf{m}_0$.
-    Since $\mathbf{H} = \mathbf{L}\tran\mathbf{L}$ is symmetric, we want our approximation of $\mathbf{H}$ to be as close to symmetric as possible.
-    Therefore, we define $\mathbf{H}$ as
-    \begin{equation}
-            \mathbf{H} \approx \mathbf{A}^{\sfrac{1}{2}}\mathbf{S}\mathbf{A}^{\sfrac{1}{2}} \;,
-    \end{equation}
-            %\mathbf{H} = \frac{1}{2}\left ( \mathbf{A}\mathbf{S} + \mathbf{S}\mathbf{A} \right )
-    where $\mathbf{A}$ is the operator that balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, and $\mathbf{S}$ is the operator that balances the local frequency content of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, both defined previously.
-    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric, since both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
-    %One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
-    Splitting up our approximation to the Hessian into two separate operators allows us to control how much of each operation and the order of each operation goes into correcting the image, and see how it affects the resulting image.
-%    \begin{equation}
-%        \mathbf{H} = \mathbf{A}_1^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}_0^{\sfrac{1}{2}}\;,
-%    \end{equation}
-%    where $\mathbf{A}_0$ is found by balancing amplitudes between $\mathbf{m}_0$ and $\mathbf{m}_1$, $\mathbf{S}$ is calculated by finding the smoothing operator that balances the local frequency content between $\mathbf{m}_0$ and $\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_1$, and $\mathbf{A}_1$ is found by balancing amplitudes between $\mathbf{S}\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_0$ and $\mathbf{m}_1$.
-%    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be close to symmetric. 
-%    However, note that here $\mathbf{H}$ is not quite symmetric, but since $\mathbf{A}_0$ and $\mathbf{A}_1$ should be very similar, it is nearly symmetric.
-%    One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
-%
-    Now that we have found the forward Hessian, $\mathbf{H}$, such that $\mathbf{H}\mathbf{m}_0 \approx \mathbf{m}_1$ using data matching operators, we want to find the inverse of this operator, $\mathbf{H}^{-1}$, such that $\hat{\mathbf{r}} \approx \mathbf{H} ^{-1} \mathbf{m}_0$ provides us with the least-squares image.
-    This is found as
-    \begin{equation}
-            \mathbf{H}^{-1} \approx \left ( \mathbf{A}^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}^{\sfrac{1}{2}} \right )^{-1} = 
-            \mathbf{A}^{\sfrac{-1}{2}} \mathbf{S}^{-1} \mathbf{A}^{\sfrac{-1}{2}}\;.
-            \label{eq:invh}
-    \end{equation}
-
-    Since the amplitude operators only contain diagonal terms, they are simple to invert. 
-    %However, the smoothing operator, $\mathbf{S}$, is more challenging to invert. 
-    %While smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric,. 
-    However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
-    Therefore, $\mathbf{S}^{-1}$ must be calculated with care to ensure the inverted data is physically plausible. 
-    We iteratively invert $\mathbf{S}$ using shaping regularization \cite[]{shap}, where the shaping operator is a bandpass filter picked to ensure the passband contains only physically possible frequencies for the given data set.
-    The cost of applying our approximation to $\mathbf{H}^{-1}$ in equation (\ref{eq:invh}) is $\mathcal{O}(N)$, where $N$ is the image size. 
-    The constant is small, typically around 10 for the number of iterations, and the calculation and application of this approximation is computationally insignificant compared to one iteration of least-squares migration.
-%is far less computationally expensive than one iteration of least-squares migration.
-    %The constant is 
-    %It is a diagonally-dominant operator
-    %The amplitude operator accounts for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms of the forward Hessian operator.
-    %Our approximation to the forward Hessian operator turns out to be diagonally-dominant, where the amplitude operators account for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms.
-
-%This allows us to find an operator that effectively balances the local frequency content of $\mathbf{m}_0$ to match with $\mathbf{m}_1$. 
-%Next, we need to find the inverse of this operation to 
-%Since the operation is non-stationary, it is applied in the time domain
-
-%we follow the approach of CITE. This approach uses non-stationary triangle smoothing. for finding the smoothing radius that 
-%
-%to increase the resolution of the
-
-%    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
-
-\section{Example}
-
-%\multiplot*{3}{mod-w3,image0-w3,migdec-w3}{width=0.66\columnwidth}{The Sigsbee model reflectivity (a), the first migrated image (b), and the corrected migrated image (c).}
-    We demonstrate the effectiveness of this method on the 2D Sigsbee model. %reverse-time migrated 
-    The Sigsbee2A 2D synthetic data set was created to mimic the geology of the Sigsbee escarpment in the Gulf of Mexico \cite[]{sigsbee}.
-    %In this example, we use reverse-time migration as our migration operator.
-    %* Zhiguang---Insert information about migration specifics (shot/receiver spacing, absorbing boundary conditions, etc.) *
-    A fixed-spread acquisition survey is generated, which consists of 301 shots spaced every 122 m.
-    The source wavelet for generating the synthetic data is a Ricker wavelet centered at 10 Hz.
-    The record length of the synthetic data is 10 s with a time step of 4 ms.
-We use reverse-time migration (RTM) as our migration operator.
-%\plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image.}
-
-    We begin with the sub-surface reflectivity model (Figure \ref{fig:mod}) and migration velocity model (Figure \ref{fig:vel-migration}).
-    Next, we forward model the seismic data and migrate it to get our first conventionally migrated image, $\mathbf{m}_0$ (Figure \ref{fig:image0}). 
-    Then, we forward model $\mathbf{m}_0$ and remigrate that data to get $\mathbf{m}_1$ (Figure \ref{fig:image1}).
-    This provides us with the two images, $\mathbf{m}_0$ and $\mathbf{m}_1$, that we can use to find the operation $\mathbf{H}$ that maps $\mathbf{m}_0$ to $\mathbf{m}_1$.
-
-    Next, we calculate and apply the data matching operations as described in the previous section. 
-    The forward amplitude balancing weight, $\mathbf{A}$, is shown in Figure \ref{fig:a0}.
-    The calculated radius for the forward smoothing operation is shown in Figure \ref{fig:rect10b}.
-    After applying these two operators to $\mathbf{m}_0$ as described by equation (\ref{eq:invh}), we produce the corrected migrated image, as shown in Figure \ref{fig:migdec-shap}.
-    This corrected image better represents the subsurface reflectivity than the conventionally migrated image (Figure \ref{fig:image0}), as it exhibits more correct amplitude content and higher resolution comparable with the reflectivity model.
-
-    Figure \ref{fig:mod-w3,image0-w3,migdec-w3} shows a windowed section of the reflectivity model, the conventionally migrated image, and the corrected migrated image.
-    %The corrected migrated image is clearly of higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.
-    The corrected migrated image exhibits clearly higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.
-
-%    Figure \ref{fig:spec2} shows the frequency content of the conventionally migrated image and the corrected migrated image. 
-%    The corrected migrated image has a broader bandwidth and a flatter spectra than the conventionally migrated image, and generally recovers the higher frequency data that was lost during conventional migration.
-%    However, it does lose some low frequency content as a result of the process, 
-%    %Additionally, the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
-%    but the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
-%    is still a better approximation of the model than that of the conventionally migrated image.
-%    %is a better approximation of the model than that of the conventionally migrated image.
-%
-
-    In addition to directly applying this operator to the conventionally migrated image to improve resolution, this operator can be used as a preconditioner in iterative least-squares migration.
-    In this case, the corrected migrated image could be used as an initial model for least-squares migration for faster convergence.
-
-\section{Conclusions}
-%Conventionally migration involves 
-%A higher resolution least-squares migrated image 
-%This method does not involve dividing the data into windows 
-Least-squares migration can produce an accurate migrated image, but it is more computationally expensive than conventional migration.
-In this paper, we apply an approximate inverse Hessian operator to a conventional migrated image to approximate the least-squares migrated image.
-Since the primary differences between least-squares migration and conventional migration amount to amplitude and frequency variations, we approximate the forward Hessian by calculating frequency and amplitude matching operators.
-The amplitude matching operator is found by calculating the amplitude envelopes of migrated and remigrated images and smoothly dividing them, and the frequency matching operator is found using an iterative algorithm and non-stationary smoothing.
-The Hessian is approximated by a combination of these two operators to ensure symmetry.
-This method involves a windowless approach and is cheap to calculate and apply.
-Additionally, by defining the Hessian with two separate operators, we can examine, and control, the ``ingredients'' of the Hessian operator, and see how changing them impacts the final image.
-
-After the forward Hessian is calculated, we invert it iteratively using shaping regularization, and apply it to the conventionally migrated image to get an approximation of the least-squares migrated image.
-Successful results are achieved on the 2D Sigsbee synthetic model with reverse-time migration as the migration operator.
-
-%\plot{spec2}{width=0.85\columnwidth}{The frequency content of the conventionally migrated image (blue solid), and the corrected migrated image (red dashed).}
-
-\inputdir{sigmoid}
-%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the corrected migrated image as a starting model (red).
-Here, the migration operator is post-stack Kirchhoff migration.}
-
-\section{Acknowledgements}
-        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
-The examples in this paper can be reproduced using the Madagascar open-source software package \cite[]{madagascar}.
-
-%\inputdir{kir}
-
-\onecolumn
-
-\bibliographystyle{seg}
-\bibliography{SEG,migdec}
-
-%        In seismic processing we have the operation of migration, which is a linear transform, and we can think of it as the adjoint of modeling.
-So if you know the velocity, and you have reflectivitym, so going from reflectivity to data is a linear transformaiton the adjoint of that is migration.
-%
-%        And then so reflectivity
-%        d = Lm
-%        So migraziton would be the adjoint applied to the data
-%        And if we try to do inverse, it would be:
-%        so this is LSM
-%
-%        And normally we would do it with iterations, so doing conjugate gradients or some sort of iterative method, where we approximate its inverse using iterations.
-But it is still expensive because in each iteration we need to do modeling and migration, and that's an expensive process.
-%        So, the idea is instead of computing this exactly, we approximate it.
-%        This is called migrtion deconvolution.
-%
-%        Now, what does it actrually do?
-%        SO the interesting part about the operations of modeling and migration here is that when you do them in term, you do modeling and migfration, so theoretixallty, it's an operation that does somethjing with the input, so you put in one image and get another image.
-%        But the other image does not have a shift---things will return to the same place. So, mostly it amounts to scaling, so different scale, and there is also some smearing.
-%
-%        SO if for example you put this as an input, you'll get the same points but they'll be smeared a little bit, but they'll be in the same place.
-%
-%        There is some smearing and there is some scaling. So that's what this is basically trying to correct.
-%        So, we go from here to here, and there are different ways people tried to do it before.
-%        One was just to focus on the scaling, and then so you're looking at the diagonal matrix to apply some scale to compensate.
-%        The other was to use theory to try to derive theoretically what this should be, and there are other theories, but they are based on ideal situations, so you don't consider the fact, for example, that the data that you have is not infinite so it has a finite extent.
-%        SO the theory is good, but it's idealized to look that everything is continuous, infinite, which is not the case.
-So part of what we see here when we look at the smearing, so part comes from the nature of modeling and migraiton, which we know theoretically, but part of it is from the fact that the data are not perfect, so we have limited extent, and discrete non-continuous data.
-So the theory may work in practice and get most of it, but not all of it because it is idealized.
-%        So it's useful, but it's not ??? 27:45
-%
-%        So Antoine in CSM\ldots
-%        This year he shows an application that is specifically for RTM, but the idea comes from his older paper which is 
-%        And that was just simply that you \ldots
-%        This was done previously to look for just the scaling.
-%        You have sort of training images.
-You can use this M ans one of the training.
-But you can also create a bunch of the other ones.
-If you create a bunch of synthetic you have a bunch of reflectivity models, but it's sort of an open question of how you do it.
-So you can use spikes, reflectors, random, but in some way generate a bunch of those but you apply modeling and migration to it.
-And now you have example inputs and example outputs, and you want the inverse of this.
-SO you want to find out how to go back from this to the theoretical.
-And you cannot use too many bc it get expensive and it is easier to do LS migration with iterations.
-Computatinoally, the challenge is how to figure out what this is without using too many training images.
-%        Instead of the simple scale, he looks for a non-stationary matching filter. Now if we learn what this is, you can just apply it once, and there are also\ldots
-%        Single iteration migration, but they mean doing it once
-%        Find out how to approximate this inverse and they apply it to compensate. But you can also use it as a preconditioner.
-%        So the other use is, so say I'm still going to run iterations, but I'll but this correction inside, and then instead of 10 iterations, maybe I can use it fewer. 
-%
-%        So there are differences between the asdasd of preconditioned conjugate gradients.
-Some of them use m, and some split m into two parts.
-So we can say that you have instead of r and you're looking for x, and you're inverting afjsdkl;, so \ldots 36:40
-%        In any conjugate gradients, you can precondition by making it run faster by making the inverted matrix closer to the identity.
-So there is a dual purpose to this --- to find something you can apply once but you can also use it as a precondioner if you want to do it more than one time.
-%        So in this other paper, . . .
-%        The reason I mention it to you now for what you did for the matching and triangle filters, so we have another way to describe this kind of a transformation which is fairly robust, and it may work in this application.
-Basically we have scaling and smearing which is like legacy and high-resolution.
-So the better question is to find a good example to try.
-I'm not sure if we have anything in Madagascar yet.
-We have modeling and migration, so we need to find some kind of example of applying modeling and migration so we can look how to measure the transformation for that.
-%        The interesting question is if you have scaling and you have smearing, maybe with variable radius traingle filters, so the two opeations you need both of them but they don't commute.
-So if you do scaling first and smearing second it's not the same if you do smearing first and then scaling.
-When we are dealing with this we know that it needs to be symmetric.
-%
-%        There is scaling with the weight and triangle filtering.
-It can be this, or this.
-So we are not scaling symmetrically.
-Or maybe this.
-So if we start doing something like that, it becomes non-linear, so if we have scaling twice we cannot use linear inversion to find the scaling.
-So it actually makes it more interesting, so now we need to think how to linearize it so if we have something like that for example, we can say that we want to find maybe an inital scaling; maybe I'll take it to be one initial and 43:15
-%        and the other term you neglect to get\ldots
-%        Now this one is linear, but it has an interesting combination here from the left side 
-%        So now it's a linear problem can be solved with regularization but not the same one as before. So it makes the whole problem a little more interesting
-%
-%        And then potentially, even if it's not that, so say we go back to legacy and high resolution, so we know there is scaling and there is smearing, but nothing says that scaling has to be on this side or on this size, so it can be both or it can be different on this side and the other size, so it makes it a more general problem with potentially more interesting solutions.
-%
-%        So in terms of ideas there is not a lot there, besides what I have told you, but you can read it and follow the references to other papers.
-So they put some work into implementing it.
-But if we make it work with scaling and smoothing, it would actually me a much cleaner implementation.
-Because they have to, So I suspect that what Antoine Guitton had to do to implement it was breaking everything into windows, some overlap, and then finding filters in each window and trying to change them, so it's not very stable and it's a bit messy.
-So if it works, it works, but I think we can find a cleaner result.
-and also you know if you break it into scaling and smearing, you know the ingredients of what happens in there, so you have a better understanding.
-%

### 2018-04-13 chapter-intro/paper.tex
Thesis updates
geofigs

@@
 
+%Data matching problems are prevalent in many applications of seismic data processing.
+Data matching is a conceptually simple problem that is present in many computational geophysics applications. 
+Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
+This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
+These must be properly matched, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted.
+
+Many other examples of data matching are prevalent in geophysical applications, such as timelapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.
+
+In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
+
+%However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
 \subsection{Background}
+Seismic data contains fundamentally non-stationary variations in attributes such as frequency and amplitude content.

### 2018-04-13 chapter-merge/paper.tex
Thesis updates
geofigs

@@
-\title{Introduction}
-\author{Sarah Yvonne Greer}
+\title{Matching and merging high-resolution and legacy seismic images}
+\author{Sarah Greer and Sergey Fomel, The University of Texas at Austin}
+
+%\righthead{Matching and merging seismic images}
+%\ms{GEO-2017-0238}
 \maketitle
 
-\subsection{Background}
+\begin{abstract}
+    When multiple seismic surveys are acquired over the same area using different technologies that produce data with different frequency content, it may be beneficial to combine these data to produce a broader bandwidth volume.
+    We have developed a workflow for matching and blending seismic images obtained from shallow high-resolution seismic surveys and conventional surveys conducted over the same area. 
+    The workflow consists of three distinct steps: 
+    (1) balancing the amplitudes and frequency content of the two images by non-stationary smoothing of the high-resolution image, 
+    (2) estimating and removing variable time shifts between the two images, and 
+    (3) blending the two images together by least-squares inversion. 
+    Our workflow is applied successfully to images from the Gulf of Mexico.
+
+\end{abstract}
 
 \section{Introduction}
+    Modern high-resolution seismic acquisition systems, such as P-cable \cite[]{pcable,tip}, can produce detailed images of the subsurface at shallow depths. 
+    These images often need to be compared with those previously produced using legacy images from conventional seismic acquisition. 
+    In comparison with high-resolution images, conventional images have generally lower frequency content and correspondingly lower resolution, but better signal content at greater depth. 
+    To reconcile the differences between the two types of images, they need to be properly matched.
 
-Modern high-resolution seismic acquisition systems, such as P-cable
-\cite[]{pcable,tip}, can produce detailed images of the subsurface at
-shallow depths. These images often need to be matched with those
-previously produced from legacy images using conventional seismic acquisition. In
-comparison with high-resolution images, conventional images have
-generally lower frequency content and correspondingly lower depth
-resolution, but better signal content with depth. In order to reconcile the
-differences between the two types of images, they need to be
-properly matched.
+    Analogous problems occur when interpreting images from multicomponent seismic acquisition. 
+    In particular, single-component PP and converted PS images often exhibit significantly different frequency content and need to be balanced for accurate registration \cite[]{hardage,multi,warp}.
 
-Analogous problems occur when interpreting images from multicomponent
-seismic acquisition. In particular, single-component
-PP and converted PS images often exhibit significantly different frequency content
-and different resolution and need to be balanced for accurate registration
-\cite[]{hardage,SEG-2003-07810784,warp}.
+    When multiple data sets are acquired over the same area using different technologies, it is likely that these data sets contain signal content from different frequency bands, which correspondingly contain unique information about the subsurface.
+    In order to utilize all available information, it may be beneficial to produce a consolidated broad-bandwidth volume that combines these data sets.
+    Many previous methods of seismic data merging have been developed for the purpose of increasing the spatial coverage of the merged volume by combining data from partially overlapping areas. 
+    This usually involves steps such as rebinning for data alignment, along with spectral and phase matching.
+    As a result, both the initial and resultant merged images poses similar signal characteristics, most notably spectral content \cite[]{kavery,gabor,supermerge}. 
+    However, previously \cite{freqmerge} are successful in applying a frequency domain merge to two separate seismic volumes over the same area to broaden the effective bandwidth.
 
-In this paper, we consider the problem of matching images obtained
-with different resolution. Using techniques borrowed from
-multicomponent image processing \cite[]{warp}, we propose a multistep
-approach. First, the two images are balanced in amplitude and
-frequency content. As a result, the resolution of the
-high-resolution image is degraded. Next, we measure shifts between
-images using local similarity
-scanning \cite[]{attr,timelapse}. Finally, when the images are aligned and 
-matched, we create a blended image using least-squares inversion.
+    In this paper, we consider the problem of matching seismic images obtained in the same area with different resolution. 
+    Using techniques borrowed from multicomponent image processing \cite[]{warp}, we propose a multistep approach. 
+    First, we balance the two images in amplitude and frequency content. 
+    As a result, the resolution of the high-resolution image is temporarily degraded to match the resolution of the legacy data. 
+    Next, we measure shifts between images using local similarity scanning \cite[]{attr,timelapse}.
+    Finally, when the images are aligned and matched, we create a blended image using least-squares inversion in the time domain. 
+    The blended image has a wider frequency bandwidth than the two initial images, along with coherent signal content with depth from the legacy image and detailed shallow coverage from the high-resolution image.
 
-%We test the proposed approach using data from the Gulf of Mexico. 
     We test the proposed approach using data from the Gulf of Mexico. 
-A 2D image is used to demonstrate the method, and a 3D
-example is provided at the end.
+    A 2D image is used to illustrate the method, followed by an example applied to 3D data.
 
     \inputdir{apache}
-
-%\multiplot{3}{legacy,hires,merge2-reverse}{width=1.0\columnwidth}{The initial legacy (a) and high-resolution (b) images.
-%The merged image (c) is the final product of the proposed workflow: the combination of both the legacy and high-resolution images.}
+    \multiplot{3}{legacy,hires,merge2-reverse}{width=0.45\columnwidth}{The initial legacy (a) and high-resolution (b) images.
+    The merged image (c) is the final product of the proposed workflow: the combination of both the legacy and high-resolution images.}
 
@@
 
-The initial legacy and high-resolution example images are shown in Figures~\ref{fig:legacy}
-and \ref{fig:hires}, respectively. The images show similar structures, particularly at shallow depths, but with
-strikingly different resolution. The main difference comes from the
-broader frequency bandwidth of the high-resolution image in comparison
-with that of the legacy image. Therefore, our first step in comparing
-the two images is balancing their spectral content.
+    The initial legacy and high-resolution example images are shown in Figure~\ref{fig:legacy,hires,merge2-reverse}. 
+    They both underwent standard marine processing flows, and are assumed to be optimally processed.
+    The images show similar structures, particularly at shallow depths, but with strikingly different resolution. 
+    The main difference comes from the broader frequency bandwidth of the high-resolution image in comparison with that of the legacy image. 
+    Therefore, our first step in comparing the two images is balancing their spectral content.
 
@@
 
-Analyzing the spectra of the legacy and high-resolution images, as
-%seen in Figure \ref{fig:nspectra}, it is clear that the
-seen in Figure \ref{fig:nspectra22-reverse}, it is clear that the
-high-resolution image has a wider range of frequencies with a higher
-dominant frequency than the legacy image. In order to match these
-images, our first step is to balance their spectral content. We can achieve 
-this by attenuating the high frequencies of the high-resolution image
-to match the lower frequency content of the legacy image. One approach
-to doing this is to apply a stationary bandpass filter to the
-high-resolution image. However, this does not take into account
-local frequency variations in each image caused by seismic wave attenuation.
-A more effective method is to apply a non-stationary filter using
-frequency information from both of the images. To accomplish this, we use a
-simple triangle smoothing operator with an adjustable radius. 
-To measure local frequencies and to estimate the smoothing radius, we
-utilize the concept of local seismic attributes, which
-involves measuring signal characteristics in a specified local region of data
-samples, rather than globally through the whole image or
-instantaneously at each point \cite[]{attr}.
+    Analyzing the spectra of the legacy and high-resolution images, as seen in Figure \ref{fig:nspectra}, it is clear that the high-resolution image has a wider range of frequencies with a higher dominant frequency than the legacy image.
+    In order to match these images, our first step is to balance their spectral content. 
+    We can achieve this by attenuating the high frequencies of the high-resolution image to match the lower frequency content of the legacy image. 
+    One approach to frequency balancing is to apply a stationary bandpass filter to the high-resolution image. 
+    However, this does not take into account local frequency variations in each image caused by seismic wave attenuation.
+    A more effective method, which accounts for temporally and spatially variable frequency content that is present in most seismic data, is to apply a non-stationary filter using frequency information from both images.
+    To accomplish this, we use a simple triangle smoothing operator with an adjustable radius. 
+    Here, the radius at each point is the amount of time, in seconds, that that specific data point gets averaged over in a triangle weight in the temporal direction.
+    We specifically look at local frequency \cite[]{attr}, which is a time-dependent frequency attribute, and can be thought of as a smoothed estimate of instantaneous frequency \cite[]{white}. 
+    For the procedure described in this paper, local frequency is a better-suited attribute than instantaneous frequency.
+    Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
+    Because the corresponding reflections between images may not be precisely aligned in time at this stage in the method, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
 
-%\multiplot{2}{nspectra,hires-smooth-spec}{width=0.68\columnwidth}{Spectra of legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}
+    \multiplot{2}{nspectra,hires-smooth-spec}{width=0.68\columnwidth}{Spectra for the entire image display of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}
 
-The justification for triangle smoothing is that it approximates
-Gaussian smoothing \cite[]{pvi}. The frequency response of the triangle smoothing filter \cite[]{pvi} is
+    The justification for triangle smoothing is that it is a simple approximation to Gaussian smoothing. The frequency response of the triangle smoothing filter \cite[]{pvi} is
     \begin{equation}
@@
     \end{equation}
-This frequency response closely resembles that of a Gaussian,
+    This frequency response resembles that of a Gaussian:
     \begin{equation}
@@
 
-Because we are smoothing the high-resolution image to match it with the legacy image, we can model the high-resolution frequencies, $S_h$, after the legacy frequencies, $S_l$, such that 
+    Because we are smoothing the high-resolution image to match it with the legacy image, we can relate the high-resolution frequencies, $S_h$, to the legacy frequencies, $S_l$, such that
     \begin{equation} 
@@
     \end{equation}
-Here, $\Delta t$ is the radius of smoothing, measured in samples,
-applied to the high-resolution image to match the frequency content with the legacy image
-at each sample. 
-%Measuring local frequencies varying across the two
-%images, we can also make the smoothing radius variable according to
-%equation~(\ref{eq:radius}).         % change this? redundant?
+    Here, $\Delta t$ is the radius of smoothing, measured in seconds, applied to the high-resolution image to match the frequency content with the legacy image at each sample. 
+    The calculated smoothing radius for this data set is shown in Figure \ref{fig:rect}.
+
+    \plot{rect}{width=0.75\columnwidth}{Calculated spatially and temporally variable smoothing radius.
+This represents the number of seconds in the temporal direction that the high-resolution image gets averaged over in a triangle weight to balance local frequency content with the legacy image at each sample.}
 
     We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
-The constant 12 in the equation is adjusted to achieve a better match.
-This effectively reduces the difference between the spectral content of the images.
-%, as shown in Figure \ref{fig:hires-smooth-spec}. 
-Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. After smoothing, the frequency difference is minimized. % Change?
+    Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
+    In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
+    Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. 
+    After smoothing, the frequency difference is minimized.
 
-%\multiplot{2}{freqdif,freqdif-filt}{width=0.85\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing the frequency content by non-stationary smoothing.}
+    This method works well for simple data sets with overlapping frequency content. 
+    However, more complicated data sets, as seen in the next example, may require additional steps for successful frequency balancing.
 
-%\plot{warpscan3}{width=\columnwidth}{Local similarity scan for the entire image. Red indicates a high similarity at that time shift between the two images.}
+    In addition to frequency balancing, we initially attempted accounting for wavelet phase differences between data sets at this step. 
+    However, we saw this had a negligible impact on the final result, so we decided not to include it in this method.
 
-% possibly skip
-%\plot{warppick3}{width=0.95\columnwidth}{Relative time shift for the entire image estimated by the trend of highest picked similarity from the local similarity scan.} % Why is the time shift generally less at depth?
-
-%\plot{nspectra22}{width=0.95\columnwidth}{The spectra of the legacy (blue dotted), high-resolution (red dashed), and merged (magenta solid) images.}
+    \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
 
 \subsection{Measuring time shifts}
-% Time variant shift?
 
-After balancing the spectral content, we attempt to account for potential time shifts of the
-high-resolution image relative to the legacy image, which can be
-caused by changes in acquisition and processing parameters. We measure
-this shift using local similarity scanning \cite[]{attr,
-  timelapse}. In this method, we detect the relative time shift by
-first calculating the local similarity at different time shifts of the
-high-resolution image relative to the legacy image
-\cite[]{timelapse}. %The result is shown in Figure \ref{fig:warpscan3}. From
-%this, the trend of greatest similarity is automatically detected
-From this, the trend of greatest similarity is picked
-and represents the relative time shift between the two images.
-%and represents the relative time shift between the two images, as shown in Figure \ref{fig:warppick3}.
+    After balancing the spectral content, we attempt to account for possible time shifts of the high-resolution image relative to the legacy image, which can be caused by changes in acquisition and processing parameters.
+    We measure this shift using local similarity scanning \cite[]{attr, timelapse}. 
+    In this method, we detect the relative time shift by first calculating the local similarity at different time shifts of the high-resolution image relative to the legacy image \cite[]{timelapse}. 
+    From this, the trend of the highest similarity is picked and represents the relative time shift between the two images.
 
-%\newpage
+    Next, we apply the estimated time shift to the original high-resolution image---the frequency content is only degraded for the purpose of finding the time shift that best aligns the signal content between the two images.
+    The differences between the two images before and after the time shift correction are shown in Figure \ref{fig:diff0,diff1}, and demonstrate a noticeably better match resulting from the time shift.
+    Similar results were achieved using amplitude-adjusted plane-wave destruction, which involves balancing amplitudes and temporally aligning the data sets simultaneously \cite[]{apwd}.
 
-Next, we apply the estimated time shift to the original high-resolution image in order to align the signal content between the two images.
-%The differences between the two images before and after the time shift correction are shown in Figure \ref{fig:diff0,diff1}, and demonstrate a better match resulting from the time shift.
-
-%\multiplot{2}{diff0,diff1}{width=0.67\columnwidth}{Difference between the legacy and smoothed high-resolution images before (a) and after (b) accounting for time shifts.
-Before warping, much of the signal content did not align in time, so coherent reflections were subtracted out.
-After warping, the reflections are more aligned, so much of the subtracted information is noise.}
+    \multiplot{2}{diff0,diff1}{width=0.6\columnwidth}{Difference between the legacy and smoothed high-resolution images before (a) and after (b) aligning the data sets.
+Before accounting for time shifts, much of the signal content did not align in time, so coherent reflections were subtracted out.
+After accounting for time shifts, the reflections are more aligned, so much of the subtracted information is noise.}
 
@@
 
-Since the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together 
-to combine the strengths of each while minimizing their weaknesses.
-%In addition to comparing the two images, we can also try to blend them together. 
+    Since the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together to combine the strengths of each while minimizing their weaknesses.
     We can achieve this by imposing two conditions. 
@@
     \end{equation}
-% should it be h hat?
-where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the
-legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$
-are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary
-smoothing specified by equation (\ref{eq:radius}). The formal solution of the
-least-squares problem~(\ref{eq:ls}) is
+    where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$ are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary smoothing specified by equation (\ref{eq:radius}).
+    The formal solution of the least-squares problem~(\ref{eq:ls}) is
     \begin{eqnarray}
-\nonumber
-\mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right) \\
-& = & \mathbf{h} +  \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,
-\mathbf{S}^T\,\mathbf{W_l}\left(\mathbf{l - W_l S h}\right)\;.
+        \mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right)\;.
         \label{eq:inv}
@@
 
-The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities 
-from each image. We estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy images's amplitudes with respect to the high-resolution image.
+    Alternatively, equation (\ref{eq:inv}) can be rearranged as
+    \begin{eqnarray}
+        \nonumber
+        \mathbf{b} & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\mathbf{W_h}^2\,\mathbf{h}+\mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\mathbf{h}-\mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\mathbf{h}+\mathbf{S}^T\,\mathbf{W_l}\mathbf{l}\right) \\
+    \nonumber
+        & = & \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,\left(\left(\mathbf{W_h}^2\,+\mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)\mathbf{h} + \mathbf{S}^T\mathbf{W_l}\left(\mathbf{l}-\mathbf{W_l}\mathbf{S}\mathbf{h}\right)\right) \\
+        & = & \mathbf{h} +  \left(\mathbf{W_h}^2 + \mathbf{S}^T\mathbf{W_l}^2\mathbf{S}\right)^{-1}\,
+        \mathbf{S}^T\,\mathbf{W_l}\left(\mathbf{l - W_l S h}\right)\;,
+        \label{eq:inv2}
+    \end{eqnarray}
+    which makes it evident that the merged image is simply the high-resolution image with some changes.
 
-%\plot{nspectra22-reverse}{width=0.90\columnwidth}{The spectra of the legacy (blue dotted), high-resolution (red dashed), and merged (magenta solid) images for the first data set.}
-% Dotted dashed solid
+    The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities from each image. 
+    For example, since we prefer the high-resolution image in the shallow section, we weight it stronger there and gradually taper the weight to preference the legacy image with depth. 
+    In addition, we estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy image's amplitudes with respect to the high-resolution image. 
+    The specific values we used for the weights are shown in Figure \ref{fig:hweight,lweight-reverse}.
 
-We implement the inversion in equation~(\ref{eq:inv}) iteratively
-using the method of conjugate gradients. The resultant blended image,
-shown in Figure~\ref{fig:merge2-reverse}, retains the higher
-frequencies from the high-resolution image while incorporating the
-lower frequencies from the legacy image
-(Figure~\ref{fig:nspectra22-reverse}). The broader frequency bandwidth
-corresponds to an increase in resolution and leads to a more detailed
-and interpretable image.  As a result, the blended image resembles the
-high-resolution image but has a marked decrease in noise and extended
-coverage with depth. 
-%The change from the high-resolution image to the blended image is shown in Figure~\ref{fig:merge1-reverse}.
+    \multiplot{2}{hweight,lweight-reverse}{width=0.65\columnwidth}{The weights for the high-resolution (a) and legacy (b) images for the least-squares merge.
+The high-resolution weight is strongly weighted in the shallow part and blends to favor the legacy image with depth.
+The legacy weight is selected to boost the legacy image's relative amplitudes to match that of the high-resolution image.}
 
-%\plot{merge1-reverse}{width=\columnwidth}{The difference between the merged and high-resolution images.
-It is clear that the merged image generally resembles the high-resolution image, especially in the shallow part.
-However, at depth, it incorporates more from the legacy image.}
+    \plot{nspectra22-reverse}{width=0.90\columnwidth}{The spectra of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and merged (magenta solid) images for the first data set.}
+
+    We implement the inversion in equation~(\ref{eq:inv2}) iteratively using the method of conjugate gradients \cite[]{conjgrad}. 
+    The resultant blended image, shown in Figure~\ref{fig:merge2-reverse}, retains the higher frequencies from the high-resolution image while incorporating the lower frequencies from the legacy image (Figure~\ref{fig:nspectra22-reverse}).
+    The broader frequency bandwidth corresponds to an increase in resolution and leads to a more detailed and interpretable image.  
+    As a result, the blended image resembles the high-resolution image but has a marked decrease in noise and extended coverage with depth.
+
+    Although the method presented in this paper is applied to post-stack images, the general method is likely flexible enough to be extended to pre-stack data.
+    Applications of matching legacy and high-resolution seismic data are also seen in time-lapse image registration, where the accurate interpretation of 4D time-lapse data heavily depends on dataset alignment and uniform processing \cite[]{nonuniform}.
+    The method from this paper could also be used in 4D time-lapse processing; particularly the steps involving frequency balancing and accounting for time shifts.
 
@@
     \inputdir{pcable}
-We also applied this method to a 3D data set, which is shown in Figure \ref{fig:legacy4,hires4,merge3}.
-%This second example includes data from the inner shelf of the Gulf of Mexico, just off of San Luis Pass, Texas.
-The high-resolution P-cable data set was acquired by The Bureau of Economic Geology at The University of Texas at Austin of a shallow marine environment in the Gulf of Mexico.
-This second example includes data from the inner shelf of the Gulf of Mexico, just off of San Luis Pass, Texas.
+    Our second example refers to data from the inner shelf of the Gulf of Mexico, just off of San Luis Pass, Texas \cite[]{data}.
     The high-resolution P-cable data set was acquired from a shallow marine environment in the Gulf of Mexico. 
-%This P-cable acquisition system allows for short offset, low fold data. 
-%The area of interest for this survey was the near subsurface, and a high frequency source was used which allows for exceptional resolution in the shallow section, at the expense of less coherent signal information at depth due to attenuation.
-There is legacy data coverage over the same area, which has better signal continuity at depth than the high-resolution P-cable data.
-This is apparent by looking at the first few hundred milliseconds of data for both data sets, as shown in Figure \ref{fig:legacy4window,hires4window,legacy4window2,hires4windowagc} (\cite{tip}).
-The area of interest for this survey was the near subsurface, and a high frequency source was used which allows for exceptional resolution in the shallow section, at the expense of less coherent signal information at depth due to attenuation \cite[]{tip}.
-There is legacy data coverage over the same area, which has better signal continuity at depth than the high-resolution P-cable data.
-%\multiplot{4}{legacy4window,hires4window,legacy4window2,hires4window2agc}{width=0.7\columnwidth}{The first 600 ms of data from a sample line from the legacy (a) and high-resolution (b) data sets, and the same images with depth for the legacy (c) and high-resolution (d) data sets.
-From this, it is clear that we would like our final data set to resemble the high-resolution data set in the shallow parts and the legacy data with depth.}
-%\multiplot{2}{window1,window2}{width=0.75\columnwidth}{The first 600 ms of data from a sample line from the legacy, high-resolution, and merged data sets (a).
-The same images with depth for the legacy, high-resolution, and merged data sets (b).
-The merged data set resembles the high-resolution data set in the shallow parts and incorporates the more coherent lower frequency information from the legacy data set with depth.}
-%\plot{windowed}{width=\columnwidth}{The first 600 ms of data from a sample line from the legacy (a) and high-resolution (b) data sets, and the same images with depth for the legacy (c) and high-resolution (d) data sets.
-From this, it is clear that we would like our final data set to resemble the high-resolution data set in the shallow parts and the legacy data with depth.}
+    The area of interest for this survey was the near subsurface, and a high frequency source was used which allows for exceptional resolution in the shallow section, at the expense of less coherent signal information at depth caused by attenuation \cite[]{tip}.
+    In addition, very little low-frequency information is present in the P-cable data because of the high-frequency source used, which makes balancing spectral content particularly difficult. 
+    The other image comes from legacy data coverage over the same area, which has better signal continuity at depth than the high-resolution P-cable data. 
+    This is apparent by looking at the first few hundred milliseconds of data for both data sets 
+    (Figure \ref{fig:window1,window2}).
 
-Due to the nature of acquisition, the high resolution data set has very dense spatial coverage, %with bins of about 6.25 m\textsuperscript{2}, 
+    \multiplot{2}{window1,window2}{width=0.75\columnwidth}{The first 600 ms of data from a sample line from the legacy, high-resolution, and merged image (a).
+The same images with depth for the legacy, high-resolution, and merged images (b).
+The merged image resembles the high-resolution image in the shallow parts and incorporates the more coherent lower frequency information from the legacy image with depth.}
+
+    Due to the nature of acquisition, the high resolution image has very dense spatial coverage, 
     providing detailed time slices of the near subsurface \cite[]{tip}. 
-The legacy data set has lower spatial resolution, and the two images were acquired using different geometries.
-%in different directions.
-As a result, when matching the high-resolution and legacy images spatially, the high spatial resolution of the high-resolution data set must be degraded to match that of the legacy data set.
-The legacy and high-resolution images are rebinned to ensure that they are aligned spatially before continuing.
-%, and the rebinned initial data sets are shown in Figures \ref{fig:legacy4} and \ref{fig:hires4}.
+    The legacy image has lower spatial resolution. 
+    As a result, when matching the high-resolution and legacy images spatially, the high spatial resolution of the high-resolution image must be degraded to match that of the legacy image. 
+    We rebinned the legacy and high-resolution images to align them spatially for comparison (Figure \ref{fig:legacy4,hires4,merge3}).
+    We chose to spatially down-sample the high-resolution image to match the legacy image as opposed to interpolating the legacy image to the high-resolution image's spatial grid to prevent potentially introducing inaccurate data in the merged image.
 
-%\plot{cdp}{width=\columnwidth}{The CDP bin map of the legacy (blue) and high-resolution (red) data sets.
-The high-resolution data set has much more dense coverage than the legacy data set, which must be compromised when spatially aligning the two data sets.}
-%\plot{nspectra}{width=\columnwidth}{The spectral content of the legacy (blue) and high-resolution (red) data sets.}
+    There is a definite separation in frequency content when comparing the legacy and high-resolution images (Figure \ref{fig:nspectra2}). 
+    Because there is not much overlap in frequency bandwidth, balancing their spectral content is challenging. 
+    In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:radius}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption.
+    As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:radius}) to ensure matching frequency content.
 
-%\inputdir{pcable}
+    We first apply a low-cut filter to the legacy data to remove the low frequency information that is simply not present in the high-resolution image. 
+    Next, we adjust the non-stationary smoothing radius using a simple iterative algorithm \cite[]{locfreq}.
 
-There is a definite separation in frequency content when comparing the legacy and high-resolution images, as shown in Figure \ref{fig:nspectra2}. 
-Because there is not much overlap in frequency bandwidth, balancing their spectral content is difficult.
-As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:radius}) to ensure matching frequency content.
-We first apply a low-cut filter to the legacy data.
+    The main premise behind the algorithm comes from the fact that, in general, the greater the smoothing radius at a specified point, the more high frequencies are attenuated by smoothing.
+    We choose an initial guess of the non-stationary smoothing radius before applying corrections based on two primary assumptions:
+    \begin{enumerate}
+    \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the high-resolution image has \emph{higher} local frequency than the legacy image.
+Thus, the smoothing radius must be \emph{increased} at that point.
+    \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the high-resolution image has \emph{lower} local frequency than the legacy image.
+Thus, the smoothing radius must be \emph{decreased} at that point.
+    \end{enumerate}
 
-Next, we adjust the non-stationary smoothing radius based on two assumptions. 
-First, the smoothing radius is too small at a specified point if, after smoothing, the high-resolution image still has a much higher local frequency than the legacy image.
-Thus, the smoothing radius must be increased at that point.
-Second, the smoothing radius is too large if the high-frequency image has lower frequency content than the legacy image at a specified point after smoothing.
-In this case, the smoothing radius must be decreased at that point.
+    We apply these assumptions using a line-search method:
+    \begin{equation}
+        \label{eq:linesearch}
+        \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \mathbf{r}^{(i)},
+    \end{equation}
+    where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $\alpha$ is a scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the residual at the $i$th iteration, which can be thought of as the search direction, and is
+    defined as
+    \begin{equation}
+        \label{eq:residual}
+        \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}} \mathbf{d}_h] - \mathbf{F}[\mathbf{d}_l]\;,
+    \end{equation}
+    where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the high-resolution image, $\mathbf{d}_l$ is the legacy image, and $\mathbf{F}$ is the local frequency operator.
+    It can be noted that when equation (\ref{eq:residual}) is positive, the high-resolution image still has a higher local frequency value at that specific point than the legacy image; thus the high-resolution image is under-smoothed and the smoothing radius should be increased at that point.
+    This follows the form of the first assumption. 
+    The second assumption is used when equation (\ref{eq:residual}) is negative. 
+    When equation (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections are made. 
+    Thus, it is justifiable to set the search direction from equation (\ref{eq:ls}) equal to the residual.
 
-Using these two assumptions, we can continually adjust the smoothing radius until we have achieved the desired result of balancing the local frequency content between the two images.
-This process is discussed in further detail in the companion paper \cite[]{locfreq}.
+    Using this method, we can continually adjust the smoothing radius until we achieve the desired result of balancing the local frequency content between the two images.
+    In practice, this method produces an acceptable solution in approximately 5 iterations and exhibits sublinear convergence. 
+    We smooth the high-resolution image with the radius this method produces to balance local frequency content between the two images.
 
-After this, we use the low-cut filtered legacy and smoothed high-resolution images to find estimated time shifts we need to apply to the high-resolution data to align the reflections with the legacy data.
-Then, we apply this estimated time shift to the original high-resolution image and blend it with the original legacy image as specified by equations~(\ref{eq:ls}) and (\ref{eq:inv}).
+    After this, we use the low-cut filtered legacy and smoothed high-resolution images to find estimated time shifts we need to apply to the high-resolution image to align the reflections with the legacy image.
+    Then, we apply this estimated time shift to the original high-resolution image and blend it with the original legacy image as specified by equations~(\ref{eq:ls}) and (\ref{eq:inv2}).
 
-The resultant merged image is shown in Figure \ref{fig:merge3}. The frequency content of the merged image is shown in Figure 
-\ref{fig:nspectra2}.
+    The resultant merged image is shown in Figure \ref{fig:merge3}. 
+    The frequency content of the merged image is shown in Figure \ref{fig:nspectra2}. 
     Here, the merged image spans the frequency bandwidth of the two initial images, thus producing a high resolution volume including optimal signal characteristics from the two initial images.
 
-%\plot{nspectra2}{width=0.90\columnwidth}{The spectral content of the legacy (blue dotted), high-resolution (red dashed), and resultant merged (magenta solid) images for the second data set.}
-
-%The results are shown in Figures \ref{fig:hires4,legacy4,mergeagc} and \ref{fig:hires4,legacy4,merge}.
+    \plot{nspectra2}{width=0.90\columnwidth}{The spectral content of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and resultant merged (magenta solid) images for the second data set.}
 
@@
 
-%\multiplot{3}{legacy4,hires4,merge3}{width=1.0\columnwidth}{The legacy (a), high-resolution (b), and resultant merged (c) images of the second data set.} 
-%\plot{nspectra3}{width=\columnwidth}{The spectral content of the legacy (blue dotted), high-resolution (red dashed), and resultant merged (magenta solid) data sets.}
+    \multiplot{3}{legacy4,hires4,merge3}{width=0.45\columnwidth}{The legacy (a), high-resolution (b), and resultant merged (c) images of the second data set.}
 
@@
 
-We have proposed an approach to matching seismic images of different
-resolutions. Our first step is non-stationary smoothing of the
-high-resolution image to match the spectral content and amplitudes
-of the legacy image. Next, we estimate the relative time shifts using
-local similarity scanning. After matching the two images, we create a
-blended image by least-squares inversion, which effectively
-combines the best features of the two images: the broader frequency
-bandwidth of the high-resolution image with the reflection continuity
-and deeper coverage of the legacy image. The final result is an 
-interpretable blended image. We have shown example applications of
-the proposed method to high-resolution and legacy images from the Gulf
-of Mexico.
+    We propose an approach to matching seismic images of different resolutions. 
+    Our first step is non-stationary smoothing of the high-resolution image to match the spectral content and amplitudes of the legacy image. 
+    Next, we estimate the relative time shifts using local similarity scanning.
+After matching the two images, we create a blended image by least-squares inversion, which effectively combines the best features of the two images: the broader frequency bandwidth of the high-resolution image with the reflection continuity and deeper coverage of the legacy image.
+    The final result is an interpretable blended image that has higher temporal resolution than either of the two initial images. 
+    Two example applications using high-resolution and legacy seismic images from the Gulf of Mexico demonstrate the effectiveness of our method.
 
@@
 
-We thank August Lau, Tip Meckel, and Chuan Yin for useful discussions and Apache and Fieldwood for providing the first example data set. 
+    We thank Michael DeAngelo, August Lau, Tip Meckel, and Chuan Yin for useful discussions and Apache and Fieldwood for providing the data used in the first example. 
     We also thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
 
-\onecolumn
+%\onecolumn
+%
+%\bibliographystyle{seg}
+%\bibliography{SEG,merge}

### 2018-04-13 chapter-mighes/paper.tex
geofigs

@@
-\title{Migration deconvolution}
-\author{Sarah Yvonne Greer}
-\maketitle
-
-%\title{Migration deconvolution using non-stationary matching}
-%\title{Approximating the inverse Hessian to enhance migration using non-stationary matching operators}
-%\title{Improving migration resolution by approximating the Hessian using non-stationary matching operators}
-%\title{Improving migration resolution by approximating the Hessian using non-stationary amplitude and frequency matching operators}
-%\title{Improving migration resolution using non-stationary amplitude and frequency matching operators}
-%\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
-%\title{Approximating the inverse Hessian to enhance migration using linear non-stationary matching operators}
-%\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
+\title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
+\author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
 \newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
 \maketitle
-%\inputdir{sigsbee}
-\inputdir{sigsbee2}
+\inputdir{sigsbee}
 \begin{abstract}
     We propose using two non-stationary operators to represent the amplitude and frequency variations in the least-squares Hessian to account for the principal differences between conventional and least-squares migrated images.
-    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration,
-    and it increases the resolution and amplitude fidelity of the migrated image.
-%    When applying these transformation to a conventionally migrated image, it improves the image resolution.
-    %We propose an approach of approximating the inverse Hessian operator in application to migration deconvolution. 
-    %Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the Hessian---one to account for amplitude variations, and the other to account for frequency variations.
-    %Successful results were achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
+    The calculation and application of these operators are computationally inexpensive when compared to one iteration of least-squares migration, and it increases the resolution and amplitude fidelity of the migrated image.
     Successful results are achieved on an application of reverse-time migration to the Sigsbee synthetic data set.
@@
 \section{Introduction}
-%However, the process may be computationally expensive as it typically involves multiple iterations of forward modeling and remigrating the data. 
-%Least-squares migration \cite[]{lsm} \ldots
     Least-squares migration can produce an accurate migrated seismic image.
     However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling and migration. 
-%However, the process may be computationally expensive as it is typically performed in an iterative manner, where each iteration involves forward modeling, calculating the residual misfit, performing a conventional migration, and updating the model.
-%At the cost of approximately one iteration of least-squares migration, 
     Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%These artifacts are due to the fact that standard migration applies only a single adjoint operation \cite[]{pvi}.
-%Least-squares migration can help alleviate 
-This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by 
-finding the least-squares model solution,
-standard migration amounts to applying a single adjoint operation \cite[]{pvi}. 
-%Conventionally migrated seismic images generally contain migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%A standard way to alleviate these artifacts 
-%is an advanced way of producing an accurate image of the subsurface \cite[]{lsm}.
-%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%Conventional migration is not , as such, 
-%conventionally migrated images generally suffer from migration artifacts affecting amplitude fidelity and resolution. 
-%However, compared to least-squares migrated images, conventionally migrated images generally suffer for migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%solving the least-squares normal equations, 
-%While this can be a good approximation to the inverse, and as such, is not a true inverse operation.
+    This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by finding the least-squares model solution, standard migration amounts to applying a single adjoint operation \cite[]{pvi}.
 
     Various methods have attempted to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
-%Migration deconvolution attempts to correct these differences by finding and applying an approximation to the inverse Hessian operator, $\mathbf{H}^{-1} = \left (\mathbf{L}\tran\mathbf{L} \right )^{-1}$, to a conventional migrated image.
     Here, $\mathbf{L}$ is a standard forward-modeling operator, and $\mathbf{L}\tran$ is its adjoint---the migration operator.
     These methods usually take the form of two approaches---for preconditioning before least-squares migration and as a single operation to improve accuracy of a conventionally migrated image.
-%This filter approximates the inverse Hessian operator, and can be approximated by solving a data matching problem between two conventionally migrated images. 
-%Migration deconvolution \cite[]{poststack,prestack}
-Previously, this has been done by 
-migration deconvolution \cite[]{poststack,prestack},
-%stochastscally approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{diagamp}, 
-approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp},
-and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
-%This has traditionally been done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different operations are specified in each region \cite[]{seiinv}.
+    Previously, this has been done by migration deconvolution \cite[]{poststack,prestack}, approximating the diagonal of $\mathbf{H}^{-1}$ to account for amplitude effects \cite[]{amp,diagamp}, and by finding and applying a bank of non-stationary matching filters \cite[]{imop,rtmmf} or deblurring filters \cite[]{debfilt} to a conventionally migrated image.
     This traditionally is done using a sliding window approach, where windowed regions and partial overlap regions are specified, and different matching filters are specified in each region \cite[]{seiinv}.
@@
     We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
-%Because of this, we choose to approximate the  
     Here, we treat this as a data matching problem between two conventionally migrated images, and find separate operations to account for both amplitude and frequency variations.
-%However, we propose using two separate non-stationary operators---one to account for amplitude variations, and the other to account for frequency variations.
 
-%This has advantages over previous methods as, instead of using a sliding window approach, we rely on local seismic attributes to measure and apply amplitude and frequency balancing operations \cite[]{attr}.
     This approach enables us to rely on local seismic attributes to measure and apply amplitude and frequency balancing operations instead of using a sliding window approach \cite[]{attr}.
 This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
-%of local seismic attributes, and for 
-%In the past, 
-Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each 
-%transformation 
-operation
-can be adjusted independently, which is another advantage of the proposed method.
+    Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each operation can be adjusted independently, which is another advantage of the proposed method.
     To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}.
-%Least squares migration is more computationally expensive than conventional migration, but it produces a more accurate image of the subsurface---conventional migrated images generally 
-%suffer from migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-%exhibit less correct amplitude and frequency content. 
-%applying a filter to a conventional migrated image to produce a more accurate image with less computational cost than least-squares migration. 
-%Previously, this has been done using non-stationary, or spatially and temporally variant, matching filters in a sliding-window approach.
 
-%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the migration-deconvolution image as a starting moel (red).}
-%Once finding the forward operation,
 \section{Theory}
@@
     \begin{equation}
-p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
+        p(\hat{\mathbf{r}}) = \frac{1}{2}\left \Vert \mathbf{\mathbf{d} - L\hat{r}} \right \Vert _2^2\;,
+        %p(\hat{\mathbf{r}}) = \frac{1}{2}\left \lVert \mathbf{\mathbf{d} - L\hat{r}} \right \rVert _2^2\;,
     \end{equation}
@@
     \end{equation}
-where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, 
-%where $\mathbf{L}\tran$ is the migration operator, 
-and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
-%Equation (\ref{eq:ls}) is usually solved iteratively, where each iteration costs %by multiple iteration of forward modeling
-%where each iteration involves 
-%On the other hand, conventional migration
+    where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator and is typically sparse, and $\left ( \mathbf{L}\tran \mathbf{L} \right )^{-1}$ is the inverse Hessian operator.
     Equation (\ref{eq:ls}) is usually solved iteratively, typically requiring multiple iterations of forward modeling and remigrating the seismic image \cite[]{wem,xue16}. 
@@
 \end{equation}
-%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
     However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images \cite[]{dutta14}. 
@@
 \end{equation}
-%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
     so $\mathbf{m}_0$ is a distorted version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by finding a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
 
-%The least squares image, $\hat{\mathbf{r}}$
-
-%Here the forward modeling operator, and subsequently the migration operator, $\mathbf{L}\tran$, depends on the type of migration; RTM vs Kirchhoff\ldots
-
-%We can represent acquired seismic data, $\mathbf{d}$, as a forward-modeled version of the Earth's true reflectivity, 
-%\begin{equation}
-%        \mathbf{d} = \mathbf{L}\mathbf{r},
-%\end{equation}
-%where $\mathbf{r}$ is the Earth's reflectivity and $\mathbf{L}$ is the forward modeling operator CITE. 
-%Least-squares migration can produce a close approximation to the Earth's reflectivity by finding the least-squares solution,
-%\begin{equation}
-%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{L}\tran\mathbf{d},
-%        \label{eq:ls}
-%\end{equation}
-%but it can be computationally expensive as it typically requires multiple iterations of forward modeling and remigrating the seismic image CITE. 
-%Conventional migration is less computationally expensive:
-%\begin{equation}
-%        \mathbf{m}_0 = \mathbf{L}\tran\mathbf{d},
-%        \label{eq:mod}
-%\end{equation}
-%where the migration operator, $\mathbf{L}\tran$, is adjoint to the forward modeling operator. 
-%However, conventionally migrated images generally exhibit less correct amplitude and frequency content than least-squares migrated images CITE. 
-%By combining equations \ref{eq:ls} and \ref{eq:mod}, it is evident that
-%\begin{equation}
-%        \hat{\mathbf{r}} = \left ( \mathbf{L}\tran\mathbf{L}\right )^{-1}\mathbf{m}_{1},
-%\end{equation}
-%so $\mathbf{m}_0$ is an $\mathbf{L}\tran\mathbf{L}$ blurred version of $\hat{\mathbf{r}}$, and $\hat{\mathbf{r}}$ can be recovered from $\mathbf{m}_0$ by a good approximation of $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$.
-%
-%In order to find $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of CITE. We begin by forward modeling the migrated image, $\mathbf{m}_9$:
-%\begin{equation}
-%        \mathbf{d}_2 = \mathbf{L}\mathbf{m}_0.
-%\end{equation}
-%We then remigrate $\mathbf{d}_2$:
-%\begin{equation}
-%        \mathbf{m}_1 = \mathbf{L}\tran\mathbf{d}_2 = \left ( \mathbf{L}\tran\mathbf{L}\right ) \mathbf{m}_0,
-%\end{equation}
-%and then find the operator, $\left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that satisfies
-%\begin{equation}
-%        \mathbf{m}_0 = \left ( \mathbf{L}\tran\mathbf{L} \right ) ^{-1} \mathbf{m}_1.
-%\end{equation}
-%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
-%
-
 \section{Method}
-%Here, we follow the forward-modeling and remigration approach of
-
     In order to approximate $\left ( \mathbf{L}\tran\mathbf{L}\right) ^{-1}$, we follow the modeling and remigration process of \cite{imop}. 
@@
     \end{equation}
-%The inverse Hessian operator that must be applied to $\mathbf{m}_0$ to correct it closer to the least-squares migrated image, $\hat{\mathbf{r}}$, therefore, can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
-%Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by finding the transformation $\mathbf{H}^{-1}$, that maps $\mathbf{m}_1$ to $\mathbf{m}_0$.
     Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
     This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.
-%This can be interpreted as a data matching problem between $\mathbf{m}_0$ and $\mathbf{m}_1$.
 
-%\multiplot{3}{mod,image0,migdec-shap}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), the conventionally migrated image (b), and the corrected migrated image (c).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=1.0\columnwidth}{The Sigsbee model reflectivity (a), migration migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
-%\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
-%Typically, the differences between least-squares migrated images and conventionally migrated images amount to only amplitude and frequency changes, 
+\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
     Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations.
     Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
-    %We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined. 
     We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
@@
     First, we choose to find an amplitude balancing operation that, when applied to $\mathbf{m}_0$, balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$. 
-%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
-%This amplitude balancing operator, $\mathbf{A}$, only has terms across the diagnonal, and is applied similarly to a matrix-vector operation trace-by-trace throughout the image.
     This operation can be equated to a trace-by-trace multiplication of a diagonal matrix to each trace, where the matrix changes for every trace.
-%The matrix $\mathbf{A}$ changes 
     We estimate it by first calculating the amplitude envelope of the traces in $\mathbf{m}_0$ and $\mathbf{m}_1$, and then smoothly dividing them.
     The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
-%to find the diagonal weighting operator 
-%to balance the amplitudes of each trace.
-%that balances the amplitudes of each trace of $\mathbf{m}_0$ to match with $\mathbf{m}_1$.
-%This is a linear diagonal weighting operator
-%This linear operator only has elements across the diagonal terms, so it is trivial to find the inverse operator. 
-%Therefore, this operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
-%Therefore, the operator $\mathbf{S}$, when applied to $\mathbf{m}_1$ as $\mathbf{m}_0 \approx \mathbf{S}\mathbf{m}_1$, .
     Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.
-
-%\multiplot{2}{a0,a1}{width=1.0\columnwidth}{The forward amplitude balancing weights, $\mathbf{A}_0$ (a) and $\mathbf{A}_1$ (b).}
-%\plot{rect10}{width=1.0\columnwidth}{The smoothing radius, which represents the number of samples in both spatial dimentions, that $\mathbf{m}_0$ must be smoothed over in a pyramid weight to balance local frequency content with $\mathbf{m}_1$.
-This represents the forward smoothing operation, $\mathbf{S}$.}
 
@@
     This loss in resolution can be equated to the fact that $\mathbf{L}\tran\mathbf{L}$ acts as a blurring operator, where the conventional migrated image is a blurred version of the ideal least-squares migrated image \cite[]{poststack}.
-%where each individual value
     We choose to approximate this blurring using non-stationary triangle smoothing.
 
-%This means that the 
     We begin by first calculating the local frequency of the two initial images \cite[]{attr}. 
@@
     To do this, we propose using non-stationary triangle smoothing. 
-%This approach involves finding and applying a non-stationary smoothing radius, which is the amount of samples, in time, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance local frequency content with $\mathbf{m}_1$.
     This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.
@@
 
-%    Unlike $\mathbf{A}$, the smoothing operator, $\mathbf{S}$, is more challenging to invert 
-%    since it is generally a banded, but not diagonal, operator and physically represents the mixing of each data point with other nearby data points.
-    %This smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric. 
-    %However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create false high-frequency data if inverted incorrectly without regularization.
-%\multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$.
+    \multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$.
 This represents the forward smoothing operation, $\mathbf{S}$.}
@@
     Now that we have found the forward operators that separately balance amplitude and frequency content from $\mathbf{m}_0$ to $\mathbf{m_1}$, where $\mathbf{m}_1 \approx \mathbf{H} \mathbf{m}_0$, we want to find what combination of $\mathbf{A}$ and $\mathbf{S}$ best approximates $\mathbf{H}$.
-    %An advantage of finding $\mathbf{A}$ and $\mathbf{S}$ separately is that they can each be individually adjusted 
-    %the inverse of this operator such that $\hat{\mathbf{r}} = \left (\mathbf{H} \right )^{-1} \mathbf{m}_0$.
     Since $\mathbf{H} = \mathbf{L}\tran\mathbf{L}$ is symmetric, we want our approximation of $\mathbf{H}$ to be as close to symmetric as possible.
@@
     \end{equation}
-            %\mathbf{H} = \frac{1}{2}\left ( \mathbf{A}\mathbf{S} + \mathbf{S}\mathbf{A} \right )
     where $\mathbf{A}$ is the operator that balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, and $\mathbf{S}$ is the operator that balances the local frequency content of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, both defined previously.
     Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric, since both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
-    %One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
     Splitting up our approximation to the Hessian into two separate operators allows us to control how much of each operation and the order of each operation goes into correcting the image, and see how it affects the resulting image.
-%    \begin{equation}
-%        \mathbf{H} = \mathbf{A}_1^{\sfrac{1}{2}} \mathbf{S} \mathbf{A}_0^{\sfrac{1}{2}}\;,
-%    \end{equation}
-%    where $\mathbf{A}_0$ is found by balancing amplitudes between $\mathbf{m}_0$ and $\mathbf{m}_1$, $\mathbf{S}$ is calculated by finding the smoothing operator that balances the local frequency content between $\mathbf{m}_0$ and $\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_1$, and $\mathbf{A}_1$ is found by balancing amplitudes between $\mathbf{S}\mathbf{A}_0^{\sfrac{1}{2}}\mathbf{m}_0$ and $\mathbf{m}_1$.
-%    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be close to symmetric. 
-%    However, note that here $\mathbf{H}$ is not quite symmetric, but since $\mathbf{A}_0$ and $\mathbf{A}_1$ should be very similar, it is nearly symmetric.
-%    One thing to note is that the operators do not commute, so $\mathbf{AS} \neq \mathbf{SA}$.
-%
     Now that we have found the forward Hessian, $\mathbf{H}$, such that $\mathbf{H}\mathbf{m}_0 \approx \mathbf{m}_1$ using data matching operators, we want to find the inverse of this operator, $\mathbf{H}^{-1}$, such that $\hat{\mathbf{r}} \approx \mathbf{H} ^{-1} \mathbf{m}_0$ provides us with the least-squares image.
@@
     Since the amplitude operators only contain diagonal terms, they are simple to invert. 
-    %However, the smoothing operator, $\mathbf{S}$, is more challenging to invert. 
-    %While smoothing operator, $\mathbf{S}$, is diagonally-dominant nearly symmetric,. 
     However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
@@
     The constant is small, typically around 10 for the number of iterations, and the calculation and application of this approximation is computationally insignificant compared to one iteration of least-squares migration.
-%is far less computationally expensive than one iteration of least-squares migration.
-    %The constant is 
-    %It is a diagonally-dominant operator
-    %The amplitude operator accounts for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms of the forward Hessian operator.
-    %Our approximation to the forward Hessian operator turns out to be diagonally-dominant, where the amplitude operators account for the diagonal terms, and the smoothing operator accounts for the diagonal and off-diagonal terms.
 
-%This allows us to find an operator that effectively balances the local frequency content of $\mathbf{m}_0$ to match with $\mathbf{m}_1$. 
-%Next, we need to find the inverse of this operation to 
-%Since the operation is non-stationary, it is applied in the time domain
-
-%we follow the approach of CITE. This approach uses non-stationary triangle smoothing. for finding the smoothing radius that 
-%
-%to increase the resolution of the
-
-%    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
+    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
 
@@
 
-%\multiplot*{3}{mod-w3,image0-w3,migdec-w3}{width=0.66\columnwidth}{The Sigsbee model reflectivity (a), the first migrated image (b), and the corrected migrated image (c).}
-    We demonstrate the effectiveness of this method on the 2D Sigsbee model. %reverse-time migrated 
+    \multiplot*{3}{mod-w3,image0-w3,migdec-w3}{width=0.66\columnwidth}{The Sigsbee model reflectivity (a), the first migrated image (b), and the corrected migrated image (c).}
+    We demonstrate the effectiveness of this method on the 2D Sigsbee model. 
     The Sigsbee2A 2D synthetic data set was created to mimic the geology of the Sigsbee escarpment in the Gulf of Mexico \cite[]{sigsbee}.
-    %In this example, we use reverse-time migration as our migration operator.
-    %* Zhiguang---Insert information about migration specifics (shot/receiver spacing, absorbing boundary conditions, etc.) *
     A fixed-spread acquisition survey is generated, which consists of 301 shots spaced every 122 m.
@@
 We use reverse-time migration (RTM) as our migration operator.
-%\plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image.}
 
@@
     Figure \ref{fig:mod-w3,image0-w3,migdec-w3} shows a windowed section of the reflectivity model, the conventionally migrated image, and the corrected migrated image.
-    %The corrected migrated image is clearly of higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.
     The corrected migrated image exhibits clearly higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.
-
-%    Figure \ref{fig:spec2} shows the frequency content of the conventionally migrated image and the corrected migrated image. 
-%    The corrected migrated image has a broader bandwidth and a flatter spectra than the conventionally migrated image, and generally recovers the higher frequency data that was lost during conventional migration.
-%    However, it does lose some low frequency content as a result of the process, 
-%    %Additionally, the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
-%    but the frequency spectra of the corrected migrated image %closer resembles that of the model than the conventionally migrated image.
-%    is still a better approximation of the model than that of the conventionally migrated image.
-%    %is a better approximation of the model than that of the conventionally migrated image.
-%
 
@@
 \section{Conclusions}
-%Conventionally migration involves 
-%A higher resolution least-squares migrated image 
-%This method does not involve dividing the data into windows 
     Least-squares migration can produce an accurate migrated image, but it is more computationally expensive than conventional migration.
@@
 
-%\plot{spec2}{width=0.85\columnwidth}{The frequency content of the conventionally migrated image (blue solid), and the corrected migrated image (red dashed).}
-
 \inputdir{sigmoid}
-%\plot{error}{width=1\columnwidth}{Convergence of conventional least-squares migration (blue) and using the corrected migrated image as a starting model (red).
-Here, the migration operator is post-stack Kirchhoff migration.}
 
@@
     The examples in this paper can be reproduced using the Madagascar open-source software package \cite[]{madagascar}.
-
-%\inputdir{kir}
-
-\onecolumn
-
-\bibliographystyle{seg}
-\bibliography{SEG,migdec}
-
-%        In seismic processing we have the operation of migration, which is a linear transform, and we can think of it as the adjoint of modeling.
-So if you know the velocity, and you have reflectivitym, so going from reflectivity to data is a linear transformaiton the adjoint of that is migration.
-%
-%        And then so reflectivity
-%        d = Lm
-%        So migraziton would be the adjoint applied to the data
-%        And if we try to do inverse, it would be:
-%        so this is LSM
-%
-%        And normally we would do it with iterations, so doing conjugate gradients or some sort of iterative method, where we approximate its inverse using iterations.
-But it is still expensive because in each iteration we need to do modeling and migration, and that's an expensive process.
-%        So, the idea is instead of computing this exactly, we approximate it.
-%        This is called migrtion deconvolution.
-%
-%        Now, what does it actrually do?
-%        SO the interesting part about the operations of modeling and migration here is that when you do them in term, you do modeling and migfration, so theoretixallty, it's an operation that does somethjing with the input, so you put in one image and get another image.
-%        But the other image does not have a shift---things will return to the same place. So, mostly it amounts to scaling, so different scale, and there is also some smearing.
-%
-%        SO if for example you put this as an input, you'll get the same points but they'll be smeared a little bit, but they'll be in the same place.
-%
-%        There is some smearing and there is some scaling. So that's what this is basically trying to correct.
-%        So, we go from here to here, and there are different ways people tried to do it before.
-%        One was just to focus on the scaling, and then so you're looking at the diagonal matrix to apply some scale to compensate.
-%        The other was to use theory to try to derive theoretically what this should be, and there are other theories, but they are based on ideal situations, so you don't consider the fact, for example, that the data that you have is not infinite so it has a finite extent.
-%        SO the theory is good, but it's idealized to look that everything is continuous, infinite, which is not the case.
-So part of what we see here when we look at the smearing, so part comes from the nature of modeling and migraiton, which we know theoretically, but part of it is from the fact that the data are not perfect, so we have limited extent, and discrete non-continuous data.
-So the theory may work in practice and get most of it, but not all of it because it is idealized.
-%        So it's useful, but it's not ??? 27:45
-%
-%        So Antoine in CSM\ldots
-%        This year he shows an application that is specifically for RTM, but the idea comes from his older paper which is 
-%        And that was just simply that you \ldots
-%        This was done previously to look for just the scaling.
-%        You have sort of training images.
-You can use this M ans one of the training.
-But you can also create a bunch of the other ones.
-If you create a bunch of synthetic you have a bunch of reflectivity models, but it's sort of an open question of how you do it.
-So you can use spikes, reflectors, random, but in some way generate a bunch of those but you apply modeling and migration to it.
-And now you have example inputs and example outputs, and you want the inverse of this.
-SO you want to find out how to go back from this to the theoretical.
-And you cannot use too many bc it get expensive and it is easier to do LS migration with iterations.
-Computatinoally, the challenge is how to figure out what this is without using too many training images.
-%        Instead of the simple scale, he looks for a non-stationary matching filter. Now if we learn what this is, you can just apply it once, and there are also\ldots
-%        Single iteration migration, but they mean doing it once
-%        Find out how to approximate this inverse and they apply it to compensate. But you can also use it as a preconditioner.
-%        So the other use is, so say I'm still going to run iterations, but I'll but this correction inside, and then instead of 10 iterations, maybe I can use it fewer. 
-%
-%        So there are differences between the asdasd of preconditioned conjugate gradients.
-Some of them use m, and some split m into two parts.
-So we can say that you have instead of r and you're looking for x, and you're inverting afjsdkl;, so \ldots 36:40
-%        In any conjugate gradients, you can precondition by making it run faster by making the inverted matrix closer to the identity.
-So there is a dual purpose to this --- to find something you can apply once but you can also use it as a precondioner if you want to do it more than one time.
-%        So in this other paper, . . .
-%        The reason I mention it to you now for what you did for the matching and triangle filters, so we have another way to describe this kind of a transformation which is fairly robust, and it may work in this application.
-Basically we have scaling and smearing which is like legacy and high-resolution.
-So the better question is to find a good example to try.
-I'm not sure if we have anything in Madagascar yet.
-We have modeling and migration, so we need to find some kind of example of applying modeling and migration so we can look how to measure the transformation for that.
-%        The interesting question is if you have scaling and you have smearing, maybe with variable radius traingle filters, so the two opeations you need both of them but they don't commute.
-So if you do scaling first and smearing second it's not the same if you do smearing first and then scaling.
-When we are dealing with this we know that it needs to be symmetric.
-%
-%        There is scaling with the weight and triangle filtering.
-It can be this, or this.
-So we are not scaling symmetrically.
-Or maybe this.
-So if we start doing something like that, it becomes non-linear, so if we have scaling twice we cannot use linear inversion to find the scaling.
-So it actually makes it more interesting, so now we need to think how to linearize it so if we have something like that for example, we can say that we want to find maybe an inital scaling; maybe I'll take it to be one initial and 43:15
-%        and the other term you neglect to get\ldots
-%        Now this one is linear, but it has an interesting combination here from the left side 
-%        So now it's a linear problem can be solved with regularization but not the same one as before. So it makes the whole problem a little more interesting
-%
-%        And then potentially, even if it's not that, so say we go back to legacy and high resolution, so we know there is scaling and there is smearing, but nothing says that scaling has to be on this side or on this size, so it can be both or it can be different on this side and the other size, so it makes it a more general problem with potentially more interesting solutions.
-%
-%        So in terms of ideas there is not a lot there, besides what I have told you, but you can read it and follow the references to other papers.
-So they put some work into implementing it.
-But if we make it work with scaling and smoothing, it would actually me a much cleaner implementation.
-Because they have to, So I suspect that what Antoine Guitton had to do to implement it was breaking everything into windows, some overlap, and then finding filters in each window and trying to change them, so it's not very stable and it's a bit messy.
-So if it works, it works, but I think we can find a cleaner result.
-and also you know if you break it into scaling and smearing, you know the ingredients of what happens in there, so you have a better understanding.
-%

### 2018-04-13 chapter-mighes/sigsbee/radius.py

@@ -1,0 +1,100 @@
+from rsf.proj import *
+
+def radius(high, low,               # initial high-resolution and legacy images
+           niter,                   # number of corrections
+           c,                       # 'step length' for radius corrections. Can be type int or float for constant c 
+                                    # or type array for changing c.
+           bias=-15, clip=30,       # bias and clip for display
+           rect1=40, rect2=80,      # radius for local frequency calculation
+           maxrad=1000,             # maximum allowed radius
+           theor=True,              # use theoretical smoothing radius
+           scale=9,                 # scale for theoretical smoothing radius
+           initial=10,              # initial value for contant smoothing radius 
+           minval=0,
+           maxval=25,
+           titlehigh="Hires",
+           titlelow="Legacy"):
+
+    if type(c) is float or type(c) is int:
+        c = [c]*niter
+
+    def seisplot(name):
+        return 'grey title="%s"'%name
+    
+    locfreq = '''iphase order=10 rect1=%d rect2=%d hertz=y complex=y | 
+                 put label="Frequency" unit=Hz'''%(rect1,rect2)
+
+    def locfreqplot(name):
+        return 'grey mean=y color=J scalebar=y title="%s" '%name
+
+    freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
+
+    def freqdifplot(num):
+        return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %s" 
+                  clip=%d bias=%d minval=%d maxval=%d''' %(num,clip,bias,minval,maxval) 
+
+    specplot = '''cat axis=2 ${SOURCES[1]} | 
+                  scale axis=1 | 
+                  graph title="Normalized Spectra" label2="Amplitude" unit2=""'''
+
+    def rectplot(name):
+        return 'grey color=j mean=y title="%s" scalebar=y barlabel=Radius barunit=samples'%name
+
+    smooth = 'nsmooth1 rect=${SOURCES[1]}'
+    #smooth = 'nsmooth rect1=${SOURCES[1]} rect2=${SOURCES[1]}'
+
[…]

### 2018-04-22 ack.tex
almost done with thesis git st

@@
-Add acknowledgements here :)
-%\begin{flushright}
-%SARAH YVONNE GREER
-%\end{flushright}
-%
-%\noindent \emph{The University of Texas at Austin}\\
-%\noindent \emph{April 2018} \\ \\
+I have received an incredible amount of support during my time as an undergraduate student. 
+First and foremost, I'd like to thank my advisor, Dr. Sergey Fomel, for his helpful guidance over the past couple of years. 
+I genuinely believe that working with him has beneficially shaped the trajectory of my life.
+Through his guidance and the opportunities he has given me, he has helped me to realize how much I truly enjoy learning, showed me the importance of reproducible computational research, introduced me new ways of thinking about and approaching problems, and inspired me to continue my studies in graduate school.
+For all that, I will be forever grateful.
+
+Many professors from the geological sciences and mathematics departments with whom I have interacted have also greatly helped me during my undergraduate career.  
+I am especially thankful to Dr.
+Todd Arbogast, Dr.
+Jaime Barnes, Dr.
+Mark Cloos, Dr.
+Luc Lavier, Dr.
+Francesco Maggi, Dr.
+Richard Tsai, and my committee members, Dr.
+Kyle Spikes and Dr.
+Clark Wilson, for their guidance during my time at UT Austin.
+
+I am also grateful to many students and research scientists I've had the pleasure of interacting with: 
+Sean Bader, Luke Decker, Preston Fussee-Durham, Zhicheng Geng, Eric Goldfarb, Ben Gremillion, Tom Hess, Ken Ikeda, Harpreet Kaur, Dr.
+Dmitrii Merzlikin, Nam Pham, Mason Phillips, Kelly Regimbal, Karl Schleicher, Yunzhi Shi, Dr.
+Junzhe Sun, Dr.
+Yanadet Sripanich, Dr.
+Xinming Wu, Dr.
+Zhiguang Xue, and Dr.
+Yunan Yang.
+
+Last but not least, I would like to express my sincere gratitude to my family for all their love and support over the years.
+Esme, Joel, Sam, Atticus, and Kali---you all mean the world to me and I wouldn't be the person I am today without you in my life.
+\begin{flushright}
+SARAH YVONNE GREER
+\end{flushright}
+
+\noindent \emph{The University of Texas at Austin}\\
+\noindent \emph{April 2018} \\ \\

### 2018-04-22 chapter-background/paper.tex
almost done with thesis git st

\title{Background}
\author{Sarah Yvonne Greer}
\maketitle
\inputdir{../chapter-locfreq/merge}
Seismic data contain fundamentally non-stationary variations in attributes such as frequency and amplitude content.
For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
%Non-stationary, or spatially and temporally variant, changes in these data can make the comparison of two data sets difficult.
%These non-stationary variations mean that, in a given data set, different 
Data matching problems involve finding some transformation, or set of transformations, that can be applied to one data set to best match some attribute with another data set.
In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
Therefore, any transformations we may apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.

Local seismic attributes are useful in the analysis of these non-stationary variations that are naturally present in seismic data \cite{attr}.
The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
For the procedures described in this thesis, local attributes are better-suited attributes than instantaneous attributes.
Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images. 
Because the corresponding reflections between images may not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency. 
Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.

\multiplot{2}{legacy,low-freq}{width=0.47\columnwidth}{A seismic image (a) and its local frequency content (b). Because its local frequency varies both spatially and temporally, we can say its frequency content is {\it non-stationary}.}

In this thesis, I propose solving data matching problems by balancing smoothly varying non-stationary attributes, such as local seismic attributes, between two data sets.
%local seismic attributes between data sets.
This is done using three primary data matching operations---filtering, scaling, and shifting---to effectively balance these attributes across seismic data sets.
These operations are applied to different data sets to correctly match them for analysis or further processing.

%These applications can be solved by specifying and applying the three previously stated data matching operators: filtering, scaling, and shifting.
To demonstrate the three matching operations in action, I apply them consecutively to an example 2D trace shown in Figure \ref{fig:one0}.
The data used in this example comes from a line from the {\em P-cable} data sets.
In this example, we want to find a transformation, or a set of transformations, to apply to the red trace to match with the black trace.
I use the three data matching operators by first filtering (Figure \ref{fig:one1}), then scaling (Figure \ref{fig:one2}), and finally shifting (Figure \ref{fig:one3}).
The three operations are described in more detail in the following sections.

\inputdir{.}
\multiplot{4}{one0,one1,one2,one3}{width=1.0\columnwidth}{(a) Two traces that need to be matched---we will match the red trace to the black trace. (b) Red trace after filtering. (c)  Red trace from (b) after scaling. (d) The final result: red trace from (c) after shifting, which now better matches with the black trace. The amount and order in which these operations is applied affects the final result (Figure \ref{fig:before,after}).}

\section{Filtering}
Perhaps one of the most visibly obvious differences between data sets comes from differences in frequency content.
For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequency content than the black trace which makes it difficult to observe that they may both contain data from the same model.
This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace, since the high frequency content is not physically present in the black trace.

There are several ways to do this.
An naive first approach would be to apply a bandpass filter to the red trace such that the passband covers only frequencies that are present in the black trace.
However, this stationary operation does not take into account the non-stationary frequency variations that may be naturally present in the data.
In order to properly match the data in frequency content, we propose balancing local frequency content between data sets.

We instead do this by applying a non-stationary triangle smoothing operator to the red trace to match local frequency content with the black trace.
We define the {\em radius} of this operator as the number of samples in a specified dimension that are averaged over in a triangle weight.
We allow the radius to vary in all dimensions to account for the potential non-stationary frequency variations present in the data.
This is a linear operation---if we represent the filtering operation by a matrix applied to the trace represented by a vector, the matrix would be diagonally banded, where the size of the band at a particular index is related to the size of the smoothing radius at that point.

Chapter 3 is dedicated to the discussion of how to find this frequency balancing operator.
Figure \ref{fig:one1} shows the two traces after balancing the local frequency content of the red trace to match the black trace.

\section{Scaling}
The second primary data matching operation is scaling. 
Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
Scaling is also a linear operation, and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.

In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces, and represent the diagonal elements of the scaling operator.
%The result of

\section{Shifting}
If two events are slightly misaligned in time, finding the transformation that correctly aligns these events is referred to as {\em shifting}.
Dynamic time warping is a common algorithm used for the alignment of events of two time series, both for geophysical and other applications, as diverse as speech recognition and finance \cite[]{herrera2012,hale2013,dtw,finance}.

In this thesis, I calculate the shifting operator by finding the time shifts that maximize local similarity between the two data sets.
Local similarity extends the concept of local seismic attributes to global correlation coefficients, and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
Unlike filtering and scaling, shifting is a non-linear transformation.
%The time shift calculated is

In certain situations, these data must be correctly aligned in space instead of time; for example, in a depth-migrated image.
In these cases, {\em time} shift is a misnomer. 
However, since the data we are typically dealing with are time series, the shifting operation that we find and apply is considered a function of time.

The result after finding and applying the time shift to the red trace to match it to the black trace is in Figure \ref{fig:one3}.
This shifting operation is discussed in more detail in chapters 3 and 4.

\section{Representation of operators}
Data matching problems are applicable for data sets that have the same physical model, yet have different characteristics that make their comparison difficult.
For example, two seismic traces that were acquired over the same area but with different acquisition methods would benefit by applying data matching operations before their direct comparison. 
These three operations can be applied to one data set to match it with the other.

When applying one operation, we assume the other two operators have already been applied, when this may not be the case.
This is why we balance {\em local} seismic attributes instead of instantaneous ones---we want the match to be accurate in a region of data points rather than a point-by-point match.
These operators must be smooth enough such that any misalignment of one attribute does not affect the result of balancing the others.
%For example, if two traces are not yet matched in time by shifting and a scaling operator is applied, then if a peak and a trough are 
For example, if a scaling operator is applied before the traces have been correctly aligned in time by shifting, 
%such that a peak an and trough are currently aligned, 
too precise of an amplitude balancing operation could inadvertently balance amplitudes to incorrect events.

The order and amount of these operators affects the final result.
After correcting for frequency variations, amplitude variations, and time shifts, additional corrections can be applied to further refine the match if necessary.
In some cases, multiple rounds of applying these operators and in different orders may be beneficial for the best match.
These three operators are noncommutative, so the order in which they are applied matters.
Applying filtering before scaling produces a different result from applying scaling before filtering. 
An illustration of this property is shown in Figure \ref{fig:before,after}.

\multiplot{2}{before,after}{width=1.0\columnwidth}{(a) A lower-resolution seismic trace (black) and a higher-resolution seismic trace (red) acquired over the same area. (b) Data matching operations are noncommutative---the order in which they are applied matters. When matching the red trace to the black trace, the green trace had first smoothing, then amplitude balancing, and finally shifting; the yellow trace had first amplitude balancing, then smoothing, and finally shifting. The operation order matters and affects the final result.}

\begin{table}[h]
\centering
\begin{tabular}{l|l}
\textbf{Operator} & \textbf{Representation} \\ \hline
        Shifting          & $\mathbf{d}_2(x) = \mathbf{d}_1(x + \mathbf{s}(x))$\\
        Scaling           & $\mathbf{d}_2(x) = \mathbf{w}(x)\mathbf{d}_1(x)$\\
        Filtering         & $\mathbf{D}_2(k) = \mathbf{W}(k)\mathbf{D}_1(k)$
\end{tabular}
\caption{Mathematical representation of the three data matching operators.}
\label{op}
\end{table}

A summary of the three data matching operations is shown in Table \ref{op}.
Both scaling and filtering are linear operations, while shifting is generally a non-linear operation.
Additionally, as scaling is to weighting in the time domain, filtering is to weighting in the Fourier domain.
The next chapter discusses a few methods and examples of filtering, or frequency balancing, between two data sets.

### 2018-04-22 chapter-conclusion/paper.tex
almost done with thesis git st

@@
 \maketitle
+
+\subsection{Summary}
+
+In this thesis, I discussed several methods and applications of data matching in seismic data analysis.
+
+Chapter 2 focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
+
+Chapter 3 introduces different methods of frequency balancing using non-stationary smoothing. 
+The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based off of the assumption that the data we observe can be modeled by a summation of Ricker wavelets.
+This method worked well in certain situations, but was not robust enough to work for any given data set.
+In the second method, I introduced an iterative algorithm to find the smoothing radius, and this method converges quickly and works well in several presented situations. 
+Finally, a modification to this algorithm was shown and allows smoothing for more complex data sets.
+
+This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application on matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.
+
+Chapter 4 goes into more detail of the application of matching and merging high-resolution and legacy seismic images.
+This example takes two seismic volumes, acquired over the same area but using different technologies, and first matches them before merging them together to produce an optimized third image.
+First, the method is demonstrated on a 2D line from the Gulf of Mexico.
+Then, the method is applied to a 3D seismic volume from a different part of the Gulf of Mexico.
+
+Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
+It is realized that the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
+An example is applied to a 2D synthetic Sigsbee data set.
+
+\subsection{Future work}
+In the future, the work presented in chapter 5 should be extended to involve real data and 3D examples. 
+It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debflt,prestack,poststack}, to see how it compares in different situations.
+
+Another component to data matching may incorporate the phase of the signal to be matched. 
+Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.
+
+Several applications of data matching were discussed in this thesis. 
+However, there are still many applications that may remain unaddressed from a data matching standpoint. 
+Problems such as seismic and well-log tying, deconvolution, automatic gain control (AGC), and surface-related multiple elimination (SRME) can also be recast as data matching problems, and looking at these problems in a new light may bring advancements to computational geophysics.
+
+\subsection{Code}
+The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagacsar}.
+The package is available at \url{http://www.ahay.org/}.
+
+The reproducible document for the results in this thesis, including code, is available at \url{http://www.sygreer.com/research/honorsThesis}.
+However, some of the data used in this thesis are proprietary, so those results may not directly be reproducible.

### 2018-04-22 chapter-intro/paper.tex
almost done with thesis git st

@@
 These must be properly matched, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
+%Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.
 
-Many other examples of data matching are prevalent in geophysical applications, such as timelapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.
-
-In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
+Many other geophysics applications can be addressed from a data matching standpoint, and fall under a few main categories.
+Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
+Other problems consist of matching differently acquired data, such time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
+Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
+An approach to these many data matching problems is to find the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
+%In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
+In this thesis, I will discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
 
 %However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
-\subsection{Background}
-Seismic data contains fundamentally non-stationary variations in attributes such as frequency and amplitude content.
+The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed in \cite{merge2} and \cite{merge}.
+In this example, two seismic data sets, each acquired over the same area but with different technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
+This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
+Much of the theory behind Chapter 3 was developed in application to this example, but was later extended to other examples.
+As a result, I will be using data from this application throughout much of this thesis.
+
+This thesis contains two primary data sets that I will be referring to. 
+The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
+These two images will always be plotted in the {\em seismic} color map.
+
+The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable}.
+These two images will always be plotted in grayscale.
+In parts of this thesis, I will show a 2D line from this 3D data set for simplicity of plotting.
+
+Two other data sets, both 2D, were used in this paper. 
+In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
+In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in application of improving migration resolution using non-stationary matching.
+
+This thesis is organized as follows.
+In the second chapter, I overview the basics behind the three data matching operations---scaling, shifting, and filtering.
+In chapter three, I introduce two methods for balancing local frequency content in seismic data sets.
+In the fourth chapter, I show the first example of data matching---matching and merging high-resolution and legacy seismic images.
+In the chapter five, I show an example of data matching to improve migration resolution.
+Finally, in chapter six, I provide concluding remarks.

### 2018-04-22 chapter-locfreq/paper.tex
almost done with thesis git st

@@
+%\title{Theory}
+\renewcommand{\thefootnote}{\fnsymbol{footnote}}
 \title{Balancing local frequency content in seismic data using non-stationary smoothing}
+\relax\footnotetext{Parts of this chapter were first published in \cite{locfreq}, \cite{merge2}, and \cite{merge}. This work was done under the supervision of Dr. Sergey Fomel.}
 \author{Sarah Yvonne Greer}
@@
 \begin{abstract}
-        Seismic data can experience non-stationary frequency variations caused by attenuation. This
-        problem is encountered when matching multiple data sets, such as in multicomponent image
-        registration, because signals with differing frequency content are hard to correlate. In
-        this paper, we propose a method to balance frequency content between data sets while taking
-        into account non-stationary frequency variations. This method involves finding and applying
-        a non-stationary smoothing operator to minimize the local frequency difference between data
-        sets. Numerical examples demonstrate that the proposed method improves multicomponent image
-        registration and matching images of differing resolution. 
+        Seismic data can experience non-stationary frequency variations caused by attenuation. 
+        This problem is encountered when matching multiple data sets, such as in multicomponent image registration, because signals with differing frequency content are hard to correlate. 
+        In this chapter, we introduce two methods for balancing frequency content between data sets while taking into account non-stationary frequency variations. 
+        Both methods involve finding and applying a non-stationary smoothing operator to minimize the local frequency difference between data sets. 
+        Numerical examples demonstrate that the proposed method improves multicomponent image registration and matching images of differing resolution. 
 \end{abstract}
@@
 \section{Introduction}
-        Matching seismic data has many applications in geophysical processing methods, such as
-        multi-component image registration, time-lapse image registration, matching well-ties to
-        seismic data, and merging seismic data sets \cite[]{ps,fomel2003,lumley,herrera2012}.
-        Typically, the workflow for matching data involves finding the optimal time shift, or amount
-        of stretching and compressing, of one trace relative to the other that produces the greatest
-        similarity between the two traces, as seen in dynamic time warping and local similarity
-        scanning \cite[]{hale2013, timelapse, herrera}. However, when the two signals that need to
-        be aligned have different spectral content, their comparison can be difficult. Most seismic
-        data experience non-stationary, or spatially and temporally variant, frequency content
-        caused by attenuation. This problem was discussed in application to multicomponent image
-        registration by \cite{fomel2003}, who applied frequency balancing methods to improve
-        registration results. \cite{ltft} proposed using local time-frequency decomposition (LTFD)
-        to balance frequencies between multicomponent data during registration. However, LTFD is a
-        relatively computationally expensive method.
+        Matching seismic data has many applications in geophysical processing methods, such as multi-component image registration, time-lapse image registration, matching well-ties to seismic data, and merging seismic data sets \cite[]{ps,fomel2003,lumley,herrera2012}.
+        Typically, the workflow for matching data involves finding the optimal time shift, or amount of stretching and compressing, of one trace relative to the other that produces the greatest similarity between the two traces, as seen in dynamic time warping and local similarity scanning \cite[]{hale2013, timelapse, herrera}.
+        However, when the two signals that need to be aligned have different spectral content, their comparison can be difficult. 
+        Most seismic data experience non-stationary, or spatially and temporally variant, frequency content caused by attenuation. 
+        This problem was discussed in application to multicomponent image registration by \cite{fomel2003}, who applied frequency balancing methods to improve registration results. 
+        \cite{ltft} proposed using local time-frequency decomposition (LTFD) to balance frequencies between multicomponent data during registration. 
+        However, LTFD is a relatively computationally expensive method.
 
-        In this paper, we propose a method to remove non-stationary frequency differences that limit
-        the effectiveness of matching data. We suggest applying the proposed method to processing
-        flows that involve matching data before attempting to find the time shift to align their
-        signal content. To balance frequency content, we use a non-stationary smoothing operator
-        with an adjustable smoothing radius to apply to the higher frequency data set. Our approach
-        takes the form of an optimization problem which is solved using an iterative method. We
-        apply this method to examples of merging high-resolution and conventional seismic images and
-        multicomponent image registration.
+        In this chapter, we propose methods for removing non-stationary frequency differences that limit the effectiveness of matching data. 
+        We suggest applying the either of the proposed methods to processing flows that involve matching data before attempting to find the time shift to align their signal content. 
+        To balance frequency content, we use a non-stationary smoothing operator with an adjustable smoothing radius to apply to the higher frequency data set. 
+        Our first approach finds the smoothing operator directly, but is based on the primary assumption that the data can be modeled by a summation of Ricker wavelets. 
+        Our second approach of finding the smoothing radius is based on understanding what the smoothing operator physically does, and takes the form of an optimization problem which is solved using an iterative method.
+        We introduce these methods and apply them to examples of merging high-resolution and conventional seismic images and multicomponent image registration.
 
@@
 \inputdir{merge}
-        Two signals of differing frequencies are more difficult to correlate than signals of similar
-        frequencies.  For example, Figure \ref{fig:legacy,hires-agc} shows two seismic images
-        representing the same subsurface, except they have distinctly different spectral content, as
-        shown in Figure \ref{fig:nspectra-orig}. In order to be directly comparable, these two
-        images should have similar frequency content.
-        In this paper, we look at local frequency \cite[]{attr}, which can be thought of as a
-        smoothed estimate of instantaneous frequency \cite[]{white}. Local frequency is a more
-        geologically accurate attribute than instantaneous frequency because it honors
-        time-frequency uncertainty and does not contain physically unrealistic negative or extremely
-        high frequency values \cite[]{attr}.
+        Two signals of differing frequencies are more difficult to correlate than signals of similar frequencies.  
+        For example, Figure \ref{fig:legacy,hires-agc} shows two seismic images representing the same subsurface, except they have distinctly different spectral content, as shown in Figure \ref{fig:nspectra-orig}.
+        In order to be directly comparable, these two images should have similar frequency content.
+        Here, we look at local frequency \cite[]{attr}, which can be thought of as a smoothed estimate of instantaneous frequency \cite[]{white}. 
+        Local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.
 
-        In order to balance local frequency content, we propose smoothing the higher frequency data
-        using a non-stationary triangle smoothing operator with an adjustable radius. Here, the
-        radius at each point is the number of samples in time that that specific data point gets 
-        averaged over
-        %in either direction 
-        in a triangle weight.
+        In order to balance local frequency content, we propose smoothing the higher frequency data using a non-stationary triangle smoothing operator with an adjustable radius. 
+        Here, the radius at each point is the number of samples in time that that specific data point gets averaged over in a triangle weight.
+
+        In order to find the temporally and spatially variable smoothing radius that we need to apply to the higher frequency image to balance local frequency content with the lower frequency image, we take two approaches.
+        The first approach is finding the smoothing radius based on assumptions of what the data we are looking at can be represented by, and the second approach is based on understanding physically what non-stationary smoothing does to a data set.
+        Both approaches work well in different situations---the first approach is less computationally expensive than the second approach, but is only applicable when the two data sets fit the assumptions that are used to calculate what the smoothing radius is.
+        The second approach finds the smoothing radius in an iterative manner, but manages to work well for any data set given to it.
+
+        \subsection{Theoretical smoothing radius}
+\inputdir{../chapter-merge/apache}
+        %A more effective method, which accounts for temporally and spatially variable frequency content that is present in most seismic data, is to apply a non-stationary filter using frequency information from both images.
+        To demonstrate the effectiveness of finding the smoothing radius using this method, we use the {\it Apache} seismic data sets.
+        The two initial images are shown in Figure \ref{fig:legacy,hires}, and their frequency content are shown in Figure \ref{fig:nspectra}.
+
+        To balance the non-stationary frequency variations between data sets, we use a simple triangle smoothing operator with an adjustable radius. 
+        Here, the radius at each point is the amount of time, in seconds, that that specific data point gets averaged over in a triangle weight in the temporal direction.
+        We specifically look at local frequency \cite[]{attr}, which is a time-dependent frequency attribute, and can be thought of as a smoothed estimate of instantaneous frequency \cite[]{white}. 
+%        For the procedures described in this thesis, local frequency is a better-suited attribute than instantaneous frequency.
+%        Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
+%        Because the corresponding reflections between images may not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
+
+        \multiplot{2}{legacy,hires}{width=0.47\columnwidth}{The initial legacy (a) and high-resolution (b) images.}
+        \multiplot{2}{nspectra,hires-smooth-spec}{width=0.47\columnwidth}{Spectra for the entire image display of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing using the theoretical method.}
+
+        This method is based off of the primary assumption that the signal can be represented by Ricker wavelets convolved with the Earth's reflectivity series.
+        Since the data we are working with are seismic, this can be a good assumption \cite[]{ricker}.
+
+        The justification for triangle smoothing is that it is a simple approximation to Gaussian smoothing. 
+        The frequency response of the triangle smoothing filter \cite[]{pvi} is
+        \begin{equation}
+            \label{eq:Tf}
+            T(f) = \mathrm{sinc}^2\left(\frac{2\pi f \Delta t}{2}\right) \approx 1-\frac{(2\pi f)^2(\Delta t)^2}{12}\;.
+        \end{equation}
+        This frequency response resembles that of a Gaussian:
+        \begin{equation}
+            \label{eq:gaussian}
+            G(f) = e^{-\alpha f^2} \approx 1 - \alpha f^2\;.
+        \end{equation}
+        If the signals' spectra can be represented by Ricker wavelets,
+        \begin{equation} 
+            \label{eq:Sn}
+            S_{n}(f) = A_{n} \left(\frac{f}{f_{n}}\right)^2e^{-\left(\frac{f}{f_{n}}\right)^{2}}\,
+        \end{equation}
+        where, in image $n$, $S_n$ is the frequency spectrum, $f_n$ is the peak frequency, and $A_n$ is the amplitude, Gaussian smoothing can transform the signal to a different dominant frequency.
+
+        Because we are smoothing the high-resolution image to match it with the legacy image, we can relate the high-resolution frequencies, $S_h$, to the legacy frequencies, $S_l$, such that
+        \begin{equation} 
+            \label{eq:smooth}
+            S_{l}(f)=A e^{-\alpha f^2}\,S_h(f)      
+        \end{equation}
+        where $A=A_l/A_h$,
+        \begin{equation}
+            \label{eq:alpha}
+            \alpha = \frac{1}{f_l^2}-\frac{1}{f_h^2} \;,
+        \end{equation}
+        and the subscripts $l$ and $h$ correspond to the legacy and high-resolution images, respectively.
+
+        Combining equations~(\ref{eq:Tf}), (\ref{eq:gaussian}), and (\ref{eq:alpha}) leads to the specification of the triangle smoothing radius as
+        \begin{equation}
+            \label{eq:radius}
+            \Delta t \approx \frac{1}{2\pi}\sqrt{12\left(\frac{1}{f_{l}^{2}}-\frac{1}{f_{h}^{2}}\right)}\;.
+        \end{equation}
+        Here, $\Delta t$ is the radius of smoothing, measured in seconds, applied to the high-resolution image to match the frequency content with the legacy image at each sample. 
+        The calculated smoothing radius for this data set is shown in Figure \ref{fig:rect}.
+
+        \plot{rect}{width=0.6\columnwidth}{Calculated spatially and temporally variable smoothing radius.
+This represents the number of seconds in the temporal direction that the high-resolution image gets averaged over in a triangle weight to balance local frequency content with the legacy image at each sample.}
+
+        We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
+        Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
+        In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
+        Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. 
+        After smoothing, the frequency difference is minimized.
+
+        This method works well for simple data sets with overlapping frequency content. 
+        However, more complicated data sets, as seen in the next example, may require additional steps for successful frequency balancing.
+
+        \multiplot{2}{freqdif,freqdif-filt}{width=0.47\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
 
@@
 
-        Our goal is to find the temporally and spatially variable smoothing radius, $\mathbf{R}$, that
-        minimizes the difference in local frequencies between the two data sets. This can be shown
-        in the objective function
+        \subsection{Iterative method for calculating the smoothing radius}
+        \inputdir{merge}
+        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it doesn't work in situations where there is not much overlap in frequency content between data sets, like in the second example of the next chapter.
+        In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.
+
+        The goal of this method is to find the temporally and spatially variable smoothing radius, $\mathbf{R}$, that minimizes the difference in local frequencies between the two data sets. 
+        This can be shown in the objective function
         \begin{equation}
@@
         \end{equation}
-        where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius
-        $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower
-        frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of
-        the smoothing radius.
-        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends
-        non-linearly on $R$. However, the objective from equation (\ref{eq:obj}) is nearly convex,
-        and we choose to use an intuitive iterative approach to find an approximate smoothing
-        radius.
+        where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of the smoothing radius.
+        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends non-linearly on $R$.
+However, the objective from equation (\ref{eq:obj}) is nearly convex, and we choose to use an intuitive iterative approach to find an approximate smoothing radius.
 
-        The main premise behind the method comes from the fact that, in general, 
-        %the more samples the data are smoothed over, 
-        the greater the smoothing radius, the more high frequencies are attenuated by smoothing.
-        We choose an initial guess of the non-stationary smoothing radius before applying
-        corrections based on two primary assumptions:
+        The main premise behind the method comes from the fact that, in general, the greater the smoothing radius, the more high frequencies are attenuated by smoothing. 
         \begin{enumerate}
-        \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the
-                higher frequency data has \emph{higher} local frequency than the lower frequency
-                data. Thus, the smoothing radius must be \emph{increased} at that point. 
-        \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the
-                higher frequency data has \emph{lower} local frequency than the lower frequency
-                data. Thus, the smoothing radius must be \emph{decreased} at that point.
+        \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the higher frequency data has \emph{higher} local frequency than the lower frequency data.
+Thus, the smoothing radius must be \emph{increased} at that point.
+        \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the higher frequency data has \emph{lower} local frequency than the lower frequency data.
+Thus, the smoothing radius must be \emph{decreased} at that point.
         \end{enumerate}
@@
                         \begin{equation}
-                               \label{eq:ls}
-                               \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \mathbf{r}^{(i)},
+                               \label{eq:alg}
+                               \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ c \mathbf{r}^{(i)},
                         \end{equation}
-        where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $\alpha$ is a
-        scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the
-        residual at the $i$th iteration, which can be thought of as the search direction, and is
-        defined as
+        where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $c$ is a scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the residual at the $i$th iteration, which can be thought of as the search direction, and is defined as
           \begin{equation}
@@
           \end{equation}
-        It can be noted that when equation (\ref{eq:residual}) is positive, the higher frequency
-        data still has a higher local frequency value at that specific point than the lower
-        frequency data, thus the higher frequency data is under-smoothed and the smoothing radius
-        should be increased at that point. This follows the form of the first assumption. The second
-        assumption is used when equation (\ref{eq:residual}) is negative. When equation
-        (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections
-        are made. Thus, it is justifiable to set the search direction from equation (\ref{eq:ls})
-        equal to the residual.
+        It can be noted that when equation (\ref{eq:residual}) is positive, the higher frequency data still has a higher local frequency value at that specific point than the lower frequency data, thus the higher frequency data is under-smoothed and the smoothing radius should be increased at that point.
+This follows the form of the first assumption.
+        The second assumption is used when equation (\ref{eq:residual}) is negative. 
+        When equation (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections are made. 
+        Thus, it is justifiable to set the search direction from equation (\ref{eq:alg}) equal to the residual.
 
-        Using the two assumptions, we can continually adjust the smoothing radius until we 
-        achieve the desired result of balancing the local frequency content between the two data
-        sets. In practice, this method produces an acceptable solution in approximately 5 iterations
-        and exhibits sublinear convergence. After smoothing the higher frequency data with the
-        estimated radius, we use the lower frequency and smoothed higher frequency data to estimate
-        time shifts and align the two data sets.
+        Using the assumptions, we can choose an intial guess for the smoothing radius and continually adjust the smoothing radius until we  achieve the desired result of balancing the local frequency content between the two data sets.
+        In practice, this method produces an acceptable solution in approximately 5 iterations and exhibits sublinear convergence.
+After smoothing the higher frequency data with the estimated radius, we use the lower frequency and smoothed higher frequency data to estimate time shifts and align the two data sets.
 
-\section{Examples}
-        This method is applicable to workflows that require matching data with different frequency
-        content. In this paper, we demonstrate two examples where smoothing data before matching
-        produces better results.
+%\section{Examples}
+        This method is applicable to workflows that require matching data with different frequency content. 
+        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images produces better results.
 
-        \subsection{Matching legacy and high-resolution images}
-        High-resolution seismic data, such as those acquired with the P-cable acquisition system,
-        can produce very detailed images of the near subsurface \cite[]{tip}. When compared to
-        conventional seismic images, high-resolution images have a higher dominant frequency and a
-        larger frequency bandwidth. However, they usually lack low frequency content and depth
-        coverage that is present in conventional seismic images. As a result, successful
-        interpretation of high-resolution images can be aided by matching with legacy data coverage
-        over the same area.
+%        \subsection{Matching legacy and high-resolution images}
+        High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
+        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a larger frequency bandwidth. 
+        However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
+        As a result, successful interpretation of high-resolution images can be aided by matching with legacy data coverage over the same area.
 
-        \multiplot{2}{legacy,hires-agc}{width=0.9\columnwidth}{Initial legacy (a) and
-        high-resolution (b) images. These images show the same subsurface geology, but look
-        remarkably different as the high-resolution image has distinctly higher frequency content
-        than the legacy image.}
+        \multiplot{2}{legacy,hires-agc}{width=0.7\columnwidth}{Initial legacy (a) and high-resolution (b) images. 
+                These images show the same subsurface geology, but look remarkably different as the high-resolution image has distinctly higher frequency content than the legacy image.}
 
-        \plot{rect5}{width=0.9\columnwidth}{The smoothing radius, which is a function of time and
-        space, this method produces after 5 iterations. This represents the number of samples in
-        time that the high-resolution image needs to be smoothed over in a triangle weight %in time
-        to balance local frequency content with the legacy image.}
+        \plot{rect5}{width=0.6\columnwidth}{The smoothing radius, which is a function of time and space, this method produces after 5 iterations.
+This represents the number of samples in time that the high-resolution image needs to be smoothed over in a triangle weight to balance local frequency content with the legacy image.}
 
-        Example legacy and high-resolution images of the same subsurface are shown in Figure
-        \ref{fig:legacy,hires-agc}. The first step in matching the two images is to ensure that they
-        both have a similar frequency bandwidth so they are directly comparable. The average frequency
-        spectra for the two images are shown in Figure \ref{fig:nspectra-orig}. From this, it is
-        evident that there is almost no overlap in frequency bandwidth between the two images.
-        To address this problem, we apply a low-cut filter to the legacy image to remove some of the
-        lower frequencies that are simply not present in the high-resolution image. Next, we
-        implement the method described in the previous section to balance local frequency content
-        between the two images. The difference in local frequencies (residual, by equation
-        \ref{eq:residual}) between the high-resolution and legacy images before balancing frequency
-        content and after 5 iterations of the algorithm in equation (\ref{eq:ls}) is shown in Figure
-        \ref{fig:freqdif,freqdif-filt5}. After balancing local frequencies, the images show a
-        similar spectral bandwidth (Figure \ref{fig:high-smooth-spec5}), which helps increase the
-        correlation between the two images and makes matching reflections better defined.
+        Example legacy and high-resolution images of the same subsurface are shown in Figure \ref{fig:legacy,hires-agc}. 
+        The first step in matching the two images is to ensure that they both have a similar frequency bandwidth so they are directly comparable. 
+        The average frequency spectra for the two images are shown in Figure \ref{fig:nspectra-orig}. 
+        From this, it is evident that there is almost no overlap in frequency bandwidth between the two images.
+        To address this problem, we apply a low-cut filter to the legacy image to remove some of the lower frequencies that are simply not present in the high-resolution image. 
+        Next, we implement the method described in the previous section to balance local frequency content between the two images. 
+        The difference in local frequencies (residual, by equation \ref{eq:residual}) between the high-resolution and legacy images before balancing frequency content and after 5 iterations of the algorithm in equation (\ref{eq:alg}) is shown in Figure \ref{fig:freqdif,freqdif-filt5}.
+        After balancing local frequencies, the images show a similar spectral bandwidth (Figure \ref{fig:high-smooth-spec5}), which helps increase the correlation between the two images and makes matching reflections better defined.
 
-        After the frequency content is matched, the optimal time shift is found to align signal
-        content between the legacy and high-resolution images. We then apply this time shift to
-        %the original legacy and high-resolution images---the frequency content is only degraded for
-        the original high-resolution image---the frequency content is only degraded for the purpose
-        of finding the time shift.
+        After the frequency content is matched, the optimal time shift is found to align signal content between the legacy and high-resolution images.
+We then apply this time shift to the original high-resolution image---the frequency content is only degraded for the purpose of finding the time shift.
 
-        An application of aligning the high-resolution and legacy images is discussed in the companion
-        paper \cite[]{merge}.
+        An application of aligning the high-resolution and legacy images is discussed in the next chapter.
 
-        \multiplot{2}{nspectra-orig,high-smooth-spec5}{width=0.81\columnwidth}{Spectral content of
-        the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral
-        balancing.}
+        \multiplot{2}{nspectra-orig,high-smooth-spec5}{width=0.47\columnwidth}{Spectral content of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing using the theoretical method.}
 
-\subsection{Multicomponent image registration}
-        Multicomponent seismic image registration is an important step before the interpretation of
-        P and S images of the subsurface. It involves warping the space of S images to align
-        reflections with the analogous reflections of P images \cite[]{fomel2003,warp}.
+%\subsection{Multicomponent image registration}
+\subsection{Iterative method for calculating the smoothing radius: A modification}
+        The algorithm previously presented works well in cases when one data set has clearly higher frequency content than the other.
+        %However, this need not always be the case.
+        However, in some cases, the two data sets may have similar local frequency content, but they may still need to be matched.
+        We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.
+
+        Multicomponent seismic image registration is an important step before the interpretation of P and S images of the subsurface.
+It involves warping the space of S images to align reflections with the analogous reflections of P images \cite[]{fomel2003,warp}.
 
         Figure \ref{fig:pp,ss} shows PP and SS images from a 9-component seismic survey \cite[]{attr}.
-        To properly register the images, we follow the
-        method proposed in \cite{warp}. It consists of three primary steps: (1) initial registration
-        of PP and SS images using initial interpretation and well-log analysis; (2) balancing
-        frequency and amplitude content; and (3) final registration using residual local similarity
-        scanning. We incorporate our method of balancing frequency content into the second step in
-        this process.
+        To properly register the images, we follow the method proposed in \cite{warp}. 
+        It consists of three primary steps: (1) initial registration of PP and SS images using initial interpretation and well-log analysis; (2) balancing frequency and amplitude content; and (3) final registration using residual local similarity scanning.
+        We incorporate our method of balancing frequency content into the second step in this process.
 
@@
 
-        \multiplot{2}{freqdif,freqdif-filt5}{width=0.81\columnwidth}{Difference in local frequencies
+        \multiplot{2}{freqdif,freqdif-filt5}{width=0.47\columnwidth}{Difference in local frequencies
         (residual) between the legacy and high-resolution images before (a) and after (b) the 5th
@@
             \end{equation}
-        The ideal radius is still found using the same line-search from equation (\ref{eq:ls}),
+        The ideal radius is still found using the same line-search from equation (\ref{eq:alg}),
         except we allow the smoothing radius to be negative. Physically, a negative smoothing radius
@@
 \inputdir{vecta}
-        \multiplot{2}{pp,ss}{width=0.85\columnwidth}{Initial PP (a) and SS (b) images.}
+        \multiplot{2}{pp,ss}{width=0.7\columnwidth}{Initial PP (a) and SS (b) images.}
 
         The results of using this spectral balancing method are shown in Figure
-        \ref{fig:before,after}. Comparable results were achieved in \cite{ltft}, who used LTFD to
+        \ref{fig:before,after}. Comparable results were achieved in \cite{ltft}, who used local time-frequency decomposition (LTFD) to
         balance the spectral content between the two images. However, the method we propose in this
-        paper is more straightforward and significantly less computationally expensive.
+        chapter is more straightforward and significantly less computationally expensive.
 
-\section{Conclusions}
-        It is difficult to compare signals with differing frequency content because signals with
-        differing frequencies are hard to correlate. In this paper, we proposed a method of
-        balancing frequency content between data which takes the form of an optimization problem
-        solved by a simple iterative algorithm. It is a relatively inexpensive and effective method
-        compared to previously proposed methods of balancing frequencies between data sets. We
-        applied this method to examples of matching seismic images of differing resolution and for
-        multicomponent image registration.
+        So far, this algorithm and its modification have been discussed when the smoothing radius is only calculated along one dimension. 
+        However, Chapter 5 provides an application where the smoothing radius is calculated in multiple directions.
 
-        \multiplot{2}{before,after}{width=0.85\columnwidth}{Interleaved PP and warped SS traces before
+        \multiplot{2}{before,after}{width=0.65\columnwidth}{Interleaved PP and warped SS traces before
         (a) and after (b) frequency balancing and residual registration. After registration, the
@@
 
+\section{Convergence analysis}
+\inputdir{convergence}
+        Since this algorithm was developed from observations and intuition based on what smoothing is physically doing, no error analysis or convergence criteria has been developed in this thesis.
+        However, it is observed that this algorithm generally exhibits sublinear convergence.
+        Additionally, the initial guess for what the smoothing radius should be negligibly impacts the final result.
+        Figure \ref{fig:all} shows the convergence of the algorithm from equation (\ref{eq:alg}) when applied to the {\em P-cable} data set from the second example in this chapter (Figure \ref{fig:legacy,hires-agc}).
+        It is evident that no matter the initial guess, the resulting convergence is relatively unaffected, and with the correct choice of step length $c$, converges in few iterations.
+        After convergence, continuing iterations do not affect the final result.
+
+        Figure \ref{fig:scalar} shows the convergence when choosing different values of $c$, the step length from Equation (\ref{eq:alg}).
+        From this, it is evident that the step length is important for fast and stable convergence. 
+        If too large a step length is chosen, the method does not converge to the ideal solution.
+        If the step length is too small, the algorithm takes many more iterations to converge.
+        With the ``correct'' step length, however, the algorithm usually converges in under 10 iterations in practice.
+
+        \multiplot{2}{all,scalar}{width=0.95\columnwidth}{Convergence of the algorithm from Equation (\ref{eq:alg}) for (a) different initial guesses, and (b) different choices of $c$, the step length, using the theoretical radius as the initial guess.}
+
+\section{Conclusions}
+        It is difficult to compare signals with differing frequency content because signals with
+        differing frequencies are hard to correlate. In this chapter, we proposed two methods of
+        balancing frequency content between data. 
+        The first one takes a theoretical approach of what we expect the data to be, and the second one takes the form of an optimization problem
+        solved by a simple iterative algorithm. This algorithm is a relatively inexpensive and effective method
+        compared to previously proposed methods of balancing frequencies between data sets. We
+        applied these methods to examples of matching seismic images of differing resolution and for
+        multicomponent image registration.
+
 \section{Acknowledgements}
@@
         financial support.
-
-\onecolumn
-
+%
+%\onecolumn
+%
 %\bibliographystyle{seg}

### 2018-04-22 chapter-merge/paper.tex
almost done with thesis git st

@@
 \author{Sarah Greer and Sergey Fomel, The University of Texas at Austin}
+\relax\footnotetext{Parts of this chapter were first published in \cite{merge2}.
+The peer-reviewed journal version appears as \cite{merge}.
+This work was done under the supervision of Dr.
+Sergey Fomel.}
 
@@
 
-    In this paper, we consider the problem of matching seismic images obtained in the same area with different resolution. 
+    In this chapter, we consider the problem of matching seismic images obtained in the same area with different resolution. 
     Using techniques borrowed from multicomponent image processing \cite[]{warp}, we propose a multistep approach. 
@@
     Analyzing the spectra of the legacy and high-resolution images, as seen in Figure \ref{fig:nspectra}, it is clear that the high-resolution image has a wider range of frequencies with a higher dominant frequency than the legacy image.
+%    \multiplot{2}{nspectra,hires-smooth-spec}{width=0.47\columnwidth}{Spectra for the entire image display of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}
     In order to match these images, our first step is to balance their spectral content. 
@@
     Here, the radius at each point is the amount of time, in seconds, that that specific data point gets averaged over in a triangle weight in the temporal direction.
-    We specifically look at local frequency \cite[]{attr}, which is a time-dependent frequency attribute, and can be thought of as a smoothed estimate of instantaneous frequency \cite[]{white}. 
-    For the procedure described in this paper, local frequency is a better-suited attribute than instantaneous frequency.
-    Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
-    Because the corresponding reflections between images may not be precisely aligned in time at this stage in the method, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
-
-    \multiplot{2}{nspectra,hires-smooth-spec}{width=0.68\columnwidth}{Spectra for the entire image display of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}
-
-    The justification for triangle smoothing is that it is a simple approximation to Gaussian smoothing. The frequency response of the triangle smoothing filter \cite[]{pvi} is
+    In this example, we find the radius of smoothing using the theoretical approach described in the previous chapter, so 
     \begin{equation}
-        \label{eq:Tf}
-        T(f) = \mathrm{sinc}^2\left(\frac{2\pi f \Delta t}{2}\right) \approx 1-\frac{(2\pi f)^2(\Delta t)^2}{12}\;.
-    \end{equation}
-    This frequency response resembles that of a Gaussian:
-    \begin{equation}
-        \label{eq:gaussian}
-        G(f) = e^{-\alpha f^2} \approx 1 - \alpha f^2\;.
-    \end{equation}
-    If the signals' spectra can be represented by Ricker wavelets,
-    \begin{equation} 
-        \label{eq:Sn}
-        S_{n}(f) = A_{n} \left(\frac{f}{f_{n}}\right)^2e^{-\left(\frac{f}{f_{n}}\right)^{2}}\,
-    \end{equation}
-    where, in image $n$, $S_n$ is the frequency spectrum, $f_n$ is the peak frequency, and $A_n$ is the amplitude, Gaussian smoothing can transform the signal to a different dominant frequency.
-
-    Because we are smoothing the high-resolution image to match it with the legacy image, we can relate the high-resolution frequencies, $S_h$, to the legacy frequencies, $S_l$, such that
-    \begin{equation} 
-        \label{eq:smooth}
-        S_{l}(f)=A e^{-\alpha f^2}\,S_h(f)      
-    \end{equation}
-    where $A=A_l/A_h$,
-    \begin{equation}
-        \label{eq:alpha}
-        \alpha = \frac{1}{f_l^2}-\frac{1}{f_h^2} \;,
-    \end{equation}
-    and the subscripts $l$ and $h$ correspond to the legacy and high-resolution images, respectively.
-
-    Combining equations~(\ref{eq:Tf}), (\ref{eq:gaussian}), and (\ref{eq:alpha}) leads to the specification of the triangle smoothing radius as
-    \begin{equation}
-        \label{eq:radius}
+        \label{eq:rad}
         \Delta t \approx \frac{1}{2\pi}\sqrt{12\left(\frac{1}{f_{l}^{2}}-\frac{1}{f_{h}^{2}}\right)}\;.
     \end{equation}
-    Here, $\Delta t$ is the radius of smoothing, measured in seconds, applied to the high-resolution image to match the frequency content with the legacy image at each sample. 
-    The calculated smoothing radius for this data set is shown in Figure \ref{fig:rect}.
+    Here, $f_l$ and $f_h$ are the local frequencies of the legacy and high-resolution images, respectively, and $\Delta t$ is the radius of smoothing, measured in seconds, applied to the high-resolution image to match the frequency content with the legacy image at each sample.
+    The spectral content of the high resolution image after balancing local frequencies clearly closer resembles that of the legacy image, as shown in Figure \ref{fig:hires-smooth-spec}.
+    %We specifically look at local frequency \cite[]{attr}, which is a time-dependent frequency attribute, and can be thought of as a smoothed estimate of instantaneous frequency \cite[]{white}. 
+    %For the procedure described in this paper, local frequency is a better-suited attribute than instantaneous frequency.
+    %Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
+    %Because the corresponding reflections between images may not be precisely aligned in time at this stage in the method, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
+    %
+    %\multiplot{2}{nspectra,hires-smooth-spec}{width=0.68\columnwidth}{Spectra for the entire image display of the legacy (red) and high-resolution (blue) images before (a) and after (b) spectral balancing.}
+    %
+    %The justification for triangle smoothing is that it is a simple approximation to Gaussian smoothing. The frequency response of the triangle smoothing filter \cite[]{pvi} is
+    %\begin{equation}
+    %    \label{eq:Tf}
+    %    T(f) = \mathrm{sinc}^2\left(\frac{2\pi f \Delta t}{2}\right) \approx 1-\frac{(2\pi f)^2(\Delta t)^2}{12}\;.
+    %\end{equation}
+    %This frequency response resembles that of a Gaussian:
+    %\begin{equation}
+    %    \label{eq:gaussian}
+    %    G(f) = e^{-\alpha f^2} \approx 1 - \alpha f^2\;.
+    %\end{equation}
+    %If the signals' spectra can be represented by Ricker wavelets,
+    %\begin{equation} 
+    %    \label{eq:Sn}
+    %    S_{n}(f) = A_{n} \left(\frac{f}{f_{n}}\right)^2e^{-\left(\frac{f}{f_{n}}\right)^{2}}\,
+    %\end{equation}
+    %where, in image $n$, $S_n$ is the frequency spectrum, $f_n$ is the peak frequency, and $A_n$ is the amplitude, Gaussian smoothing can transform the signal to a different dominant frequency.
+    %
+    %Because we are smoothing the high-resolution image to match it with the legacy image, we can relate the high-resolution frequencies, $S_h$, to the legacy frequencies, $S_l$, such that
+    %\begin{equation} 
+    %    \label{eq:smooth}
+    %    S_{l}(f)=A e^{-\alpha f^2}\,S_h(f)      
+    %\end{equation}
+    %where $A=A_l/A_h$,
+    %\begin{equation}
+    %    \label{eq:alpha}
+    %    \alpha = \frac{1}{f_l^2}-\frac{1}{f_h^2} \;,
+    %\end{equation}
+    %and the subscripts $l$ and $h$ correspond to the legacy and high-resolution images, respectively.
+    %
+    %Combining equations~(\ref{eq:Tf}), (\ref{eq:gaussian}), and (\ref{eq:alpha}) leads to the specification of the triangle smoothing radius as
+    %\begin{equation}
+    %    \label{eq:radius}
+    %    \Delta t \approx \frac{1}{2\pi}\sqrt{12\left(\frac{1}{f_{l}^{2}}-\frac{1}{f_{h}^{2}}\right)}\;.
+    %\end{equation}
+    %Here, $\Delta t$ is the radius of smoothing, measured in seconds, applied to the high-resolution image to match the frequency content with the legacy image at each sample. 
+    %The calculated smoothing radius for this data set is shown in Figure \ref{fig:rect}.
+    %
+    %\plot{rect}{width=0.75\columnwidth}{Calculated spatially and temporally variable smoothing radius.
+This represents the number of seconds in the temporal direction that the high-resolution image gets averaged over in a triangle weight to balance local frequency content with the legacy image at each sample.}
+    %
+    %We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
+    %Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
+    %In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
+    %Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing.
 
-    \plot{rect}{width=0.75\columnwidth}{Calculated spatially and temporally variable smoothing radius.
-This represents the number of seconds in the temporal direction that the high-resolution image gets averaged over in a triangle weight to balance local frequency content with the legacy image at each sample.}
-
-    We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
-    Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
-    In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
-    Figure \ref{fig:freqdif,freqdif-filt} shows the difference in local frequencies before and after smoothing. 
-    After smoothing, the frequency difference is minimized.
+%    After smoothing, the frequency difference is minimized.
 
@@
 
-    \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
+%%    \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
 
@@
     \begin{equation}
-        \label{eq:ls}
+        \label{eq:lsf}
         \left[\begin{array}{c} \mathbf{W_h} \\
@@
     \end{equation}
-    where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$ are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary smoothing specified by equation (\ref{eq:radius}).
-    The formal solution of the least-squares problem~(\ref{eq:ls}) is
+    where $\mathbf{h}$ denotes the high-resolution image, $\mathbf{l}$ is the legacy image, $\mathbf{b}$ is the desired blended image, $\mathbf{W_h}$ and $\mathbf{W_l}$ are the diagonal weighting matrices for the high-resolution and legacy images, respectively, and $\mathbf{S}$ is the non-stationary smoothing specified by equation (\ref{eq:rad}).
+    The formal solution of the least-squares problem~(\ref{eq:lsf}) is
     \begin{eqnarray}
@@
 
-    \plot{nspectra22-reverse}{width=0.90\columnwidth}{The spectra of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and merged (magenta solid) images for the first data set.}
+    \plot{nspectra22-reverse}{width=0.75\columnwidth}{The spectra of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and merged (magenta solid) images for the first data set.}
 
@@
 
-    Although the method presented in this paper is applied to post-stack images, the general method is likely flexible enough to be extended to pre-stack data.
+    Although the method presented in this chapter is applied to post-stack images, the general method is likely flexible enough to be extended to pre-stack data.
     Applications of matching legacy and high-resolution seismic data are also seen in time-lapse image registration, where the accurate interpretation of 4D time-lapse data heavily depends on dataset alignment and uniform processing \cite[]{nonuniform}.
-    The method from this paper could also be used in 4D time-lapse processing; particularly the steps involving frequency balancing and accounting for time shifts.
+    The method from this chapter could also be used in 4D time-lapse processing; particularly the steps involving frequency balancing and accounting for time shifts.
 
@@
     Because there is not much overlap in frequency bandwidth, balancing their spectral content is challenging. 
-    In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:radius}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption.
-    As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:radius}) to ensure matching frequency content.
+    In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:rad}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption.
+    As a result, additional steps must be taken beyond applying the smoothing specified by equation~(\ref{eq:rad}) to ensure matching frequency content. 
+    \plot{nspectra2}{width=0.75\columnwidth}{The spectral content of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and resultant merged (magenta solid) images for the second data set.}
 
     We first apply a low-cut filter to the legacy data to remove the low frequency information that is simply not present in the high-resolution image. 
-    Next, we adjust the non-stationary smoothing radius using a simple iterative algorithm \cite[]{locfreq}.
+    Next, we adjust the non-stationary smoothing radius using the simple iterative algorithm \cite[]{locfreq} that was described in the previous chapter.
 
-    The main premise behind the algorithm comes from the fact that, in general, the greater the smoothing radius at a specified point, the more high frequencies are attenuated by smoothing.
-    We choose an initial guess of the non-stationary smoothing radius before applying corrections based on two primary assumptions:
-    \begin{enumerate}
-    \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the high-resolution image has \emph{higher} local frequency than the legacy image.
+%    The main premise behind the algorithm comes from the fact that, in general, the greater the smoothing radius at a specified point, the more high frequencies are attenuated by smoothing.
+%    We choose an initial guess of the non-stationary smoothing radius before applying corrections based on two primary assumptions:
+%    \begin{enumerate}
+%    \item The smoothing radius is too \emph{small} at a specified point if, after smoothing, the high-resolution image has \emph{higher} local frequency than the legacy image.
 Thus, the smoothing radius must be \emph{increased} at that point.
-    \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the high-resolution image has \emph{lower} local frequency than the legacy image.
+%    \item The smoothing radius is too \emph{large} at a specified point if, after smoothing, the high-resolution image has \emph{lower} local frequency than the legacy image.
 Thus, the smoothing radius must be \emph{decreased} at that point.
-    \end{enumerate}
-
-    We apply these assumptions using a line-search method:
-    \begin{equation}
-        \label{eq:linesearch}
-        \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \mathbf{r}^{(i)},
-    \end{equation}
-    where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $\alpha$ is a scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the residual at the $i$th iteration, which can be thought of as the search direction, and is
-    defined as
-    \begin{equation}
-        \label{eq:residual}
-        \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}} \mathbf{d}_h] - \mathbf{F}[\mathbf{d}_l]\;,
-    \end{equation}
-    where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the high-resolution image, $\mathbf{d}_l$ is the legacy image, and $\mathbf{F}$ is the local frequency operator.
-    It can be noted that when equation (\ref{eq:residual}) is positive, the high-resolution image still has a higher local frequency value at that specific point than the legacy image; thus the high-resolution image is under-smoothed and the smoothing radius should be increased at that point.
-    This follows the form of the first assumption. 
-    The second assumption is used when equation (\ref{eq:residual}) is negative. 
-    When equation (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections are made. 
-    Thus, it is justifiable to set the search direction from equation (\ref{eq:ls}) equal to the residual.
-
-    Using this method, we can continually adjust the smoothing radius until we achieve the desired result of balancing the local frequency content between the two images.
-    In practice, this method produces an acceptable solution in approximately 5 iterations and exhibits sublinear convergence. 
-    We smooth the high-resolution image with the radius this method produces to balance local frequency content between the two images.
+%    \end{enumerate}
+%    
+%    We apply these assumptions using a line-search method:
+%    \begin{equation}
+%        \label{eq:linesearch}
+%        \mathbf{R}^{(i+1)} = \mathbf{R}^{(i)}+ \alpha \mathbf{r}^{(i)},
+%    \end{equation}
+%    where $\mathbf{R}^{(i)}$ is the smoothing radius at the $i$th iteration, $\alpha$ is a scalar constant that can be thought of as the step length, and $\mathbf{r}^{(i)}$ is the residual at the $i$th iteration, which can be thought of as the search direction, and is
+%    defined as
+%    \begin{equation}
+%        \label{eq:residual}
+%        \mathbf{r} = \mathbf{F}[\mathbf{S}_{\mathbf{R}} \mathbf{d}_h] - \mathbf{F}[\mathbf{d}_l]\;,
+%    \end{equation}
+%    where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the high-resolution image, $\mathbf{d}_l$ is the legacy image, and $\mathbf{F}$ is the local frequency operator.
+%    It can be noted that when equation (\ref{eq:residual}) is positive, the high-resolution image still has a higher local frequency value at that specific point than the legacy image; thus the high-resolution image is under-smoothed and the smoothing radius should be increased at that point.
+%    This follows the form of the first assumption. 
+%    The second assumption is used when equation (\ref{eq:residual}) is negative. 
+%    When equation (\ref{eq:residual}) is zero, the correct radius has been found and no further corrections are made. 
+%    Thus, it is justifiable to set the search direction from equation (\ref{eq:ls}) equal to the residual.
+%    
+%    Using this method, we can continually adjust the smoothing radius until we achieve the desired result of balancing the local frequency content between the two images.
+%    In practice, this method produces an acceptable solution in approximately 5 iterations and exhibits sublinear convergence. 
+%    We smooth the high-resolution image with the radius this method produces to balance local frequency content between the two images.
 
     After this, we use the low-cut filtered legacy and smoothed high-resolution images to find estimated time shifts we need to apply to the high-resolution image to align the reflections with the legacy image.
-    Then, we apply this estimated time shift to the original high-resolution image and blend it with the original legacy image as specified by equations~(\ref{eq:ls}) and (\ref{eq:inv2}).
+    Then, we apply this estimated time shift to the original high-resolution image and blend it with the original legacy image as specified by equations~(\ref{eq:lsf}) and (\ref{eq:inv2}).
 
@@
 
-    \plot{nspectra2}{width=0.90\columnwidth}{The spectral content of the entire image display of the legacy (red dashed), high-resolution (blue dotted), and resultant merged (magenta solid) images for the second data set.}
-
     \inputdir{pcable2}
 
-    \multiplot{3}{legacy4,hires4,merge3}{width=0.45\columnwidth}{The legacy (a), high-resolution (b), and resultant merged (c) images of the second data set.}
+    \multiplot{3}{legacy4,hires4,merge3}{width=0.47\columnwidth}{The legacy (a), high-resolution (b), and resultant merged (c) images of the second data set.}
 

### 2018-04-22 chapter-mighes/paper.tex
almost done with thesis git st

@@
 \title{Improving migration resolution by approximating the least-squares Hessian using non-stationary amplitude and frequency matching}
+
+\usetikzlibrary{arrows,automata}
 \author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
+\relax\footnotetext{Parts of this chapter were first published in \cite{mighess}.
+This work was done under the supervision of Dr.
+Sergey Fomel, and Dr.
+Zhiguang Xue helped in the migration of the data.}
+
 \newcommand*{\tran}{^{\mkern-1.5mu\mathsf{T}}}
@@
 
-\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
+\begin{center}
+\begin{tikzpicture}[auto,node distance=4cm,thick, ->, >=stealth',shorten >=1pt]
+  \tikzstyle{every state}=[fill=black,draw=none,text=white]
+
+        \node[state]         (A)              {$\mathbf{m}_0$};
+        \node[state]         (B) [right of=A] {$\mathbf{m}_1$};
+        \node[state]         (C) [left of=A]  {$\hat{\mathbf{r}}$};
+
+        \path (A) edge [bend left] node {$\mathbf{H}$} (B)
+            edge [bend left] node {$\mathbf{H}^{-1}$} (C)
+        (B) edge [bend left] node {$\mathbf{H}^{-1}$} (A)
+        (C) edge [bend left] node {$\mathbf{H}$} (A);
+
+\end{tikzpicture}
+\end{center}
+
+    \multiplot{2}{mod,vel-migration}{width=0.85\columnwidth}{The Sigsbee model reflectivity (a), and migration velocity model (b).}
+    \multiplot{2}{image0,image1}{width=0.85\columnwidth}{The first migrated image, $\mathbf{m}_0$ (a), and the second migrated image, $\mathbf{m}_1$ (b).}
+%\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
     Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations.
@@
 
-    We find the smoothing radius iteratively using the method of \cite{locfreq}, with a modification that allows the smoothing radius to be calculated in both spatial directions. 
+    We find the smoothing radius iteratively using the method of \cite{locfreq} from chapter 3, with a modification that allows the smoothing radius to be calculated in both spatial directions. 
 Essentially, this is found by choosing an initial guess of a smoothing radius, $\mathbf{R}^{(0)}$, and updating it iteratively such that 
@@
 
-    \multiplot{2}{a0,rect10b}{width=1.0\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$.
+    For this particular application using depth migration, this operator should technically be specified to balance {\em wavenumber} instead of {\em frequency}.
+    However, it is kept as frequency to keep consistent terminology with the algorithm developed in chapter 3.
+
+    \multiplot{2}{a0,rect10b}{width=0.85\columnwidth}{The forward amplitude balancing weight, $\mathbf{A}$ (a) and the smoothing radius (b), which represents the number of samples in both dimensions that $\mathbf{m}_0$ must be smoothed over in a triangle weight to balance the local frequency content with $\mathbf{m}_1$.
 This represents the forward smoothing operation, $\mathbf{S}$.}
@@
     However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
+
+    \inputdir{triop}
+    \plot{tf}{width=0.75\columnwidth}{Transfer functions for a stationary forward triangle smoothing operator (blue) and its inverse (red).}
+
+    Figure \ref{fig:tf} shows transfer functions for a stationary forward and inverse triangle smoothing operator of a radius of 10 samples.
+    In the forward case, triangle smoothing acts as a low-pass filter.
+    However, its inverse can introduce high frequency information, which is physically unrealistic for the data we are working with.
+
     Therefore, $\mathbf{S}^{-1}$ must be calculated with care to ensure the inverted data is physically plausible. 
@@
 
-    \plot{migdec-shap}{width=1\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
-
 \section{Example}
 
-    \multiplot*{3}{mod-w3,image0-w3,migdec-w3}{width=0.66\columnwidth}{The Sigsbee model reflectivity (a), the first migrated image (b), and the corrected migrated image (c).}
     We demonstrate the effectiveness of this method on the 2D Sigsbee model. 
@@
 
+    \inputdir{sigsbee}
+    \plot{migdec-shap}{width=0.8\columnwidth}{The corrected migrated image, found by applying equation (\ref{eq:invh}) to $\mathbf{m}_0$.}
+
     We begin with the sub-surface reflectivity model (Figure \ref{fig:mod}) and migration velocity model (Figure \ref{fig:vel-migration}).
@@
     This provides us with the two images, $\mathbf{m}_0$ and $\mathbf{m}_1$, that we can use to find the operation $\mathbf{H}$ that maps $\mathbf{m}_0$ to $\mathbf{m}_1$.
+
+\multiplot{3}{image0-w3,migdec-w3,mod-w3}{width=0.47\columnwidth}{The first migrated image (a), the corrected migrated image (b), and the Sigsbee model reflectivity (c).}
 
@@
 
-    Figure \ref{fig:mod-w3,image0-w3,migdec-w3} shows a windowed section of the reflectivity model, the conventionally migrated image, and the corrected migrated image.
+    Figure \ref{fig:image0-w3,migdec-w3,mod-w3} shows a windowed section of the reflectivity model, the conventionally migrated image, and the corrected migrated image.
     The corrected migrated image exhibits clearly higher resolution and has more correct and consistent amplitude content than the conventionally migrated image.

### 2018-04-22 vita.tex
Thesis updates
almost done with thesis git st

@@
 Sarah graduated with high honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin (UT Austin) to pursue her undergraduate studies. 
-She is a candidate for two Bachelor of Science degrees from UT Austin in Geologocal Sciences and Mathematics. 
-After graduation, she plans on pursuing a PhD in Computational Science, Engineering, and Mathematics from UT Austin's Institute for Computational Engineering and Sciences.
+%She is a candidate for two Bachelor of Science degrees from UT Austin in Geological Sciences and Mathematics. 
+She is a candidate for a Bachelor of Science degree in Geophysics from the Jackson School of Geosciences and a Bachelor of Science degree in Mathematics from the College of Natural Sciences.
+After graduation, she plans on pursuing a PhD in Mathematics and Computational Science from the Massachusetts Institute of Technology.
+
+%After graduation, she plans on pursuing a PhD in Computational Science, Engineering, and Mathematics from UT Austin's Institute for Computational Engineering and Sciences.
+%After graduation, she plans on pursuing a PhD in Computational and Mathematical Engineering from Stanford University.

### 2018-04-22 chapter-locfreq/convergence/plot.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import matplotlib.font_manager as font_manager
+
+fontpath = '/home/sarah/.fonts/cmunss.ttf'
+
+prop = font_manager.FontProperties(fname=fontpath)
+mpl.rcParams['font.family'] = prop.get_name()
+
+
+# freqdif: 78386968 
+niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
+niter2 = [0, 1, 2, 3]
+norm1= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
+norm2= [32475928, 23425132, 28284798, 26716290]
+norm3= [32475928, 27446940, 23236344, 20663992, 18737512, 17107040, 15649435, 14493308, 13569843, 12907267, 12425467,12109981, 11745056]
+norm1[:] = [x / 10371235.0 for x in norm1]
+norm2[:] = [x / 10371235.0 for x in norm2]
+norm3[:] = [x / 10371235.0 for x in norm3]
+#norm2[:] = [x / 110486663.0 for x in norm2]
+#norm3[:] = [x / 110486663.0 for x in norm3]
+#norm3[:] = [x / 10069987.0 for x in norm3]
+
+plt.figure(figsize=(9.60,5.40), dpi=1000)
+l1 = plt.scatter(niter,norm3)
+l2 = plt.scatter(niter2,norm2, marker='x', color='g')
+l3 = plt.scatter(niter,norm1, marker='*', color='y')
+
+plt.legend((l1, l2, l3),('Too small c', 'Too large c','Good c'))
+plt.plot([-1, 14], [1, 1],'r--')
+plt.xlim(-0.2, 12.2)
+plt.ylim(0, 3.5)
+plt.xlabel("Iterations")
+#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
+plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
+
+
+#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
+
+#plt.title('"Correct" C')
+#plt.title('Convergence')
[…]

### 2018-04-22 chapter-locfreq/convergence/plot2.py

@@ -1,0 +1,43 @@
+#!/usr/bin/python
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import matplotlib.font_manager as font_manager
+
+fontpath = '/home/sarah/.fonts/cmunss.ttf'
+
+prop = font_manager.FontProperties(fname=fontpath)
+mpl.rcParams['font.family'] = prop.get_name()
+
+
+# freqdif: 78386968 
+niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
+#niter = [0, 1, 2, 3, 4, 5]
+norm1= [47484892, 33515692, 23253388, 16376629, 11599820, 10069987, 10116965,10258426,10321123,10282613,10289243,10398856,10446601]
+
+#norm2=[78369720,60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
+norm2=[60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
+norm3= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
+norm1[:] = [x / 10069987.0 for x in norm1]
+norm2[:] = [x / 10069987.0 for x in norm2]
+norm3[:] = [x / 10069987.0 for x in norm3]
+
+plt.figure(figsize=(9.60,5.40), dpi=1000)
+l1 = plt.scatter(niter,norm1)
+l2 = plt.scatter(niter,norm2, marker='x', color='g')
+l3 = plt.scatter(niter,norm3, marker='*', color='y')
+
+plt.legend((l1, l2, l3),('Initial = constant 10','Initial = constant 1', 'Initial = theoretical radius'))
+plt.plot([-1, 14], [1, 1],'r--')
+plt.xlim(-0.2, 12.2)
+plt.ylim(0, 6.5)
+plt.xlabel("Iterations")
+#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
+plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
+
+
+#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
+
[…]

### 2018-04-22 chapter-locfreq/merge/radius.py

@@ -51,6 +51,12 @@ def radius(high, low,               # initial high-resolution and legacy images
     Flow('low-freq',low,locfreq)
     Result('low-freq',locfreqplot('%s Local Frequency'%titlelow))
 
+    locfreq2 = '''iphase order=10 rect1=1 rect2=1 hertz=y complex=y | 
+                 put label="Frequency" unit=Hz'''
+
+    Flow('low-freq2',low,locfreq2)
+    Result('low-freq2',locfreqplot('%s Instantaneous Frequency'%titlelow))
+
     Flow('freqdif','low-freq high-freq',freqdif)
     Result('freqdif',freqdifplot(''))
 

### 2018-04-22 chapter-mighes/triop/solve.py

@@ -1,0 +1,103 @@
+#!/usr/bin/env python2
+
+from triOp import *
+from numpy import zeros, matmul, identity
+from numpy.linalg import norm, matrix_rank
+def main():
+    print('Generic systems solver')
+    print('functions include...')
+    print('    conjGrad(A, b, tol, maxItr)')
+    print('    irls(A, b, tol, maxItr, nliter)')
+    print('    lsConjGrad(A, b, tol, maxItr)')
+    print('    regLsConjGrad(A, b, alpha, tol, maxItr)')
+
+def conjGrad(A, b, tol=1e-8, maxItr=1500, x=0):
+    '''
+    conjugate gradients solver
+    does NOT check if A is SPD
+    '''
+    n = len(b)
+
+    if norm(x) == 0:
+        x = zeros(n)
+
+    r = b - A.dot(x)
+    p = r
+
+    res0 = norm(r)
+    for i in range(1,maxItr):
+        Ap = A.dot(p)
+        pAp = p.dot(Ap)
+        alpha = r.dot(p)/pAp
+
+        x += alpha*p
+        r -= alpha*Ap
+
+        if norm(r)/res0 <= tol:
+            break
+
+        beta = -Ap.dot(r)/pAp
+        p = r + beta * p
+    return x
+
+def irls(A, b, nrm=1, tol=1e-8, maxItr=1500, nliter=10):
+    # find L2 solution
+    At = A.transpose()
+    A = matmul(A,At)
+    b = At.dot(b)
+    psinv = conjGrad(A,b,tol,maxItr)
+
+    # find nrm solution
+    for i in range (1,nliter):
+        print("IRLS nliter # %i"%i)
+        r = b - A.dot(psinv)
+        R = zeros((len(b),len(b)))
+        for j in range(1,len(r)):
+            R[j,j] = abs(r[i]**(nrm-2));
+
+        A = matmul(matmul(At,R),A)
+        b = matmul(At,R).dot(b)
+        psinv = conjGrad(A,b,tol,maxItr)
+
+    return psinv
+
+def lsConjGrad(A, b, tol=1e-8, maxItr=1500):
+    At = A.transpose()
+    Als = matmul(At,A) 
+    bls = At.dot(b)
+    print ("Matrix rank: %i" %matrix_rank(Als))
+    print ("Full rank: %i" %len(bls))
+    return conjGrad(Als, bls, tol, maxItr)
+
[…]

### 2018-04-22 chapter-mighes/triop/trfu.py

@@ -1,0 +1,45 @@
+#! /usr/bin/env python2
+
+from triOp import *
+import numpy as np
+import matplotlib.pyplot as plt
+
+# create an impulse
+spike = np.zeros(100)
+spike[50] = 1
+
+# smooth spike to get impulse respnse of filter
+rect = 10
+tri = triOper(10)
+smoo = foldConv(spike,tri)
+
+# create filter
+a = 1           # filter a term
+fs = 1/0.001    # sampling frequency
+
+# forward
+w, h = freqz(smoo, a)
+
+# inverse
+w2, h2 = freqz(a, smoo)
+
+
+# plot everything
+fig, ax1 = plt.subplots()
+ax1.set_title('Transfer functions, rect=%i samples, fs=%i Hz'%(rect,fs))
+#ax1.set_title('Transfer functions')
+ax1.plot(w*fs/(2*pi),  abs(h ), 'b')
+ax1.set_ylim([0,4])
+ax1.set_xlim([0,500])
+ax1.set_xlabel('Frequency (Hz)')
+ax1.set_ylabel('Forward', color='b')
+ax1.tick_params('y', colors='b')
+ax2 = ax1.twinx()
+ax2.plot(w2*fs/(2*pi), abs(h2), 'r')
+ax2.set_ylim([0,400])
+ax2.set_ylabel('Inverse', color='r')
+ax2.tick_params('y', colors='r')
+fig.tight_layout()
+#plt.show()
+plt.savefig('Fig/tf.pdf', format='pdf', bbox_inches='tight')
+

### 2018-04-22 chapter-mighes/triop/triOp.py

@@ -1,0 +1,139 @@
+#!/usr/bin/env python2
+
+from solve import *
+
+from numpy import empty, linspace, concatenate, pi, pad
+from numpy.linalg import pinv, norm
+from scipy.signal import butter, filtfilt, freqz
+from scipy import fft, arange
+import matplotlib.pyplot as plt
+
+def main():
+    print('Triange smoothing')
+    print('functions include...')
+    print('    foldConv(signal, filt)')
+    print('    foldConvOp(triOper, sl)')
+    print('    triOper(rect)')
+    print('    lowPassFilter(data, highcut, fs, order, plot)')
+    print('    plotSpec(y,Fs,col="red")')
+
+def foldConv(signal,filt):
+    """ 1D convolution with folding """
+    
+    # length of arrays and center
+    fl = len(filt)
+    sl = len(signal)
+    center = int(len(filt)/2)
+
+    # initialize convolved signal
+    conv = [0]*sl
+
+    # filter must be smaller than signal
+    if fl > sl:
+        raise ValueError, "Filter longer than signal"
+    
+    # convolve
+    for i in range(0,sl):
+        # center
+        conv[i] += filt[center]*signal[i]
+
+        # left
+        for j in range(0,center):
+            idx = abs(i-center+j)
+            conv[i] += filt[j]*signal[idx]
+            
+        # right 
+        for j in range(center + 1, fl):
+            idx = i+j-center
+            if idx >= sl:
+                idx = (sl-1) - (idx - (sl-1))
+            conv[i] += filt[j]*signal[idx]
+
+    return conv
+
+def foldConvOp(triOper, sl, plot=False):
+    """ 1D convolution with folding """
+    
+    # length of arrays and center
+    fl = len(triOper)
+    center = int(fl/2)
+
+    # initialize convolved signal
+    conv = [0]*sl
+    mat = empty([sl,sl])
+
+    # filter must be smaller than signal
+    if fl > sl:
+        raise ValueError, "Filter longer than signal"
+    
+    # convolve
+    for i in range(0,sl):
+        # center
+        mat[i,i] += triOper[center]
+
+        # left
+        for j in range(0,center):
+            idx = abs(i-center+j)
+            mat[i,idx] += triOper[j]
+            
+        # right 
[…]

### 2018-04-22 other/plot.py

@@ -1,0 +1,44 @@
+#!/usr/bin/python
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import matplotlib.font_manager as font_manager
+
+fontpath = '/home/sarah/.fonts/cmunss.ttf'
+
+prop = font_manager.FontProperties(fname=fontpath)
+mpl.rcParams['font.family'] = prop.get_name()
+
+
+# freqdif: 78386968 
+niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
+niter2 = [0, 1, 2, 3]
+norm1= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
+norm2= [32475928, 23425132, 28284798, 26716290]
+norm3= [32475928, 27446940, 23236344, 20663992, 18737512, 17107040, 15649435, 14493308, 13569843, 12907267, 12425467,12109981, 11745056]
+norm1[:] = [x / 10371235.0 for x in norm1]
+norm2[:] = [x / 10371235.0 for x in norm2]
+norm3[:] = [x / 10371235.0 for x in norm3]
+#norm2[:] = [x / 110486663.0 for x in norm2]
+#norm3[:] = [x / 110486663.0 for x in norm3]
+#norm3[:] = [x / 10069987.0 for x in norm3]
+
+plt.figure(figsize=(9.60,5.40), dpi=1000)
+l1 = plt.scatter(niter,norm1)
+l2 = plt.scatter(niter2,norm2, marker='x', color='g')
+l3 = plt.scatter(niter,norm3, marker='*', color='y')
+
+plt.legend((l1, l2, l3),('Good c','Too large c', 'Too small c'))
+plt.plot([-1, 14], [1, 1],'r--')
+plt.xlim(-0.2, 12.2)
+plt.ylim(0, 3.5)
+plt.xlabel("Iterations")
+#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
+plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
+
+
+#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
+
+#plt.title('"Correct" C')
+#plt.title('Convergence')
[…]

### 2018-04-22 other/plot2.py

@@ -1,0 +1,43 @@
+#!/usr/bin/python
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import matplotlib.font_manager as font_manager
+
+fontpath = '/home/sarah/.fonts/cmunss.ttf'
+
+prop = font_manager.FontProperties(fname=fontpath)
+mpl.rcParams['font.family'] = prop.get_name()
+
+
+# freqdif: 78386968 
+niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
+#niter = [0, 1, 2, 3, 4, 5]
+norm1= [47484892, 33515692, 23253388, 16376629, 11599820, 10069987, 10116965,10258426,10321123,10282613,10289243,10398856,10446601]
+
+#norm2=[78369720,60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
+norm2=[60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
+norm3= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
+norm1[:] = [x / 10069987.0 for x in norm1]
+norm2[:] = [x / 10069987.0 for x in norm2]
+norm3[:] = [x / 10069987.0 for x in norm3]
+
+plt.figure(figsize=(9.60,5.40), dpi=1000)
+l1 = plt.scatter(niter,norm1)
+l2 = plt.scatter(niter,norm2, marker='x', color='g')
+l3 = plt.scatter(niter,norm3, marker='*', color='y')
+
+plt.legend((l1, l2, l3),('Initial = constant 10','Initial = constant 1', 'Initial = theoretical radius'))
+plt.plot([-1, 14], [1, 1],'r--')
+plt.xlim(-0.2, 12.2)
+plt.ylim(0, 6.5)
+plt.xlabel("Iterations")
+#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
+plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
+
+
+#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
+
[…]

### 2018-04-23 abs.tex
done... can't get thesis to compile though!

Data matching applications are present in many computational geophysics problems.
In this thesis, I introduce a new algorithm to aid in data matching that balances local frequency content between seismic data sets.
Then, I provide a few examples where applying this algorithm to seismic data helps improve results.
These applications include multi-component image registration, matching and merging high-resolution and legacy seismic images, and improving migration resolution by approximating the least-squares Hessian.
The applications are applied to several 2D and 3D, real and synthetic data sets.

### 2018-04-23 chapter-conclusion/paper.tex
done... can't get thesis to compile though!

@@
 
-This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application on matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.
+This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application of matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.
 
@@
 Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
-It is realized that the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
+An approximation to the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
 An example is applied to a 2D synthetic Sigsbee data set.
@@
 In the future, the work presented in chapter 5 should be extended to involve real data and 3D examples. 
-It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debflt,prestack,poststack}, to see how it compares in different situations.
+It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debfilt,prestack,poststack}, to see how it compares in different situations.
 
-Another component to data matching may incorporate the phase of the signal to be matched. 
+Another extension of this data matching procedure may be to incorporate
+%Another component to data matching may incorporate 
+the phase of the signal to be matched. 
 Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.
@@
 \subsection{Code}
-The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagacsar}.
+The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagascar}.
+
 The package is available at \url{http://www.ahay.org/}.

### 2018-04-23 chapter-intro/paper.tex
done... can't get thesis to compile though!

@@
 
-The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable}.
+The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
 These two images will always be plotted in grayscale.

### 2018-04-23 chapter-locfreq/paper.tex
done... can't get thesis to compile though!

@@
 
-%\section{Examples}
         This method is applicable to workflows that require matching data with different frequency content. 
@@
 
-%        \subsection{Matching legacy and high-resolution images}
         High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
@@
 
-%\subsection{Multicomponent image registration}
 \subsection{Iterative method for calculating the smoothing radius: A modification}
@@
 
-        Before initial registration, the PP image has much higher frequency content than the SS
-        image. After the SS image is temporally compressed to PP time for initial registration, the
-        two images have more similar frequency content. However, additional frequency balancing is
-        still needed before residual registration. This poses a problem as neither image has
-        distinctly higher frequencies than the other, so both images need to be smoothed in
-        different areas to balance frequency content. In order to do this, we modify the proposed
-        method to include two separate smoothing operators---one for each image.
+        Before initial registration, the PP image has much higher frequency content than the SS image. 
+        After the SS image is temporally compressed to PP time for initial registration, the two images have more similar frequency content. 
+        However, additional frequency balancing is still needed before residual registration. 
+        This poses a problem as neither image has distinctly higher frequencies than the other, so both images need to be smoothed in different areas to balance frequency content. 
+        In order to do this, we modify the proposed method to include two separate smoothing operators---one for each image.
 
-        \multiplot{2}{freqdif,freqdif-filt5}{width=0.47\columnwidth}{Difference in local frequencies
-        (residual) between the legacy and high-resolution images before (a) and after (b) the 5th
-        iteration of frequency balancing.}
+        \multiplot{2}{freqdif,freqdif-filt5}{width=0.47\columnwidth}{Difference in local frequencies (residual) between the legacy and high-resolution images before (a) and after (b) the 5th iteration of frequency balancing.}
 
@@
             \end{equation}
-        %were $S_{R_p}$ and $S_{R_s}$ are the non-stationary smoothing operators for the PP and
-        %SS images, respectively, and 
-        where $\mathbf{d}_p$ and $\mathbf{d}_s$ are the PP and SS images, respectively, and
-        $\mathbf{S}_{\mathbf{R}_p}$ and $\mathbf{S}_{\mathbf{R}_s}$ are the non-stationary smoothing
-        operators for the PP and SS images, respectively.
+        where $\mathbf{d}_p$ and $\mathbf{d}_s$ are the PP and SS images, respectively, and $\mathbf{S}_{\mathbf{R}_p}$ and $\mathbf{S}_{\mathbf{R}_s}$ are the non-stationary smoothing operators for the PP and SS images, respectively.
         We also modify the residual from equation (\ref{eq:residual}) as
@@
             \end{equation}
-        The ideal radius is still found using the same line-search from equation (\ref{eq:alg}),
-        except we allow the smoothing radius to be negative. Physically, a negative smoothing radius
-        would signify that the image should be sharpened at that particular point instead of
-        smoothed. In this case, instead of trying to sharpen the PP image at that particular point, 
-        we
-        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
-        %define $\mathbf{R}_p$ anda $\mathbf{R}_s$ at each sample as
-        %\begin{equation}
-        %        \mathbf{R}_p = \begin{cases} \mathbf{R} &\mbox{if } \mathbf{R} \ge 1 \\
-        %1 & \mbox{otherwise} \end{cases} 
-        %\end{equation}
-        %and
-        %\begin{equation}
-        %        \mathbf{R}_s = \begin{cases} |\mathbf{R}| &\mbox{if } \mathbf{R} \le -1 \\
-        %1 & \mbox{otherwise} \end{cases} 
-        %\end{equation}
-        %choose to smooth the SS image by the negative component of the smoothing radius. Thus, we
-        %define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as
-        choose to smooth the SS image by the negative part of the smoothing radius. 
+        The ideal radius is still found using the same line-search from equation (\ref{eq:alg}), except we allow the smoothing radius to be negative. 
+        Physically, a negative smoothing radius would signify that the image should be sharpened at that particular point instead of smoothed. 
+        In this case, instead of trying to sharpen the PP image at that particular point, we choose to smooth the SS image by the negative part of the smoothing radius. 
         Thus, we define the $i$th components of $\mathbf{R}_p$ and $\mathbf{R}_s$ as 
-        %Thus, we define $R_{p,i}$ and $R_{s,i}$ (the $i$th components of $\mathbf{R}_p$ and
-        %$\mathbf{R}_s$) as
         \begin{equation}
@@
         \end{equation}
-
-        where $R_i$ is the $i$th component of $\mathbf{R}$ and a radius of 1 represents no
-        smoothing. This allows each image to be smoothed in different areas to balance the frequency
-        content between the two images.
+        where $R_i$ is the $i$th component of $\mathbf{R}$ and a radius of 1 represents no smoothing. 
+        This allows each image to be smoothed in different areas to balance the frequency content between the two images.
 
@@
 
-        The results of using this spectral balancing method are shown in Figure
-        \ref{fig:before,after}. Comparable results were achieved in \cite{ltft}, who used local time-frequency decomposition (LTFD) to
-        balance the spectral content between the two images. However, the method we propose in this
-        chapter is more straightforward and significantly less computationally expensive.
+        The results of using this spectral balancing method are shown in Figure \ref{fig:before,after}. 
+        Comparable results were achieved in \cite{ltft}, who used local time-frequency decomposition (LTFD) to balance the spectral content between the two images. 
+        However, the method we propose in this chapter is more straightforward and significantly less computationally expensive.
 
@@
 
-        \multiplot{2}{before,after}{width=0.65\columnwidth}{Interleaved PP and warped SS traces before
-        (a) and after (b) frequency balancing and residual registration. After registration, the
-        signal content between the two initial images is more aligned; for example, the reflections
-        around 0.3 and 0.6 s. This indicates a successful registration.}
+        \multiplot{2}{before,after}{width=0.65\columnwidth}{Interleaved PP and warped SS traces before (a) and after (b) frequency balancing and residual registration.
+After registration, the signal content between the two initial images is more aligned; for example, the reflections around 0.3 and 0.6 s.
+This indicates a successful registration.}
 
@@
 \section{Conclusions}
-        It is difficult to compare signals with differing frequency content because signals with
-        differing frequencies are hard to correlate. In this chapter, we proposed two methods of
-        balancing frequency content between data. 
-        The first one takes a theoretical approach of what we expect the data to be, and the second one takes the form of an optimization problem
-        solved by a simple iterative algorithm. This algorithm is a relatively inexpensive and effective method
-        compared to previously proposed methods of balancing frequencies between data sets. We
-        applied these methods to examples of matching seismic images of differing resolution and for
-        multicomponent image registration.
+        It is difficult to compare signals with differing frequency content because signals with differing frequencies are hard to correlate. 
+        In this chapter, we proposed two methods of balancing frequency content between data. 
+        The first one takes a theoretical approach of what we expect the data to be, and the second one takes the form of an optimization problem solved by a simple iterative algorithm. 
+        This algorithm is a relatively inexpensive and effective method compared to previously proposed methods of balancing frequencies between data sets. 
+        We applied these methods to examples of matching seismic images of differing resolution and for multicomponent image registration.
 
 \section{Acknowledgements}
-        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their
-        financial support.
-%
-%\onecolumn
-%
-%\bibliographystyle{seg}
-%\bibliography{SEG,locfreq}
+        We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.

### 2018-04-23 other/plot.py
moved all files around

@@ -1,44 +1,0 @@
-#!/usr/bin/python
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import matplotlib.font_manager as font_manager
-
-fontpath = '/home/sarah/.fonts/cmunss.ttf'
-
-prop = font_manager.FontProperties(fname=fontpath)
-mpl.rcParams['font.family'] = prop.get_name()
-
-
-# freqdif: 78386968 
-niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
-niter2 = [0, 1, 2, 3]
-norm1= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
-norm2= [32475928, 23425132, 28284798, 26716290]
-norm3= [32475928, 27446940, 23236344, 20663992, 18737512, 17107040, 15649435, 14493308, 13569843, 12907267, 12425467,12109981, 11745056]
-norm1[:] = [x / 10371235.0 for x in norm1]
-norm2[:] = [x / 10371235.0 for x in norm2]
-norm3[:] = [x / 10371235.0 for x in norm3]
-#norm2[:] = [x / 110486663.0 for x in norm2]
-#norm3[:] = [x / 110486663.0 for x in norm3]
-#norm3[:] = [x / 10069987.0 for x in norm3]
-
-plt.figure(figsize=(9.60,5.40), dpi=1000)
-l1 = plt.scatter(niter,norm1)
-l2 = plt.scatter(niter2,norm2, marker='x', color='g')
-l3 = plt.scatter(niter,norm3, marker='*', color='y')
-
-plt.legend((l1, l2, l3),('Good c','Too large c', 'Too small c'))
-plt.plot([-1, 14], [1, 1],'r--')
-plt.xlim(-0.2, 12.2)
-plt.ylim(0, 3.5)
-plt.xlabel("Iterations")
-#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
-plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
-
-
-#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
-
-#plt.title('"Correct" C')
-#plt.title('Convergence')
[…]

### 2018-04-23 other/plot2.py

@@ -1,43 +1,0 @@
-#!/usr/bin/python
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import matplotlib.font_manager as font_manager
-
-fontpath = '/home/sarah/.fonts/cmunss.ttf'
-
-prop = font_manager.FontProperties(fname=fontpath)
-mpl.rcParams['font.family'] = prop.get_name()
-
-
-# freqdif: 78386968 
-niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
-#niter = [0, 1, 2, 3, 4, 5]
-norm1= [47484892, 33515692, 23253388, 16376629, 11599820, 10069987, 10116965,10258426,10321123,10282613,10289243,10398856,10446601]
-
-#norm2=[78369720,60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
-norm2=[60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
-norm3= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
-norm1[:] = [x / 10069987.0 for x in norm1]
-norm2[:] = [x / 10069987.0 for x in norm2]
-norm3[:] = [x / 10069987.0 for x in norm3]
-
-plt.figure(figsize=(9.60,5.40), dpi=1000)
-l1 = plt.scatter(niter,norm1)
-l2 = plt.scatter(niter,norm2, marker='x', color='g')
-l3 = plt.scatter(niter,norm3, marker='*', color='y')
-
-plt.legend((l1, l2, l3),('Initial = constant 10','Initial = constant 1', 'Initial = theoretical radius'))
-plt.plot([-1, 14], [1, 1],'r--')
-plt.xlim(-0.2, 12.2)
-plt.ylim(0, 6.5)
-plt.xlabel("Iterations")
-#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
-plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
-
-
-#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
-
[…]

### 2018-04-24 chapter-background/paper.tex
thesis updated

@@
 
-\inputdir{.}
+\inputdir{dmExample}
 \multiplot{4}{one0,one1,one2,one3}{width=1.0\columnwidth}{(a) Two traces that need to be matched---we will match the red trace to the black trace.
@@
 (d) The final result: red trace from (c) after shifting, which now better matches with the black trace.
-The amount and order in which these operations is applied affects the final result (Figure \ref{fig:before,after}).}
+The amount and order in which these operations is applied affects the final result (Figure \ref{fig:bef,aft}).}
 
@@
 Applying filtering before scaling produces a different result from applying scaling before filtering. 
-An illustration of this property is shown in Figure \ref{fig:before,after}.
+An illustration of this property is shown in Figure \ref{fig:bef,aft}.
 
-\multiplot{2}{before,after}{width=1.0\columnwidth}{(a) A lower-resolution seismic trace (black) and a higher-resolution seismic trace (red) acquired over the same area.
+\multiplot{2}{bef,aft}{width=1.0\columnwidth}{(a) A lower-resolution seismic trace (black) and a higher-resolution seismic trace (red) acquired over the same area.
 (b) Data matching operations are noncommutative---the order in which they are applied matters.

### 2018-04-24 chapter-conclusion/paper.tex
thesis updated

@@
 
-\subsection{Code}
+\appendix
+\section{Code}
+%Below is the code for the 
 The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagascar}.
-
 The package is available at \url{http://www.ahay.org/}.
@@
 However, some of the data used in this thesis are proprietary, so those results may not directly be reproducible.
+
+The scripts and programs used to produce the examples in this thesis are below.
+
+\definecolor{mygreen}{rgb}{0,0.5,0}
+\definecolor{mygray}{rgb}{0.5,0.5,0.5}
+\definecolor{mymauve}{rgb}{0.5,0,0.8}
+\definecolor{c0}{rgb}{0.71,0.54,0}
+\definecolor{c1}{rgb}{0.75,0.29,0.09}
+\definecolor{c2}{rgb}{0.80,0.20,0.18}
+\definecolor{c3}{rgb}{0.15,0.54,0.82}
+\definecolor{c4}{rgb}{0.52,0.60,0}
+\definecolor{c5}{rgb}{0,0.5,0}
+\lstset{ 
+  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}; should come as last argument
+  basicstyle=\scriptsize\ttfamily,        % the size of the fonts that are used for the code
+  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
+  breaklines=true,                 % sets automatic line breaking
+  commentstyle=\color{c5},    % comment style
+  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
+  frame=single,	                   % adds a frame around the code
+  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
+  language=Python,                 % the language of the code
+  deletecomment={[s]{'''}{'''}},
+  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
+  numbersep=5pt,                   % how far the line-numbers are from the code
+  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
+  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
+  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
+  showstringspaces=false,          % underline spaces within strings only
+  showtabs=false,                  % show tabs within strings adding particular underscores
+  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
+  stringstyle=\color{c2},     % string literal style
+  tabsize=2,	                   % sets default tabsize to 2 spaces
+  keywords=[1]{from,for,if,in,import},
+  keywords=[2]{Flow,Fetch},
+  keywords=[3]{Result,Plot},
+  keywordstyle={\color{c0}},
+  keywordstyle=[2]{\color{blue}},
+  keywordstyle=[3]{\color{c3}},
+}
+%\lstset{language=python,numbers=left,numberstyle=\tiny,showstringspaces=false}
+
+\begin{table}[h]
+\centering
+\caption{Figures and the scripts to generate them}
+\label{my-label}
+\begin{tabular}{l|l|l}
+\hline
+        \textbf{Figures} & \textbf{Directory} & \textbf{Listings} \\ \hline 
+        \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
+        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & \ref{lst:dm} \\ 
+        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
+        \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\
+        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  \ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
+        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  \ref{lst:conv}\\ 
+        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
+        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & \ref{lst:mps} \\ 
+        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ & \ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
+        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & \ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\
+        \ref{fig:tf}, & chapter-merge/triop/ & \ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
+\end{tabular}
+\end{table}
+
+\subsection{Chapter 2}
+
+\lstinputlisting[label={lst:dm},caption={chapter-background/dmExample/dmExample.py}]{../chapter-background/dmExample/dmExample.py}
+
+\subsection{Chapter 3}
+%
+%\inputdir{../chapter-locfreq/merge}
+%This chapter is split into three main projects (directories). 
+%
+%\inputdir{../chapter-merge/apache}
+%The code to generate Figures \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, and \ref{fig:freqdif,freqdif-filt}, which are used to demonstrate the theoretical smoothing radius, is contained with the code for Chapter 4.
+%
+%The second project is in the merge directory and includes the example with of the iterative algorithm to balance local frequency content between data sets.
+%This includes the code to generate Figures \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, and \ref{fig:freqdif,freqdif-filt5}.
+%
+%The third project demonstrates the 
+\lstinputlisting[label={lst:lms},caption={chapter-locfreq/merge/SConstruct}]{../chapter-locfreq/merge/SConstruct}
+\lstinputlisting[label={lst:lmrp},caption={chapter-locfreq/merge/radius.py}]{../chapter-locfreq/merge/radius.py}
+\lstinputlisting[language=C,label={lst:lmrc},caption={chapter-locfreq/merge/radius.c}]{../chapter-locfreq/merge/radius.c}
+
+\lstinputlisting[label={lst:lvs},caption={chapter-locfreq/vecta/SConstruct}]{../chapter-locfreq/vecta/SConstruct}
+\lstinputlisting[label={lst:lvn},caption={chapter-locfreq/vecta/newwarplocfreq.py}]{../chapter-locfreq/vecta/newwarplocfreq.py}
+\lstinputlisting[label={lst:lvrp},caption={chapter-locfreq/vecta/radius2.py}]{../chapter-locfreq/vecta/radius2.py}
+\lstinputlisting[label={lst:lvrc},language=C,caption={chapter-locfreq/vecta/radius2.c}]{../chapter-locfreq/vecta/radius2.c}
+
+\lstinputlisting[label={lst:conv},caption={chapter-locfreq/convergence/plot.py}]{../chapter-locfreq/convergence/plot.py}
+
+\subsection{Chapter 4}
+\lstinputlisting[label={lst:mas},caption={chapter-merge/apache/SConstruct}]{../chapter-merge/apache/SConstruct}
+\lstinputlisting[label={lst:mps},caption={chapter-merge/pcable/SConstruct}]{../chapter-merge/pcable/SConstruct}
+\lstinputlisting[label={lst:mp2s},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/SConstruct}
+\lstinputlisting[label={lst:mp2rp},caption={chapter-merge/pcable2/radius.py}]{../chapter-merge/pcable2/radius.py}
+\lstinputlisting[language=C,label={lst:mp2rc},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/radius.c}
+
+\subsection{Chapter 5}
+\lstinputlisting[label={lst:hss},caption={chapter-mighes/sigsbee/SConstruct}]{../chapter-mighes/sigsbee/SConstruct}
+\lstinputlisting[label={lst:hsrp},caption={chapter-mighes/sigsbee/radius.py}]{../chapter-mighes/sigsbee/radius.py}
+\lstinputlisting[language=C,label={lst:hsrc},caption={chapter-mighes/sigsbee/radius.c}]{../chapter-mighes/sigsbee/radius.c}
+
+\lstinputlisting[label={lst:triop},caption={chapter-mighes/triop/triOp.py}]{../chapter-mighes/triop/triOp.py}
+\lstinputlisting[label={lst:trfu},caption={chapter-mighes/triop/trfu.py}]{../chapter-mighes/triop/trfu.py}
+\lstinputlisting[label={lst:solve},caption={chapter-mighes/triop/solve.py}]{../chapter-mighes/triop/solve.py}

### 2018-04-24 vita.tex
done... can't get thesis to compile though!
thesis updated

--- 2018-03-13 vita.tex
@@
 Sarah graduated with high honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin (UT Austin) to pursue her undergraduate studies.
-She is a candidate for two Bachelor of Science degrees from UT Austin in Geologocal Sciences and Mathematics. 
-After graduation, she plans on pursuing a PhD in Computational Science, Engineering, and Mathematics from UT Austin's Institute for Computational Engineering and Sciences.
+She is a candidate for a Bachelor of Science degree in Geophysics from the Jackson School of Geosciences and a Bachelor of Science degree in Mathematics from the College of Natural Sciences.
+After graduation, she plans on pursuing a PhD in Mathematics and Computational Science at the Massachusetts Institute of Technology.

### 2018-04-24 chapter-locfreq/convergence/plot.py

@@ -8,19 +8,17 @@ fontpath = '/home/sarah/.fonts/cmunss.ttf'
 prop = font_manager.FontProperties(fname=fontpath)
 mpl.rcParams['font.family'] = prop.get_name()
 
-
-# freqdif: 78386968 
+# first plot
 niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
 niter2 = [0, 1, 2, 3]
-norm1= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
+norm1= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 
+        10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
 norm2= [32475928, 23425132, 28284798, 26716290]
-norm3= [32475928, 27446940, 23236344, 20663992, 18737512, 17107040, 15649435, 14493308, 13569843, 12907267, 12425467,12109981, 11745056]
+norm3= [32475928, 27446940, 23236344, 20663992, 18737512, 17107040, 15649435, 
+        14493308, 13569843, 12907267, 12425467,12109981, 11745056]
 norm1[:] = [x / 10371235.0 for x in norm1]
 norm2[:] = [x / 10371235.0 for x in norm2]
 norm3[:] = [x / 10371235.0 for x in norm3]
-#norm2[:] = [x / 110486663.0 for x in norm2]
-#norm3[:] = [x / 110486663.0 for x in norm3]
-#norm3[:] = [x / 10069987.0 for x in norm3]
 
 plt.figure(figsize=(9.60,5.40), dpi=1000)
 l1 = plt.scatter(niter,norm3)
@@ -32,13 +30,35 @@ plt.plot([-1, 14], [1, 1],'r--')
 plt.xlim(-0.2, 12.2)
 plt.ylim(0, 3.5)
 plt.xlabel("Iterations")
-#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
 plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
 
-
-#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
-
-#plt.title('"Correct" C')
-#plt.title('Convergence')
[…]

### 2018-04-24 chapter-locfreq/convergence/plot2.py

@@ -11,10 +11,8 @@ mpl.rcParams['font.family'] = prop.get_name()
 
 # freqdif: 78386968 
 niter = [0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12]
-#niter = [0, 1, 2, 3, 4, 5]
 norm1= [47484892, 33515692, 23253388, 16376629, 11599820, 10069987, 10116965,10258426,10321123,10282613,10289243,10398856,10446601]
 
-#norm2=[78369720,60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
 norm2=[60672360,33617148,20220940,13173313,10842506,10398470,10210745,10296503,10313730,10298821,10204044,10263224,10321556]
 norm3= [32475928, 25392492, 19320528, 14462173, 11263933, 10371235, 10477612, 10634981, 10760000, 10680567, 10628854, 10559621, 10391489]
 norm1[:] = [x / 10069987.0 for x in norm1]
@@ -31,13 +29,6 @@ plt.plot([-1, 14], [1, 1],'r--')
 plt.xlim(-0.2, 12.2)
 plt.ylim(0, 6.5)
 plt.xlabel("Iterations")
-#plt.ylabel(r'$\Vert\mathbf{F}($smoothed$) -  \mathbf{F}($legacy$) \Vert$')
 plt.ylabel(r'$\Vert\mathbf{F}(S_R * d_h) -  \mathbf{F}(d_l) \Vert$')
 
-
-#\Vert \textbf{F}(\text{smoothed}) - \textbf{F}(\text{legacy}) \Vert
-
-#plt.title('"Correct" C')
-#plt.title('Convergence')
-#plt.savefig('l1l2.pdf', format='pdf', bbox_inches='tight')
 plt.savefig('Fig/all.pdf', format='pdf', bbox_inches='tight')

### 2018-04-24 chapter-locfreq/merge/radius.c

@@ -1,5 +1,4 @@
 /* smoothing radius (min = 1) */
-
 #include <rsf.h>
 #include <math.h>
 
@@ -53,5 +52,3 @@ int main (int argc, char* argv[])
     sf_floatwrite(rad,n12,out);
     exit(0);
 }
-
-

### 2018-04-24 chapter-locfreq/merge/radius.py

@@ -2,7 +2,8 @@ from rsf.proj import *
 
 def radius(high, low,               # initial high-resolution and legacy images
            niter,                   # number of corrections
-           c,                       # 'step length' for radius corrections. Can be type int or float for constant c 
+           c,                       # 'step length' for radius corrections. Can 
+                                    # be type int or float for constant c 
                                     # or type array for changing c.
            bias=-15, clip=30,       # bias and clip for display
            rect1=40, rect2=80,      # radius for local frequency calculation
@@ -30,15 +31,18 @@ def radius(high, low,               # initial high-resolution and legacy images
     freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
 
     def freqdifplot(num):
-        return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %s" 
-                  clip=%d bias=%d minval=%d maxval=%d''' %(num,clip,bias,minval,maxval) 
+        return '''grey allpos=y color=j scalebar=y mean=y 
+                  title="Difference in Local Frequencies %s" 
+                  clip=%d bias=%d minval=%d 
+                  maxval=%d''' %(num,clip,bias,minval,maxval) 
 
     specplot = '''cat axis=2 ${SOURCES[1]} | 
                   scale axis=1 | window max1=180 |
                   graph title="Normalized Spectra" label2="Amplitude" unit2=""'''
 
     def rectplot(name):
-        return 'grey color=j mean=y title="%s" scalebar=y barlabel=Radius barunit=samples'%name
+        return '''grey color=j mean=y title="%s" scalebar=y barlabel=Radius 
+                  barunit=samples'''%name
 
     smooth = 'nsmooth1 rect=${SOURCES[1]}'
 
@@ -64,7 +68,7 @@ def radius(high, low,               # initial high-resolution and legacy images
     if (theor):
         from math import pi
         Flow('rect0','low-freq high-freq','''math f1=${SOURCES[1]} 
-              output="sqrt(%g*(1/(input*input)-1/(f1*f1)))/%g" '''%(scale,2*pi*0.001))
[…]

### 2018-04-24 chapter-locfreq/vecta/newwarp_locfreq.py

@@ -1,643 +1,0 @@
-from rsf.proj import *
-import math, string, sys
-import rsf.recipes.version as version
-from radius2 import radius2
-
-###########################################################
-#  Modified from $RSFSRC/book/tccs/ltft/vecta/newwarp.py  #
-###########################################################
-
-warp0 = '''
-warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
-verb=1 nliter=0
-'''
-
-getmask = 'add scale=1,-1 ${SOURCES[1]} | mask min=0 | dd type=float'
-
-def psrect(rect):
-    return '''
-    math min=${SOURCES[2]} max=${SOURCES[1]}
-    output="sqrt(1+%d*(1/min^2-1/max^2)*input)" | dd type=int
-    ''' % rect
-
-def pprect(rect):
-    return '''
-    math min=${SOURCES[2]} max=${SOURCES[1]}
-    output="sqrt(1+%d*(1/max^2-1/min^2)*(1-input))" | dd type=int
-    ''' % rect
-
-balance = '''
-nsmooth1 rect=${SOURCES[1]} |
-abalance rect1=100 order=100 other=${SOURCES[2]}
-'''
-
-def simil(rect1=1,rect2=1):
-    return '''
-    similarity other=${SOURCES[1]} rect1=%d rect2=%d
-    ''' % (rect1,rect2)
-
-def warping(niter,rect1=1,rect2=1,rect3=1):
-    return '''
-    warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
-    warpout=www.rsf
-    verb=1 nliter=%d noamp=1 rect1=%d rect2=%d rect3=%d > ${TARGETS[1]} &&
-    warpadd < ${SOURCES[3]} add=www.rsf > $TARGET &&
-    rm www.rsf
-    ''' % (niter,rect1,rect2,rect3)
-
-def pick(min2,max2,rect1=1,rect2=1,rect3=1,an=0.5):
-    return '''
-    window min2=%g max2=%g | 
-    pick rect1=%d rect2=%d rect3=%d an=%g |
-    window''' % (min2,max2,rect1,rect2,rect3,an)
-
-def warpscan(ng,g0,gmax,rect1=1,rect2=1,rect3=1,rect4=1):
-    dg = (gmax-g0)/(ng-1)
-    return '''
-    warpscan other=${SOURCES[1]} niter=100
[…]

### 2018-04-24 chapter-locfreq/vecta/newwarplocfreq.py

@@ -1,0 +1,466 @@
+from rsf.proj import *
+import math, string, sys
+import rsf.recipes.version as version
+from radius2 import radius2
+
+###########################################################
+#  Modified from $RSFSRC/book/tccs/ltft/vecta/newwarp.py  #
+###########################################################
+
+warp0 = '''
+warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
+verb=1 nliter=0
+'''
+
+getmask = 'add scale=1,-1 ${SOURCES[1]} | mask min=0 | dd type=float'
+
+def psrect(rect):
+    return '''
+    math min=${SOURCES[2]} max=${SOURCES[1]}
+    output="sqrt(1+%d*(1/min^2-1/max^2)*input)" | dd type=int
+    ''' % rect
+
+def pprect(rect):
+    return '''
+    math min=${SOURCES[2]} max=${SOURCES[1]}
+    output="sqrt(1+%d*(1/max^2-1/min^2)*(1-input))" | dd type=int
+    ''' % rect
+
+balance = '''
+nsmooth1 rect=${SOURCES[1]} |
+abalance rect1=100 order=100 other=${SOURCES[2]}
+'''
+
+def simil(rect1=1,rect2=1):
+    return '''
+    similarity other=${SOURCES[1]} rect1=%d rect2=%d
+    ''' % (rect1,rect2)
+
+def warping(niter,rect1=1,rect2=1,rect3=1):
+    return '''
+    warp1 other=${SOURCES[1]} warpin=${SOURCES[2]}
+    warpout=www.rsf
+    verb=1 nliter=%d noamp=1 rect1=%d rect2=%d rect3=%d > ${TARGETS[1]} &&
+    warpadd < ${SOURCES[3]} add=www.rsf > $TARGET &&
+    rm www.rsf
+    ''' % (niter,rect1,rect2,rect3)
+
+def pick(min2,max2,rect1=1,rect2=1,rect3=1,an=0.5):
+    return '''
+    window min2=%g max2=%g | 
+    pick rect1=%d rect2=%d rect3=%d an=%g |
+    window''' % (min2,max2,rect1,rect2,rect3,an)
+
+def warpscan(ng,g0,gmax,rect1=1,rect2=1,rect3=1,rect4=1):
+    dg = (gmax-g0)/(ng-1)
+    return '''
+    warpscan other=${SOURCES[1]} niter=100
[…]

### 2018-04-24 chapter-locfreq/vecta/radius2.py

@@ -2,8 +2,9 @@ from rsf.proj import *
 
 def radius2(high, low,               # initial high-resolution and legacy images
             niter,                   # number of corrections
-            c,                       # step length for radius corrections. Can be type int or float for constant c 
-                                     #      or type array for changing c.
+            c,                       # step length for radius corrections. Can 
+                                     # be type int or float for constant c 
+                                     # or type array for changing c.
             bias=-15, clip=30,       # bias and clip for display
             rect1=40, rect2=80,      # radius for local frequency calculation
             maxrad=1000,             # maximum allowed radius
@@ -30,10 +31,8 @@ def radius2(high, low,               # initial high-resolution and legacy images
     freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
 
     def freqdifplot(num):
-        #return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %d" ''' %num
-        #return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %d" 
-        #          clip=%d bias=%d minval=%d maxval=%d''' %(num,clip,bias,minval,maxval) 
-        return '''grey allpos=y color=j scalebar=y mean=y title="Difference in Local Frequencies %d" 
+        return '''grey allpos=y color=j scalebar=y mean=y 
+                  title="Difference in Local Frequencies %d" 
                   clip=%d bias=%d minval=%d maxval=%d''' %(num,22,-15,-15,8) 
 
     specplot = '''cat axis=2 ${SOURCES[1]} | 
@@ -41,12 +40,10 @@ def radius2(high, low,               # initial high-resolution and legacy images
                   graph title="Normalized Spectra" label2="Amplitude" unit2=""'''
 
     def rectplot(name):
[…]

### 2018-04-30 ack.tex
thesis and presentation

@@
 I am also grateful to many students and research scientists I've had the pleasure of interacting with: 
-Sean Bader, Luke Decker, Preston Fussee-Durham, Zhicheng Geng, Eric Goldfarb, Ben Gremillion, Tom Hess, Ken Ikeda, Harpreet Kaur, Dr.
-Dmitrii Merzlikin, Nam Pham, Mason Phillips, Kelly Regimbal, Karl Schleicher, Yunzhi Shi, Dr.
+Sean Bader, Luke Decker, Preston Fussee-Durham, Zhicheng Geng, Eric Goldfarb, Ben Gremillion, Tom Hess, Ken Ikeda, Harpreet Kaur, Dmitrii Merzlikin, Nam Pham, Mason Phillips, Kelly Regimbal, Karl Schleicher, Yunzhi Shi, Dr.
 Junzhe Sun, Dr.
@@
 Yunan Yang.
+
+I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two years.
+%Thank you for all your guidance, and for being there for the best memories during my undergraduate career.
+%Thank you for your intellectually stimulating conversations, life advice, and making me feel as though I am ``part of the group'', despite the fact that I was not a graduate student.
+Thank you all for your intellectually stimulating conversations, life advice, and for including me as ``part of the group'', despite the fact that I was only an undergraduate student.
+%You are an incredibly enjoyable and intellectually stimulating group, and I am glad I have had the opportunity to cross paths with all of you in life.
+I will forever cherish the friendships and memories I have made with all of you during my time as a part of TCCS.
+%Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
+You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
 

### 2018-04-30 chapter-background/paper.tex
thesis and presentation

@@
 In data matching applications, in particular, it is crucial to acknowledge the non-stationary variations present in seismic data.
-Therefore, any transformations we may apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.
+Therefore, any transformations we might apply in a data matching problem must be variant in all data dimensions to account for these non-stationary variations.
 
@@
 The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
-For the procedures described in this thesis, local attributes are better-suited attributes than instantaneous attributes.
+For the procedures described in this thesis, local attributes are more appropriate than instantaneous attributes.
 Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
 Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
-Because the corresponding reflections between images may not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
+Because the corresponding reflections between images might not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
 Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.
@@
 This is done using three primary data matching operations---filtering, scaling, and shifting---to effectively balance these attributes across seismic data sets.
-These operations are applied to different data sets to correctly match them for analysis or further processing.
+These operations are applied to different data sets to match them correctly for analysis or further processing.
 
@@
 This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
-In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace, since the high frequency content is not physically present in the black trace.
+In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace because the high frequency content is not physically present in the black trace.
 
 There are several ways to do this.
-An naive first approach would be to apply a bandpass filter to the red trace such that the passband covers only frequencies that are present in the black trace.
+A na\"ive first approach would be to apply a bandpass filter to the red trace such that the passband covers only frequencies that are present in the black trace.
 However, this stationary operation does not take into account the non-stationary frequency variations that may be naturally present in the data.
@@
 Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
-Scaling is also a linear operation, and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.
+Scaling is also a linear operation and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.
 
 In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
-Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces, and represent the diagonal elements of the scaling operator.
+Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces and represents the diagonal elements of the scaling operator.
 %The result of
@@
 In this thesis, I calculate the shifting operator by finding the time shifts that maximize local similarity between the two data sets.
-Local similarity extends the concept of local seismic attributes to global correlation coefficients, and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
+Local similarity extends the concept of local seismic attributes to global correlation coefficients and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
 Unlike filtering and scaling, shifting is a non-linear transformation.
@@
 In these cases, {\em time} shift is a misnomer. 
-However, since the data we are typically dealing with are time series, the shifting operation that we find and apply is considered a function of time.
+However, because the data we are typically dealing with are time series, the shifting operation that we find and apply is considered a function of time.
 
@@
 A summary of the three data matching operations is shown in Table \ref{op}.
-Both scaling and filtering are linear operations, while shifting is generally a non-linear operation.
+Both scaling and filtering are linear operations, whereas shifting is generally a non-linear operation.
 Additionally, as scaling is to weighting in the time domain, filtering is to weighting in the Fourier domain.

### 2018-04-30 chapter-conclusion/paper.tex
thesis and presentation

@@
 In this thesis, I discussed several methods and applications of data matching in seismic data analysis.
-
 Chapter 2 focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
-
 Chapter 3 introduces different methods of frequency balancing using non-stationary smoothing. 
@@
 Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
-An approximation to the least-squares Hessian can calculated by solving a data matching problem between two conventionally migrated images, and can be represented by the combination of amplitude and frequency balancing operations.
+An approximation to the least-squares Hessian can be calculated by solving a data matching problem between two conventionally migrated images, and the Hessian can be represented by the combination of amplitude and frequency balancing operations.
 An example is applied to a 2D synthetic Sigsbee data set.
@@
 the phase of the signal to be matched. 
-Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems may benefit from these corrections.
+Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems could benefit from these corrections.
 
 Several applications of data matching were discussed in this thesis. 
-However, there are still many applications that may remain unaddressed from a data matching standpoint. 
-Problems such as seismic and well-log tying, deconvolution, automatic gain control (AGC), and surface-related multiple elimination (SRME) can also be recast as data matching problems, and looking at these problems in a new light may bring advancements to computational geophysics.
+However, many applications remain unaddressed from a data matching standpoint. 
+Problems such as seismic and well-log tying, deconvolution, automatic gain control (AGC), and surface-related multiple elimination (SRME) can also be recast as data matching problems.
+Looking at these problems in a new light may bring advancements to computational geophysics.
 
@@
 \end{table}
+For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.
 
-\subsection{Chapter 2}
-
-\lstinputlisting[label={lst:dm},caption={chapter-background/dmExample/dmExample.py}]{../chapter-background/dmExample/dmExample.py}
-
-\subsection{Chapter 3}
+%\subsection{Chapter 2}
+%
+%\lstinputlisting[label={lst:dm},caption={chapter-background/dmExample/dmExample.py}]{../chapter-background/dmExample/dmExample.py}
+%
+%\subsection{Chapter 3}
 %
@@
 
-\lstinputlisting[label={lst:lvs},caption={chapter-locfreq/vecta/SConstruct}]{../chapter-locfreq/vecta/SConstruct}
-\lstinputlisting[label={lst:lvn},caption={chapter-locfreq/vecta/newwarplocfreq.py}]{../chapter-locfreq/vecta/newwarplocfreq.py}
-\lstinputlisting[label={lst:lvrp},caption={chapter-locfreq/vecta/radius2.py}]{../chapter-locfreq/vecta/radius2.py}
-\lstinputlisting[label={lst:lvrc},language=C,caption={chapter-locfreq/vecta/radius2.c}]{../chapter-locfreq/vecta/radius2.c}
-
-\lstinputlisting[label={lst:conv},caption={chapter-locfreq/convergence/plot.py}]{../chapter-locfreq/convergence/plot.py}
-
-\subsection{Chapter 4}
-\lstinputlisting[label={lst:mas},caption={chapter-merge/apache/SConstruct}]{../chapter-merge/apache/SConstruct}
-\lstinputlisting[label={lst:mps},caption={chapter-merge/pcable/SConstruct}]{../chapter-merge/pcable/SConstruct}
-\lstinputlisting[label={lst:mp2s},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/SConstruct}
-\lstinputlisting[label={lst:mp2rp},caption={chapter-merge/pcable2/radius.py}]{../chapter-merge/pcable2/radius.py}
-\lstinputlisting[language=C,label={lst:mp2rc},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/radius.c}
-
-\subsection{Chapter 5}
-\lstinputlisting[label={lst:hss},caption={chapter-mighes/sigsbee/SConstruct}]{../chapter-mighes/sigsbee/SConstruct}
-\lstinputlisting[label={lst:hsrp},caption={chapter-mighes/sigsbee/radius.py}]{../chapter-mighes/sigsbee/radius.py}
-\lstinputlisting[language=C,label={lst:hsrc},caption={chapter-mighes/sigsbee/radius.c}]{../chapter-mighes/sigsbee/radius.c}
-
-\lstinputlisting[label={lst:triop},caption={chapter-mighes/triop/triOp.py}]{../chapter-mighes/triop/triOp.py}
-\lstinputlisting[label={lst:trfu},caption={chapter-mighes/triop/trfu.py}]{../chapter-mighes/triop/trfu.py}
-\lstinputlisting[label={lst:solve},caption={chapter-mighes/triop/solve.py}]{../chapter-mighes/triop/solve.py}
+%
+%
+%\lstinputlisting[label={lst:lvs},caption={chapter-locfreq/vecta/SConstruct}]{../chapter-locfreq/vecta/SConstruct}
+%\lstinputlisting[label={lst:lvn},caption={chapter-locfreq/vecta/newwarplocfreq.py}]{../chapter-locfreq/vecta/newwarplocfreq.py}
+%\lstinputlisting[label={lst:lvrp},caption={chapter-locfreq/vecta/radius2.py}]{../chapter-locfreq/vecta/radius2.py}
+%\lstinputlisting[label={lst:lvrc},language=C,caption={chapter-locfreq/vecta/radius2.c}]{../chapter-locfreq/vecta/radius2.c}
+%
+%\lstinputlisting[label={lst:conv},caption={chapter-locfreq/convergence/plot.py}]{../chapter-locfreq/convergence/plot.py}
+%
+%
+%\subsection{Chapter 4}
+%\lstinputlisting[label={lst:mas},caption={chapter-merge/apache/SConstruct}]{../chapter-merge/apache/SConstruct}
+%\lstinputlisting[label={lst:mps},caption={chapter-merge/pcable/SConstruct}]{../chapter-merge/pcable/SConstruct}
+%\lstinputlisting[label={lst:mp2s},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/SConstruct}
+%\lstinputlisting[label={lst:mp2rp},caption={chapter-merge/pcable2/radius.py}]{../chapter-merge/pcable2/radius.py}
+%\lstinputlisting[language=C,label={lst:mp2rc},caption={chapter-merge/pcable2/SConstruct}]{../chapter-merge/pcable2/radius.c}
+%
+%
+%\subsection{Chapter 5}
+%\lstinputlisting[label={lst:hss},caption={chapter-mighes/sigsbee/SConstruct}]{../chapter-mighes/sigsbee/SConstruct}
+%\lstinputlisting[label={lst:hsrp},caption={chapter-mighes/sigsbee/radius.py}]{../chapter-mighes/sigsbee/radius.py}
+%\lstinputlisting[language=C,label={lst:hsrc},caption={chapter-mighes/sigsbee/radius.c}]{../chapter-mighes/sigsbee/radius.c}
+%
+%\lstinputlisting[label={lst:triop},caption={chapter-mighes/triop/triOp.py}]{../chapter-mighes/triop/triOp.py}
+%\lstinputlisting[label={lst:trfu},caption={chapter-mighes/triop/trfu.py}]{../chapter-mighes/triop/trfu.py}
+%\lstinputlisting[label={lst:solve},caption={chapter-mighes/triop/solve.py}]{../chapter-mighes/triop/solve.py}

### 2018-04-30 chapter-intro/paper.tex
thesis and presentation

@@
 This is useful in applications such as multi-component seismic image registration, where two separate seismic images, one P-wave image and one S- wave image, are acquired over the same area. 
-These must be properly matched, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
+These must be matched properly, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted. 
 %Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.
 
-Many other geophysics applications can be addressed from a data matching standpoint, and fall under a few main categories.
+Many other geophysics applications can be addressed from a data matching standpoint and fall under a few main categories.
 Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
-Other problems consist of matching differently acquired data, such time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
+Other problems consist of matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
 Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
@@
 This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
-Much of the theory behind Chapter 3 was developed in application to this example, but was later extended to other examples.
-As a result, I will be using data from this application throughout much of this thesis.
+Much of the theory behind Chapter 3 was developed in application to this example but was later extended to other examples.
+As a result, I use data from this application throughout much of this thesis.
 
-This thesis contains two primary data sets that I will be referring to. 
+This thesis contains two primary data sets to which I refer. 
 The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
@@
 These two images will always be plotted in grayscale.
-In parts of this thesis, I will show a 2D line from this 3D data set for simplicity of plotting.
+In parts of this thesis, I show a 2D line from this 3D data set for simplicity of plotting.
 
@@
 In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
-In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in application of improving migration resolution using non-stationary matching.
+In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.
 

### 2018-04-30 chapter-locfreq/paper.tex
thesis and presentation

@@
         Both methods involve finding and applying a non-stationary smoothing operator to minimize the local frequency difference between data sets. 
-        Numerical examples demonstrate that the proposed method improves multicomponent image registration and matching images of differing resolution. 
+        Numerical examples demonstrate that the proposed method improves multicomponent image registration and matching images of differing resolutions. 
 \end{abstract}
@@
         However, when the two signals that need to be aligned have different spectral content, their comparison can be difficult. 
-        Most seismic data experience non-stationary, or spatially and temporally variant, frequency content caused by attenuation. 
+        Seismic data contain non-stationary, or spatially and temporally variant, frequency content caused by attenuation. 
         This problem was discussed in application to multicomponent image registration by \cite{fomel2003}, who applied frequency balancing methods to improve registration results. 
@@
         In this chapter, we propose methods for removing non-stationary frequency differences that limit the effectiveness of matching data. 
-        We suggest applying the either of the proposed methods to processing flows that involve matching data before attempting to find the time shift to align their signal content. 
+        We suggest applying either of the proposed methods to processing flows that involve matching data before attempting to find the time shift to align their signal content. 
         To balance frequency content, we use a non-stationary smoothing operator with an adjustable smoothing radius to apply to the higher frequency data set. 
-        Our first approach finds the smoothing operator directly, but is based on the primary assumption that the data can be modeled by a summation of Ricker wavelets. 
+        Our first approach finds the smoothing operator directly, but it is based on the primary assumption that the data can be modeled by a summation of Ricker wavelets. 
         Our second approach of finding the smoothing radius is based on understanding what the smoothing operator physically does, and takes the form of an optimization problem which is solved using an iterative method.
@@
         In order to balance local frequency content, we propose smoothing the higher frequency data using a non-stationary triangle smoothing operator with an adjustable radius. 
-        Here, the radius at each point is the number of samples in time that that specific data point gets averaged over in a triangle weight.
+        Here, the radius at each point is the number of samples in time that that specific data point is averaged over in a triangle weight.
 
-        In order to find the temporally and spatially variable smoothing radius that we need to apply to the higher frequency image to balance local frequency content with the lower frequency image, we take two approaches.
+        %In order to find the temporally and spatially variable smoothing radius that we need to apply to the higher frequency image to balance local frequency content with the lower frequency image, we take two approaches.
+        We find the temporally and spatially variable smoothing radius to apply to the higher frequency image to balance local frequency content with the lower frequency image by taking two approaches.
         The first approach is finding the smoothing radius based on assumptions of what the data we are looking at can be represented by, and the second approach is based on understanding physically what non-stationary smoothing does to a data set.
         Both approaches work well in different situations---the first approach is less computationally expensive than the second approach, but is only applicable when the two data sets fit the assumptions that are used to calculate what the smoothing radius is.
-        The second approach finds the smoothing radius in an iterative manner, but manages to work well for any data set given to it.
+        The second approach finds the smoothing radius in an iterative manner, but it manages to work well for any data set given to it.
 
@@
         This method is based off of the primary assumption that the signal can be represented by Ricker wavelets convolved with the Earth's reflectivity series.
-        Since the data we are working with are seismic, this can be a good assumption \cite[]{ricker}.
+        Because the data we are working with are seismic amplitudes, this can be a good assumption \cite[]{ricker}.
 
@@
         We measure local frequencies in both images and apply smoothing specified by equation~(\ref{eq:radius}) to the high-resolution image.
-        Since this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
+        Because this is only an approximation of what the smoothing radius should be under ideal conditions, we adjust the constant $12$ in the equation to achieve a better match. 
         In this example, this effectively reduces the difference between the spectral content of the images, as shown in Figure \ref{fig:hires-smooth-spec}. 
@@
         \inputdir{merge}
-        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it doesn't work in situations where there is not much overlap in frequency content between data sets, like in the second example of the next chapter.
+        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it does not work in situations where litte overlap is present in frequency content between data sets, like in the second example of the next chapter.
         In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.
@@
         where $\mathbf{S}_\mathbf{R}$ is the non-stationary smoothing operator of smoothing radius $\mathbf{R}$, $\mathbf{d}_h$ is the higher frequency data, $\mathbf{d}_l$ is the lower frequency data, $\mathbf{F}$ is the local frequency operator, and $N$ is the maximum size of the smoothing radius.
-        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends non-linearly on $R$.
+        Although smoothing is a linear operation, the smoothed data, $\mathbf{S_R d}_h$, depends non-linearly on $\mathbf{R}$.
 However, the objective from equation (\ref{eq:obj}) is nearly convex, and we choose to use an intuitive iterative approach to find an approximate smoothing radius.
@@
         This method is applicable to workflows that require matching data with different frequency content. 
-        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images produces better results.
+        Here, we demonstrate that using this algorithm to match high-resolution and legacy seismic images improves the results.%produces better results.
 
         High-resolution seismic data, such as those acquired with the P-cable acquisition system, can produce very detailed images of the near subsurface \cite[]{tip}. 
-        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a larger frequency bandwidth. 
+        When compared to conventional seismic images, high-resolution images have a higher dominant frequency and a wider frequency bandwidth. 
         However, they usually lack low frequency content and depth coverage that is present in conventional seismic images. 
@@
         %However, this need not always be the case.
-        However, in some cases, the two data sets may have similar local frequency content, but they may still need to be matched.
+        However, in some cases, the two data sets may have similar local frequency content, but they might still need to be matched.
         We illustrate a modified version of the previous algorithm by demonstrating it on an example of multi-component seismic image registration.
@@
 \inputdir{convergence}
-        Since this algorithm was developed from observations and intuition based on what smoothing is physically doing, no error analysis or convergence criteria has been developed in this thesis.
+        Because this algorithm was developed from observations and intuition based on what smoothing is physically doing, no error analysis or convergence criteria has been developed in this thesis.
         However, it is observed that this algorithm generally exhibits sublinear convergence.
@@
         If the step length is too small, the algorithm takes many more iterations to converge.
-        With the ``correct'' step length, however, the algorithm usually converges in under 10 iterations in practice.
+        With the ``correct'' step length, however, the algorithm usually converges in fewer than 10 iterations in practice.
 
@@
 \section{Conclusions}
-        It is difficult to compare signals with differing frequency content because signals with differing frequencies are hard to correlate. 
+        Comparing signals with differing frequency content is difficult because signals with differing frequencies are hard to correlate. 
         In this chapter, we proposed two methods of balancing frequency content between data. 

### 2018-04-30 chapter-merge/paper.tex
done... can't get thesis to compile though!
thesis and presentation

@@
     As a result, both the initial and resultant merged images poses similar signal characteristics, most notably spectral content \cite[]{kavery,gabor,supermerge}. 
-    However, previously \cite{freqmerge} are successful in applying a frequency domain merge to two separate seismic volumes over the same area to broaden the effective bandwidth.
+    However, previously \cite{freqmerge} were successful in applying a frequency domain merge to two separate seismic volumes over the same area to broaden the effective bandwidth.
 
@@
     The initial legacy and high-resolution example images are shown in Figure~\ref{fig:legacy,hires,merge2-reverse}. 
-    They both underwent standard marine processing flows, and are assumed to be optimally processed.
+    They both underwent standard marine processing flows and are assumed to be optimally processed.
     The images show similar structures, particularly at shallow depths, but with strikingly different resolution. 
@@
 
-%    After smoothing, the frequency difference is minimized.
+    %After smoothing, the frequency difference is minimized.
 
@@
 
-    In addition to frequency balancing, we initially attempted accounting for wavelet phase differences between data sets at this step. 
+    In addition to frequency balancing, we initially attempted to account for wavelet phase differences between data sets at this step. 
     However, we saw this had a negligible impact on the final result, so we decided not to include it in this method.
 
-%%    \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
+    % \multiplot{2}{freqdif,freqdif-filt}{width=0.65\columnwidth}{Difference in local frequencies between the legacy and high-resolution images before (a) and after (b) balancing their frequency content by non-stationary smoothing.}
 
@@
 
-    Since the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together to combine the strengths of each while minimizing their weaknesses.
+    Because the high-resolution and legacy images contain information about the same subsurface, we can attempt to create an optimal image of this area by blending the two images together to combine the strengths of each while minimizing their weaknesses.
     We can achieve this by imposing two conditions. 
@@
     The weights, $\mathbf{W_h}$ and $\mathbf{W_l}$, are applied to the images to bring out the desired qualities from each image. 
-    For example, since we prefer the high-resolution image in the shallow section, we weight it stronger there and gradually taper the weight to preference the legacy image with depth. 
+    For example, because we prefer the high-resolution image in the shallow section, we weight it more significantly there and gradually taper the weight to preference the legacy image with depth. 
     In addition, we estimate the legacy weight, $\mathbf{W_l}$, to balance the legacy image's amplitudes with respect to the high-resolution image. 
@@
     There is a definite separation in frequency content when comparing the legacy and high-resolution images (Figure \ref{fig:nspectra2}). 
-    Because there is not much overlap in frequency bandwidth, balancing their spectral content is challenging. 
+    Because of little overlap in frequency bandwidth, balancing their spectral content is challenging. 
     In addition, a primary assumption made in deriving the theoretical smoothing radius (equation \ref{eq:rad}) is that the signal is modeled by a summation of Ricker wavelets, which may not be a correct assumption.
@@
     We also thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
-
-%\onecolumn
-%
-%\bibliographystyle{seg}
-%\bibliography{SEG,merge}

### 2018-04-30 chapter-mighes/paper.tex
done... can't get thesis to compile though!
thesis and presentation

@@
 Sergey Fomel, and Dr.
-Zhiguang Xue helped in the migration of the data.}
+Zhiguang Xue assisted in the migration of the Sigsbee synthetic data set.}
 
@@
     Although conventional seismic migration is less computationally expensive than least-squares migration, it generally contains migration artifacts affecting amplitude fidelity and resolution \cite[]{lsamp,pwlsrtm}.
-    This may be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by finding the least-squares model solution, standard migration amounts to applying a single adjoint operation \cite[]{pvi}.
+    This can be attributed to the fact that, while least-squares migration inverts for subsurface reflectivity by finding the least-squares model solution, standard migration amounts to applying a single adjoint operation \cite[]{pvi}.
 
@@
 This allows for the smooth estimation and application of these matching operations instead of applying them in discrete windows.
-    Since the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each operation can be adjusted independently, which is another advantage of the proposed method.
+    Because the operations for balancing amplitude and frequency content are calculated and applied separately from each another, the effect of each operation can be adjusted independently, which is another advantage of the proposed method.
     To test the proposed approach, we apply this method to an example of reverse-time migration on the Sigsbee synthetic data set \cite[]{sigsbee}.
@@
     \end{equation}
-    Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to get $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
+    Therefore, the inverse Hessian operator, $\mathbf{H}^{-1} = \left ( \mathbf{L} \tran \mathbf{L} \right )^{-1}$, that must be applied to $\mathbf{m}_0$ to obtain $\hat{\mathbf{r}}$ can be calculated by first finding the transformation, $\mathbf{H}$, that maps $\mathbf{m}_0$ to $\mathbf{m}_1$, and then inverting it.
     This can be interpreted as a data matching problem between $\mathbf{m}_1$ and $\mathbf{m}_0$.
@@
 %\multiplot{4}{mod,vel-migration,image0,image1}{width=0.98\columnwidth}{The Sigsbee model reflectivity (a), migration velocity model (b), the first migrated image, $\mathbf{m}_0$ (c), and the second migrated image, $\mathbf{m}_1$ (d).}
-    Since the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations.
+    Because the primary differences between conventionally migrated images and least-squares migrated images amount to amplitude and frequency variations, we use two separate non-stationary operators to represent the forward Hessian---one to account for amplitude variations, and the other to account for frequency variations.
     Therefore, our approximation of $\mathbf{H}$ can be calculated from some application of a non-stationary amplitude balancing operator, $\mathbf{A}$, and a non-stationary frequency balancing operator, $\mathbf{S}$.
-    We first calculate the forward Hessian since the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
+    We first calculate the forward Hessian because the forward frequency balancing operation, $\mathbf{S}$, is well defined and simple to calculate. 
     We then invert our approximation to the Hessian and apply it to $\mathbf{m}_0$ to correct the amplitude and frequency content of the migrated image.
@@
     The corresponding diagonal weighting operator, $\mathbf{A}$, can be applied such that $\mathbf{m}_1 \approx \mathbf{A}\mathbf{m}_0$ to balance the amplitudes of each trace.
-    Since this is a linear operation that only has diagonal elements, it is trivial to find the inverse operator, $\mathbf{A}^{-1}$.
+    Because this is a linear operation that only has diagonal elements, finding the inverse operator, $\mathbf{A}^{-1}$ is trivial.
 
@@
     To do this, we propose using non-stationary triangle smoothing. 
-    This approach involves finding and applying a non-stationary smoothing operator, which is the amount of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.
+    This approach involves finding and applying a non-stationary smoothing operator, which is the number of samples, in both dimensions, that $\mathbf{m}_0$ will be averaged over in a triangle weight, to balance the local frequency content with $\mathbf{m}_1$.
 
@@
     where $\mathbf{A}$ is the operator that balances the amplitudes of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, and $\mathbf{S}$ is the operator that balances the local frequency content of $\mathbf{m}_0$ with respect to $\mathbf{m}_1$, both defined previously.
-    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric, since both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
+    Applying the operations in this order allows the approximation of $\mathbf{H}$ to be symmetric because both $\mathbf{A}$ and $\mathbf{S}$ are symmetric operations. 
     Splitting up our approximation to the Hessian into two separate operators allows us to control how much of each operation and the order of each operation goes into correcting the image, and see how it affects the resulting image.
@@
 
-    Since the amplitude operators only contain diagonal terms, they are simple to invert. 
+    Because the amplitude operators only contain diagonal terms, they are simple to invert. 
     However, $\mathbf{S}^{-1}$ is non-trivial to calculate since inverse smoothing can create physically unrealistic high-frequency data if inverted incorrectly without regularization.
@@
     The source wavelet for generating the synthetic data is a Ricker wavelet centered at 10 Hz.
-    The record length of the synthetic data is 10 s with a time step of 4 ms.
+    The record length of the synthetic data is 10 s with a sampling interval of 4 ms.
 We use reverse-time migration (RTM) as our migration operator.
@@
     We begin with the sub-surface reflectivity model (Figure \ref{fig:mod}) and migration velocity model (Figure \ref{fig:vel-migration}).
-    Next, we forward model the seismic data and migrate it to get our first conventionally migrated image, $\mathbf{m}_0$ (Figure \ref{fig:image0}). 
-    Then, we forward model $\mathbf{m}_0$ and remigrate that data to get $\mathbf{m}_1$ (Figure \ref{fig:image1}).
+    Next, we forward model the seismic data and migrate it to obtain our first conventionally migrated image, $\mathbf{m}_0$ (Figure \ref{fig:image0}). 
+    Then, we forward model $\mathbf{m}_0$ and remigrate that data to obtain $\mathbf{m}_1$ (Figure \ref{fig:image1}).
     This provides us with the two images, $\mathbf{m}_0$ and $\mathbf{m}_1$, that we can use to find the operation $\mathbf{H}$ that maps $\mathbf{m}_0$ to $\mathbf{m}_1$.
@@
     In this paper, we apply an approximate inverse Hessian operator to a conventional migrated image to approximate the least-squares migrated image.
-    Since the primary differences between least-squares migration and conventional migration amount to amplitude and frequency variations, we approximate the forward Hessian by calculating frequency and amplitude matching operators.
+    Because the primary differences between least-squares migration and conventional migration amount to amplitude and frequency variations, we approximate the forward Hessian by calculating frequency and amplitude matching operators.
     The amplitude matching operator is found by calculating the amplitude envelopes of migrated and remigrated images and smoothly dividing them, and the frequency matching operator is found using an iterative algorithm and non-stationary smoothing.

### 2018-05-03 abs.tex
thesis updated
thesis almost done

@@
-Data matching applications are present in many computational geophysics problems.
-In this thesis, I introduce a new algorithm to aid in data matching that balances local frequency content between seismic data sets.
+\author{Sarah Greer, The University of Texas at Austin}
+\title{Abstract}
+\label{ch:abs}
+
+Data matching applications appear in many computational geophysics problems.
+In this thesis, I introduce a new efficient algorithm to aid in data matching that balances local frequency content between seismic data sets.
 Then, I provide a few examples where applying this algorithm to seismic data helps improve results.
 These applications include multi-component image registration, matching and merging high-resolution and legacy seismic images, and improving migration resolution by approximating the least-squares Hessian.
-The applications are applied to several 2D and 3D, real and synthetic data sets.
+The applications are illustrated by several 2D and 3D, real and synthetic data sets.

### 2018-05-03 ack.tex
thesis almost done

@@
 %Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
-You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
+%You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
+You are an incredibly bright and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
 

### 2018-05-03 chapter-background/paper.tex
thesis almost done

@@
 \author{Sarah Yvonne Greer}
+\label{ch:chapter-background}
+
 \maketitle
 \inputdir{../chapter-locfreq/merge}
-Seismic data contain fundamentally non-stationary variations in attributes such as frequency and amplitude content.
+Seismic data exhibit fundamentally non-stationary variations in attributes such as frequency and amplitude content.
 For example, Figure \ref{fig:legacy,low-freq} shows a sample seismic image and its local frequency content \cite[]{locfreq}.
@@
 
-Local seismic attributes are useful in the analysis of these non-stationary variations that are naturally present in seismic data \cite{attr}.
-The calculation of these attributes uses iterative inversion with shaping regularization \cite{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
+Local seismic attributes are useful in the analysis of these non-stationary variations \cite[]{attr}.
+The calculation of these attributes uses iterative inversion with shaping regularization \cite[]{shap} to measure signal characteristics in local regions of data, rather than specifying windows or looking at instantaneous attributes.
 For the procedures described in this thesis, local attributes are more appropriate than instantaneous attributes.
 Take, for example, local frequency (Figure \ref{fig:legacy,low-freq}), as opposed to instantaneous frequency.
-Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which allows for a point by point comparison of frequency values between images.
+Local frequency allows the comparison of frequency content in a local region of samples, as opposed to instantaneous frequency, which attempts to provide a point by point comparison of frequency values between images.
 Because the corresponding reflections between images might not be precisely aligned in time, using the local frequency attribute to balance frequency content between images would allow for more accurate frequency balancing than instantaneous frequency.
-Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or extremely high frequency values \cite[]{attr}.
+Additionally, local frequency is a more geologically accurate attribute than instantaneous frequency because it honors time-frequency uncertainty and does not contain physically unrealistic negative or unrealistic high frequency values \cite[]{attr}.
 
 \multiplot{2}{legacy,low-freq}{width=0.47\columnwidth}{A seismic image (a) and its local frequency content (b).
-Because its local frequency varies both spatially and temporally, we can say its frequency content is {\it non-stationary}.}
+Because its local frequency varies both spatially and temporally, we can say its frequency content is smoothly {\it non-stationary}.}
 
@@
 %These applications can be solved by specifying and applying the three previously stated data matching operators: filtering, scaling, and shifting.
-To demonstrate the three matching operations in action, I apply them consecutively to an example 2D trace shown in Figure \ref{fig:one0}.
+To demonstrate the three matching operations in action, I apply them consecutively to an example trace shown in Figure \ref{fig:one0}.
 The data used in this example comes from a line from the {\em P-cable} data sets.
@@
 I use the three data matching operators by first filtering (Figure \ref{fig:one1}), then scaling (Figure \ref{fig:one2}), and finally shifting (Figure \ref{fig:one3}).
-The three operations are described in more detail in the following sections.
+These three operations are described in more detail in the following sections.
 
@@
 \section{Filtering}
-Perhaps one of the most visibly obvious differences between data sets comes from differences in frequency content.
-For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequency content than the black trace which makes it difficult to observe that they may both contain data from the same model.
+Perhaps one of the most visibly obvious differences between data sets comes from their difference in frequency content.
+For example, Figure \ref{fig:one0} shows two traces that need to be matched; the red trace has visibly higher frequencies than the black trace which makes it difficult to observe that they may both contain data from the same model.
 This makes the correlation of these two signals, both visually and computationally, difficult as they have information in different frequency bands.
-In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content with the black trace because the high frequency content is not physically present in the black trace.
+In this situation, we want to remove the higher frequency variations from the red trace to match the lower frequency content of the black trace.
+%because the high frequency content is not physically present in the black trace.
 
@@
 
-We instead do this by applying a non-stationary triangle smoothing operator to the red trace to match local frequency content with the black trace.
+We can do this by applying a non-stationary triangle smoothing operator to the red trace to match the local frequency content of the black trace.
 We define the {\em radius} of this operator as the number of samples in a specified dimension that are averaged over in a triangle weight.
 We allow the radius to vary in all dimensions to account for the potential non-stationary frequency variations present in the data.
-This is a linear operation---if we represent the filtering operation by a matrix applied to the trace represented by a vector, the matrix would be diagonally banded, where the size of the band at a particular index is related to the size of the smoothing radius at that point.
+This is a linear operation---if we represent the filtering operation by a matrix applied to the trace represented by a vector, the matrix would be diagonally banded, where the width of the band at a particular index is related to the size of the smoothing radius at that point.
 
@@
 The second primary data matching operation is scaling. 
-Amplitudes of the data we are trying to match may not be initially correct---scaling attempts to balance the amplitudes between these data.
+Amplitudes of the data we are trying to match may not be initially equivalent---scaling attempts to balance the amplitudes between these data.
 Scaling is also a linear operation and can be thought of as a diagonal operation; if the scaling operator is represented by a matrix multiplication to the data vector, this matrix only contains terms along the diagonal.
@@
 In this thesis, the diagonal scaling operator is found by first calculating the amplitude envelope of the data that need to be matched.
-Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces and represents the diagonal elements of the scaling operator.
+Then, the scaling weight is calculated by smoothly dividing the amplitude envelopes of the two traces to find the diagonal elements of the scaling operator.
 %The result of

### 2018-05-03 chapter-conclusion/paper.tex
thesis almost done

@@
 \author{Sarah Yvonne Greer}
+\label{ch:chapter-conclusion}
+
 \maketitle
@@
 
-The scripts and programs used to produce the examples in this thesis are below.
+For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.
+The code for the rest of the examples in this thesis are available online at the URL above.
+%The code for the rest of the examples in this thesis is available online at the URL above.
+
+%The scripts and programs used to produce the examples in this thesis are below.
 
@@
   tabsize=2,	                   % sets default tabsize to 2 spaces
-  keywords=[1]{from,for,if,in,import},
+  keywords=[1]{from,for,if,in,import,def},
   keywords=[2]{Flow,Fetch},
@@
         \ref{fig:legacy,low-freq} & chapter-locfreq/merge/ & \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\ 
-        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & \ref{lst:dm} \\ 
-        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
+        \ref{fig:one0,one1,one2,one3}, \ref{fig:bef,aft} & chapter-background/dmExample/ & ---\\%\ref{lst:dm} \\ 
+        \ref{fig:legacy,hires}, \ref{fig:nspectra,hires-smooth-spec}, \ref{fig:rect}, \ref{fig:freqdif,freqdif-filt}           & chapter-merge/apache/ & ---\\%\ref{lst:mas} \\ 
         \ref{fig:legacy,hires-agc}, \ref{fig:rect5}, \ref{fig:nspectra-orig,high-smooth-spec5}, \ref{fig:freqdif,freqdif-filt5}          & chapter-locfreq/merge/ &   \ref{lst:lms}, \ref{lst:lmrp}, \ref{lst:lmrc}\\
-        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  \ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
-        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  \ref{lst:conv}\\ 
-        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & \ref{lst:mas} \\ 
-        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & \ref{lst:mps} \\ 
-        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ & \ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
-        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & \ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\
-        \ref{fig:tf}, & chapter-merge/triop/ & \ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
+        \ref{fig:pp,ss}, \ref{fig:before,after}         & chapter-locfreq/vecta/&  --- \\%\ref{lst:lvs}, \ref{lst:lvn}, \ref{lst:lvrp}, \ref{lst:lvrc}\\ 
+        \ref{fig:all,scalar} & chapter-locfreq/convergence/&  --- \\%\ref{lst:conv}\\ 
+        \ref{fig:legacy,hires,merge2-reverse}, \ref{fig:diff0,diff1}, \ref{fig:hweight,lweight-reverse}, \ref{fig:nspectra22-reverse}           & chapter-merge/apache/ & --- \\% \ref{lst:mas} \\ 
+        \ref{fig:window1,window2}, \ref{fig:nspectra2} & chapter-merge/pcable/ & --- \\%\ref{lst:mps} \\ 
+        \ref{fig:legacy4,hires4,merge3}  & chapter-merge/pcable2/ &  --- \\%\ref{lst:mp2s}, \ref{lst:mp2rp}, \ref{lst:mp2rc}\\ 
+        \ref{fig:mod,vel-migration}, \ref{fig:image0,image1}, \ref{fig:a0,rect10b}, \ref{fig:migdec-shap}, \ref{fig:image0-w3,migdec-w3,mod-w3} & chapter-merge/mighes/ & --- \\%\ref{lst:hss}, \ref{lst:hsrp}, \ref{lst:hsrc}\\
+        \ref{fig:tf}, & chapter-merge/triop/ & --- \\%\ref{lst:triop}, \ref{lst:trfu} \ref{lst:solve}\\ 
 \end{tabular}
 \end{table}
-For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.
 

### 2018-05-03 chapter-intro/paper.tex
thesis almost done

@@
 \author{Sarah Yvonne Greer}
+\label{ch:chapter-intro}
+
 \maketitle
 
-%Data matching problems are prevalent in many applications of seismic data processing.
-Data matching is a conceptually simple problem that is present in many computational geophysics applications. 
+Data matching is a conceptually simple problem that appears in many computational geophysics applications. 
 Essentially, given two data sets, data matching can be thought of as finding the transformation from one data set to the other. 
@@
 These must be matched properly, as the two images are not temporally aligned and have different frequency and amplitude content, in order for them to be directly compared and interpreted.
-%Many other examples of data matching are prevalent in geophysical applications, such as time-lapse image registration, seismic and well-log tying, deconvolution, and surface-related multiple elimination.
 
-Many other geophysics applications can be addressed from a data matching standpoint and fall under a few main categories.
-Applications are present for data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in chapter 3.
-Other problems consist of matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in chapter 4.
-Data matching problems are also present for matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in chapter 5.
-An approach to these many data matching problems is to find the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
+Many other geophysics applications can be addressed from a data matching standpoint and fall under several main categories.
+One category is matching data of different physics, such as tying synthetic seismograms from well log data to surface seismic data \cite[]{herrera, bader} and multicomponent seismic image registration \cite[]{multi,warp,hardage}, which is discussed in Chapter \ref{ch:chapter-locfreq}.
+Another category involves matching differently acquired data, such as time-lapse image registration \cite[]{timelapse} and merging legacy and high-resolution seismic data \cite[]{merge}, which is a primary application in this thesis and is addressed in Chapter \ref{ch:chapter-merge}.
+The third category is matching data and ideal models, such as in deconvolution or approximating the inverse Hessian to improve migration resolution \cite[]{migdec,rtmmf,mighess}, which is discussed further in Chapter \ref{ch:chapter-mighes}.
+The objective of these many data matching problems is to approximate the operation to match the data using a combination of three data matching operations---filtering, scaling, and shifting.
 %In this thesis, I will outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
-In this thesis, I will discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
+In this thesis, I discuss these three data matching operators, outline several methods and applications of seismic data matching, and introduce a new method for matching frequency content between data sets.
 
 %However, many data matching algorithms, such as Dynamic Time Warping, can be computationally expensive, especially when applied to large multi-dimensional seismic data sets.
-The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed in \cite{merge2} and \cite{merge}.
-In this example, two seismic data sets, each acquired over the same area but with different technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
-This new image includes the best signal characteristics from the two initial images while minimizing their weaknesses.
-Much of the theory behind Chapter 3 was developed in application to this example but was later extended to other examples.
-As a result, I use data from this application throughout much of this thesis.
+The primary inspiration for much of the work in this thesis comes from the example of matching and merging high-resolution and legacy seismic images, as discussed by \cite{merge2, merge}.
+In this example, two seismic data sets, each acquired over the same area but with different acquisition technologies, are first matched in frequency, amplitude, and time, before being merged together to produce a third image.
+This new image includes the best signal characteristics from the two initial images while minimizing their comparative weaknesses.
+Much of the theory behind Chapter \ref{ch:chapter-locfreq} was developed in application to this example but was later extended to other examples.
+Therefore, I data from this application throughout much of this thesis.
 
-This thesis contains two primary data sets to which I refer. 
+\section{Data}
+This thesis refers to two primary data sets. 
 The first pair, henceforth called the {\it Apache} data sets, are two 2D lines, acquired over the same area but with different methods, from the Gulf of Mexico. 
-These two images will always be plotted in the {\em seismic} color map.
+These two images are plotted in the {\em seismic} color map, as in Figure \ref{fig:legacy,hires}.
 
-The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets in the Gulf of Mexico \cite[]{pcable,data}.
-These two images will always be plotted in grayscale.
-In parts of this thesis, I show a 2D line from this 3D data set for simplicity of plotting.
+The second pair, the {\em P-cable} data sets, are two 3D volumes, acquired over the same area but with different methods, from a different area from the {\em Apache} data sets, but also in the Gulf of Mexico \cite[]{pcable,data}.
+These two images will always be plotted in grayscale, as in Figure \ref{fig:legacy,hires-agc}.
+In parts of this thesis, I show a 2D line from this 3D data set for simplicity of illustration.
 
 Two other data sets, both 2D, were used in this paper. 
-In chapter 3, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
-In chapter 5, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.
+In Chapter \ref{ch:chapter-locfreq}, I use two multi-component images to demonstrate an adaptation for the proposed frequency balancing algorithm in an application of multi-component image registration \cite[]{attr}.
+In Chapter \ref{ch:chapter-mighes}, I use the Sigsbee synthetic data set \cite[]{sigsbee} in the application of improving migration resolution using non-stationary matching.
 
+\section{Outline}
 This thesis is organized as follows.
-In the second chapter, I overview the basics behind the three data matching operations---scaling, shifting, and filtering.
-In chapter three, I introduce two methods for balancing local frequency content in seismic data sets.
-In the fourth chapter, I show the first example of data matching---matching and merging high-resolution and legacy seismic images.
-In the chapter five, I show an example of data matching to improve migration resolution.
-Finally, in chapter six, I provide concluding remarks.
+In Chapter \ref{ch:chapter-background}, I overview the theory behind the three data matching operations---scaling, shifting, and filtering.
+In Chapter \ref{ch:chapter-locfreq}, I introduce two methods for balancing local frequency content in seismic data sets.
+In Chapter \ref{ch:chapter-merge}, I show the first example of data matching: matching and merging high-resolution and legacy seismic images.
+In Chapter \ref{ch:chapter-mighes}, I show an example of applying data matching to improve migration resolution.
+In Chapter \ref{ch:chapter-conclusion}, I provide concluding remarks.
+Finally, in the appendix, I include information on how to reproduce the results of this thesis.

### 2018-05-03 chapter-locfreq/merge/radius.py

@@ -1,33 +1,35 @@
 from rsf.proj import *
 
-def radius(high, low,               # initial high-resolution and legacy images
+def radius(high, low,               # initial high and low frequency images
            niter,                   # number of corrections
            c,                       # 'step length' for radius corrections. Can 
-                                    # be type int or float for constant c 
-                                    # or type array for changing c.
+                                    #       be type int or float for constant c 
+                                    #       or type array for changing c.
            bias=-15, clip=30,       # bias and clip for display
            rect1=40, rect2=80,      # radius for local frequency calculation
            maxrad=1000,             # maximum allowed radius
            theor=True,              # use theoretical smoothing radius
            scale=9,                 # scale for theoretical smoothing radius
            initial=10,              # initial value for contant smoothing radius 
-           minval=0,
-           maxval=25,
+           minval=0, maxval=25,     # min and max local frequency for display
            titlehigh="Hires",
            titlelow="Legacy"):
 
     if type(c) is float or type(c) is int:
         c = [c]*niter
 
+    # plot image
     def seisplot(name):
         return 'grey title="%s"'%name
     
+    # local frequency
     locfreq = '''iphase order=10 rect1=%d rect2=%d hertz=y complex=y | 
                  put label="Frequency" unit=Hz'''%(rect1,rect2)
 
     def locfreqplot(name):
         return 'grey mean=y color=j scalebar=y title="%s" '%name
 
+    # difference in local frequencies
     freqdif = 'add scale=-1,1 ${SOURCES[1]} | put label=Frequency'
 
     def freqdifplot(num):
@@ -36,31 +38,33 @@ def radius(high, low,               # initial high-resolution and legacy images
                   clip=%d bias=%d minval=%d 
                   maxval=%d''' %(num,clip,bias,minval,maxval) 
 
+    # plot spectral content  
     specplot = '''cat axis=2 ${SOURCES[1]} | 
-                  scale axis=1 | window max1=180 |
-                  graph title="Normalized Spectra" label2="Amplitude" unit2=""'''
+                 scale axis=1 | window max1=180 |
[…]

### 2018-05-04 chapter-conclusion/paper.tex
thesis update

@@
 
-\subsection{Summary}
+%\subsection{Summary}
 
 In this thesis, I discussed several methods and applications of data matching in seismic data analysis.
-Chapter 2 focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
-Chapter 3 introduces different methods of frequency balancing using non-stationary smoothing. 
+Chapter \ref{ch:chapter-background} focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
+Chapter \ref{ch:chapter-locfreq} introduces different methods of frequency balancing using non-stationary smoothing. 
 The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based off of the assumption that the data we observe can be modeled by a summation of Ricker wavelets.
@@
 
-Chapter 4 goes into more detail of the application of matching and merging high-resolution and legacy seismic images.
+Chapter \ref{ch:chapter-merge} goes into more detail of the application of matching and merging high-resolution and legacy seismic images.
 This example takes two seismic volumes, acquired over the same area but using different technologies, and first matches them before merging them together to produce an optimized third image.
@@
 
-Chapter 5 discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
+Chapter \ref{ch:chapter-mighes} discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
 An approximation to the least-squares Hessian can be calculated by solving a data matching problem between two conventionally migrated images, and the Hessian can be represented by the combination of amplitude and frequency balancing operations.
@@
 \subsection{Future work}
-In the future, the work presented in chapter 5 should be extended to involve real data and 3D examples. 
+In the future, the work presented in Chapter \ref{ch:chapter-mighes} should be extended to involve real data and 3D examples. 
 It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debfilt,prestack,poststack}, to see how it compares in different situations.
@@
 the phase of the signal to be matched. 
-Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of chapter 4, but other data matching problems could benefit from these corrections.
+Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of Chapter \ref{ch:chapter-merge}, but other data matching problems could benefit from these corrections.
 
@@
 
-For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in chapter 3.
+For brevity in this thesis, code is only included for one example of the main frequency balancing algorithm presented in Chapter \ref{ch:chapter-locfreq}.
 The code for the rest of the examples in this thesis are available online at the URL above.
@@
 \centering
-\caption{Figures and the scripts to generate them}
+\caption{List of figures in this thesis and the locations of scripts and programs to generate them}
 \label{my-label}

### 2018-05-04 chapter-locfreq/paper.tex
thesis almost done
thesis update

@@
 \author{Sarah Yvonne Greer}
+\label{ch:chapter-locfreq}
+
 \maketitle
@@
         \inputdir{merge}
-        The theoretical smoothing radius works in some situations, like in the first example of the next chapter, but it does not work in situations where litte overlap is present in frequency content between data sets, like in the second example of the next chapter.
+        The theoretical smoothing radius works in some situations, like in the first example of Chapter \ref{ch:chapter-merge}, but it does not work in situations where litte overlap is present in frequency content between data sets, like in the second example of Chapter \ref{ch:chapter-merge}.
         In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.
@@
 
-        An application of aligning the high-resolution and legacy images is discussed in the next chapter.
+        An application of aligning the high-resolution and legacy images is discussed in Chapter \ref{ch:chapter-merge}.
 
@@
         So far, this algorithm and its modification have been discussed when the smoothing radius is only calculated along one dimension. 
-        However, Chapter 5 provides an application where the smoothing radius is calculated in multiple directions.
+        However, Chapter \ref{ch:chapter-mighes} provides an application where the smoothing radius is calculated in multiple directions.
 
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
         We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.

### 2018-05-04 chapter-mighes/paper.tex
thesis almost done
thesis update

@@
 \author{Sarah Greer*, Zhiguang Xue, and Sergey Fomel, The University of Texas at Austin}
+\label{ch:chapter-mighes}
+
 \relax\footnotetext{Parts of this chapter were first published in \cite{mighess}.
@@
 
-    In this paper, we take a different approach. 
+    In this thesis, we take a different approach. 
     We note that the two primary differences between least squares migrated images and conventional migrated images are amplitude and frequency variations \cite[]{Hou2015, Hou2016}. 
@@
 
-    We find the smoothing radius iteratively using the method of \cite{locfreq} from chapter 3, with a modification that allows the smoothing radius to be calculated in both spatial directions. 
+    We find the smoothing radius iteratively using the method of \cite{locfreq} from Chapter \ref{ch:chapter-locfreq}, with a modification that allows the smoothing radius to be calculated in both spatial directions.
 Essentially, this is found by choosing an initial guess of a smoothing radius, $\mathbf{R}^{(0)}$, and updating it iteratively such that 
@@
     For this particular application using depth migration, this operator should technically be specified to balance {\em wavenumber} instead of {\em frequency}.
-    However, it is kept as frequency to keep consistent terminology with the algorithm developed in chapter 3.
+    However, it is kept as frequency to keep consistent terminology with the algorithm developed in Chapter \ref{ch:chapter-locfreq}.
 
@@
     Least-squares migration can produce an accurate migrated image, but it is more computationally expensive than conventional migration.
-    In this paper, we apply an approximate inverse Hessian operator to a conventional migrated image to approximate the least-squares migrated image.
+    In this chapter, we apply an approximate inverse Hessian operator to a conventional migrated image to approximate the least-squares migrated image.
     Because the primary differences between least-squares migration and conventional migration amount to amplitude and frequency variations, we approximate the forward Hessian by calculating frequency and amplitude matching operators.
@@
 
-\section{Acknowledgements}
+\section{Acknowledgments}
     We thank the sponsors of the Texas Consortium for Computational Seismology (TCCS) for their financial support.
-    The examples in this paper can be reproduced using the Madagascar open-source software package \cite[]{madagascar}.
+    The examples in this chapter can be reproduced using the Madagascar open-source software package \cite[]{madagascar}.

### 2018-05-25 ack.tex
thesis done

@@
 I genuinely believe that working with him has beneficially shaped the trajectory of my life.
-Through his guidance and the opportunities he has given me, he has helped me to realize how much I truly enjoy learning, showed me the importance of reproducible computational research, introduced me new ways of thinking about and approaching problems, and inspired me to continue my studies in graduate school.
+Through his guidance and the opportunities he has given me, he has helped me to realize how much I truly enjoy learning, showed me the importance of reproducible computational research, introduced me to new ways of thinking about and approaching problems, and inspired me to continue my studies in graduate school.
 For all that, I will be forever grateful.
@@
 
-I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two years.
-%Thank you for all your guidance, and for being there for the best memories during my undergraduate career.
-%Thank you for your intellectually stimulating conversations, life advice, and making me feel as though I am ``part of the group'', despite the fact that I was not a graduate student.
+I would especially like to thank the members of the Texas Consortium for Computational Seismology (TCCS), of which I have been a part for the past two and a half years.
 Thank you all for your intellectually stimulating conversations, life advice, and for including me as ``part of the group'', despite the fact that I was only an undergraduate student.
-%You are an incredibly enjoyable and intellectually stimulating group, and I am glad I have had the opportunity to cross paths with all of you in life.
 I will forever cherish the friendships and memories I have made with all of you during my time as a part of TCCS. 
-%Many of the best memories of my time at UT Austin are from being a part of TCCS, %come from the %time I have spent as a part of TCCS.
-%You are an incredibly ingenuitive and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
 You are an incredibly bright and enjoyable group, and I am fortunate to have had the opportunity to cross paths in life with every single one of you.
+
+%I am very fortunate to be a part of the Jackson School of Geoscience's Undergraduate Honors Research Program, which has given me the opportunity to write this thesis. ... hm.
 

### 2018-05-25 chapter-background/paper.tex
thesis done

@@
 
-Chapter 3 is dedicated to the discussion of how to find this frequency balancing operator.
+Chapter \ref{ch:chapter-locfreq} is dedicated to the discussion of how to find this frequency balancing operator.
 Figure \ref{fig:one1} shows the two traces after balancing the local frequency content of the red trace to match the black trace.
@@
 \section{Shifting}
-If two events are slightly misaligned in time, finding the transformation that correctly aligns these events is referred to as {\em shifting}.
+If two events are misaligned in time, finding the transformation that correctly aligns these events is referred to as {\em shifting}.
 Dynamic time warping is a common algorithm used for the alignment of events of two time series, both for geophysical and other applications, as diverse as speech recognition and finance \cite[]{herrera2012,hale2013,dtw,finance}.
@@
 Local similarity extends the concept of local seismic attributes to global correlation coefficients and is effective for measuring the match of seismic events in a local region of samples \cite[]{attr}.
-Unlike filtering and scaling, shifting is a non-linear transformation.
+%Unlike filtering and scaling, shifting is a non-linear transformation.
 %The time shift calculated is
@@
 The result after finding and applying the time shift to the red trace to match it to the black trace is in Figure \ref{fig:one3}.
-This shifting operation is discussed in more detail in chapters 3 and 4.
+This shifting operation is discussed in more detail in Chapters \ref{ch:chapter-locfreq} and \ref{ch:chapter-merge}..
 
@@
 After correcting for frequency variations, amplitude variations, and time shifts, additional corrections can be applied to further refine the match if necessary.
-In some cases, multiple rounds of applying these operators and in different orders may be beneficial for the best match.
 These three operators are noncommutative, so the order in which they are applied matters.
@@
 An illustration of this property is shown in Figure \ref{fig:bef,aft}.
+In some cases, multiple rounds of applying these operators and in different orders may be beneficial for the best match.
 
@@
 A summary of the three data matching operations is shown in Table \ref{op}.
-Both scaling and filtering are linear operations, whereas shifting is generally a non-linear operation.
-Additionally, as scaling is to weighting in the time domain, filtering is to weighting in the Fourier domain.
-The next chapter discusses a few methods and examples of filtering, or frequency balancing, between two data sets.
+%Both scaling and filtering are linear operations, whereas shifting is generally a non-linear operation.
+In the stationary case, if scaling is weighting in the time domain, filtering is weighting in the Fourier domain.
+Chapter \ref{ch:chapter-locfreq} discusses a few methods and examples of filtering, or frequency balancing, between two data sets.

### 2018-05-25 chapter-locfreq/paper.tex
thesis done

@@
         \inputdir{merge}
-        The theoretical smoothing radius works in some situations, like in the first example of Chapter \ref{ch:chapter-merge}, but it does not work in situations where litte overlap is present in frequency content between data sets, like in the second example of Chapter \ref{ch:chapter-merge}.
+        The theoretical smoothing radius works in some situations, like in the first example of Chapter \ref{ch:chapter-merge}, but it does not work in situations where little overlap is present in frequency content between data sets, like in the second example of Chapter \ref{ch:chapter-merge}.
         In this case, we use an iterative method to find what the smoothing radius should be that is based on the physical understanding of what smoothing is doing.
@@
 
-        Using the assumptions, we can choose an intial guess for the smoothing radius and continually adjust the smoothing radius until we  achieve the desired result of balancing the local frequency content between the two data sets.
+        Using the assumptions, we can choose an initial guess for the smoothing radius and continually adjust the smoothing radius until we  achieve the desired result of balancing the local frequency content between the two data sets.
         In practice, this method produces an acceptable solution in approximately 5 iterations and exhibits sublinear convergence.

### 2018-05-25 vita.tex
thesis done

@@
-Sarah graduated with high honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin (UT Austin) to pursue her undergraduate studies.
+Sarah graduated with high honors from Cinco Ranch High School in Katy, Texas in 2014 and came to The University of Texas at Austin to pursue her undergraduate studies. 
 She is a candidate for a Bachelor of Science degree in Geophysics from the Jackson School of Geosciences and a Bachelor of Science degree in Mathematics from the College of Natural Sciences. 
 After graduation, she plans on pursuing a PhD in Mathematics and Computational Science at the Massachusetts Institute of Technology.
+%After graduation, she plans on pursuing a PhD in Computational Science, Engineering, and Mathematics at The University of Texas at Austin.
+%After graduation, she plans on pursuing a PhD in Computational and Mathematical Engineering at Stanford University.

### 2019-08-15 thesis/chapter-merge/paper.tex
moving thesis

--- 2018-04-30 chapter-merge/paper.tex
@@
 \author{Sarah Greer and Sergey Fomel, The University of Texas at Austin}
+\label{ch:chapter-merge}
+
 \relax\footnotetext{Parts of this chapter were first published in \cite{merge2}.
@@
     Here, the radius at each point is the amount of time, in seconds, that that specific data point gets averaged over in a triangle weight in the temporal direction.
-    In this example, we find the radius of smoothing using the theoretical approach described in the previous chapter, so 
+    In this example, we find the radius of smoothing using the theoretical approach described in Chapter \ref{ch:chapter-locfreq}, so 
     \begin{equation}
@@
     We first apply a low-cut filter to the legacy data to remove the low frequency information that is simply not present in the high-resolution image. 
-    Next, we adjust the non-stationary smoothing radius using the simple iterative algorithm \cite[]{locfreq} that was described in the previous chapter.
+    Next, we adjust the non-stationary smoothing radius using the simple iterative algorithm \cite[]{locfreq} that was described in Chapter \ref{ch:chapter-locfreq}.
 

### 2019-08-15 chapter-conclusion/paper.tex
moved thesis from research repo

@@
 
-%\subsection{Summary}
+%\section{Summary}
 
 In this thesis, I discussed several methods and applications of data matching in seismic data analysis.
-Chapter \ref{ch:chapter-background} focuses on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
-Chapter \ref{ch:chapter-locfreq} introduces different methods of frequency balancing using non-stationary smoothing. 
-The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based off of the assumption that the data we observe can be modeled by a summation of Ricker wavelets.
-This method worked well in certain situations, but was not robust enough to work for any given data set.
-In the second method, I introduced an iterative algorithm to find the smoothing radius, and this method converges quickly and works well in several presented situations. 
-Finally, a modification to this algorithm was shown and allows smoothing for more complex data sets.
+Chapter \ref{ch:chapter-background} introduced on introducing the three data matching operators that are used in this thesis---shifting, scaling, and filtering.
+Chapter \ref{ch:chapter-locfreq} introduced different methods of frequency balancing using non-stationary smoothing. 
+The first method to find the non-stationary smoothing {\em radius}, or number of samples each data point is averaged over with a triangle weight, took a theoretical approach based on the assumption that the data we observe can be represented by a superposition of Ricker wavelets.
+This method worked well in certain situations, but was not robust enough to work for all of the given data sets.
+In the second method, I introduced an iterative algorithm to find the smoothing radius. 
+In my experiments, this method converges quickly and works well in several presented situations. 
+Finally, a modification to this algorithm was shown that allows adaptive smoothing for more complex data sets.
 
-This chapter also discusses two applications of these algorithms---the frequency balancing algorithm was demonstrated on an application of matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application of multicomponent seismic image registration.
+This chapter also discussed two applications of these algorithms.
+The frequency balancing algorithm was demonstrated on an application to matching high-resolution and legacy seismic images, and the modified algorithm was demonstrated on an application to multicomponent seismic image registration.
 
-Chapter \ref{ch:chapter-merge} goes into more detail of the application of matching and merging high-resolution and legacy seismic images.
+Chapter \ref{ch:chapter-merge} went into more detail of the application of matching and merging high-resolution and legacy seismic images.
 This example takes two seismic volumes, acquired over the same area but using different technologies, and first matches them before merging them together to produce an optimized third image.
-First, the method is demonstrated on a 2D line from the Gulf of Mexico.
-Then, the method is applied to a 3D seismic volume from a different part of the Gulf of Mexico.
+First, I demonstrated the method on a 2D line from the Gulf of Mexico.
+Then, I applied the method to a 3D seismic volume from a different part of the Gulf of Mexico.
 
 Chapter \ref{ch:chapter-mighes} discusses another application of improving migration resolution by approximating the least-squares Hessian using non-stationary data matching operations.
-An approximation to the least-squares Hessian can be calculated by solving a data matching problem between two conventionally migrated images, and the Hessian can be represented by the combination of amplitude and frequency balancing operations.
-An example is applied to a 2D synthetic Sigsbee data set.
+I showed that an approximation to the least-squares Hessian can be calculated by solving a data matching problem between two conventionally migrated images, and the Hessian can be represented by the combination of amplitude and frequency balancing operations.
+I applied the proposed approach to a 2D synthetic Sigsbee data set, a traditional benchmark for imaging algorithms.
 
-\subsection{Future work}
+\section{Future work}
 In the future, the work presented in Chapter \ref{ch:chapter-mighes} should be extended to involve real data and 3D examples. 
-It also could benefit by comparing the results of the proposed approach taken in the chapter to other previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debfilt,prestack,poststack}, to see how it compares in different situations.
+It could also benefit from comparing the results of the proposed approach to previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,poststack,prestack,diagamp,debfilt,lsamp,pwlsrtm,siklsm}, to see how it compares in different situations.
+%It could also benefit from comparing the results of the proposed approach to previous approaches presented to approximate the least-squares Hessian \cite[]{migdec,lsamp,siklsm,pwlsrtm,diagamp,debfilt,prestack,poststack}, to see how it compares in different situations.
 
@@
 the phase of the signal to be matched. 
-Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of Chapter \ref{ch:chapter-merge}, but other data matching problems could benefit from these corrections.
+Negligible improvements were made when trying to incorporate phase corrections into the high-resolution and legacy data matching problem of Chapter \ref{ch:chapter-merge}. 
+However, other data matching problems could benefit from these corrections.
+
+The newly developed field of deep learning may also benefit from including these data matching techniques in the parameterization, as specifically tailoring the neural networks to work with geophysical data in this manner may produce better results.
+%Deep learning.
+%So fundamentally deep learning is about matching
+%so you have an input and an output and you're trying to find an operator that matches 
+%and so just the building blocks are different but possibly with the kind of operators that you develop here, shifting, scaling, and filtering, one could build a different kind of network that works with deep learning
+%so there's actually a connection
+%The example that we saw for image processing where with convolutional neural networks they are the building block with convolution and some form of non-linear mapping
+%and then you add them together to create layers
+%but actually seismic data in particular may make more sense to build them out of shifting and scaling
+%so I think it would be good to insert your mapping total (?)
+
+%Fundamentally deep learning is about matching, so you have an input and an output and you're trying to find an operator that matches. 
+%So just the building blocks are different, but possibly with the kind of operators that are developed here, shifting, scaling, and filtering, one could build a different kind of network that works with deep learning.
+%So there's actually a connection.
+%The example that we saw for image processing where with convolutional neural networks are the building blocks with convolution and some form of non-linear mapping, and then you add them together to create layers
+%But actually seismic data in particular may make more sense to build them out of shifting and scaling
 
@@
 %Below is the code for the 
-The examples in this thesis were implemented with the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagascar}.
+The examples in this thesis were implemented using the Madagascar open-source software environment for reproducible computational experiments \cite[]{madagascar}.
 The package is available at \url{http://www.ahay.org/}.
@@
 The reproducible document for the results in this thesis, including code, is available at \url{http://www.sygreer.com/research/honorsThesis}.
-However, some of the data used in this thesis are proprietary, so those results may not directly be reproducible.
+However, some of the data used in this thesis are proprietary, so those results may not be directly reproducible.
 
